\input{preamble}
\input{ep03_cast}
\title{Episode 3: S1E3 - Lord Snow}
\author{}
\date{}
\maketitle

\input{ep03_casttable}

\scene

\ti{KING'S LANDING GATES}

\ti{\NED ~arrives, with \SEPTAMORDANE, \JORY, and others.  They are met by a \PAGE}

\PAGE: Welcome, Lord Stark. Grand Maester Pycelle has called a meeting of the Small Council. The honor of your presence is requested. 

\NED: Get the girls settled in. I'll be back in time for supper. And, Jory, you go with them. 

\JORY: Yes, my Lord. 

\PAGE: If you'd like to change into something more appropriate$\ldots$ 

\scene

\ti{KINGS LANDING - THE THRONE ROOM}

\ti{\NED ~enters to see \JAIME ~sitting in front of the throne.}

\JAIME: Thank the gods you're here, Stark. About time we had some stern northern leadership. 

\NED: Glad to see you're protecting the throne. 

\JAIME: Sturdy old thing. How many kings' arses have polished it, I wonder ? What's the line ? The King shits and the Hand wipes. 

\NED: Very handsome armor. Not a scratch on it. 

\JAIME: I know. People have been swinging at me for years, but they always seem to miss. 

\NED: You've chosen your opponents wisely then. 

\JAIME: I have a knack for it. It must be strange for you coming into this room. I was standing right here when it happened. He was very brave, your brother. Your father too. They didn't deserve to die like that. Nobody deserves to die like that. 

\NED: But you just stood there and watched. 

\JAIME: 500 men just stood there and watched. All the great knights of the Seven Kingdoms. You think anyone said a word, lifted a finger ? No, Lord Stark. 500 men and this room was silent as a crypt. Except for the screams, of course, and the Mad King laughing. And later$\ldots$ When I watched the Mad King die, I remembered him laughing as your father burned$\ldots$ It felt like justice. 

\NED: Is that what you tell yourself at night ? You're a servant of justice ? That you were avenging my father when you shoved your sword in Aerys Targaryen's back ? 

\JAIME: Tell me$\ldots$ If I'd stabbed the Mad King in the belly instead of the back, would you admire me more ? 

\NED: You served him well when serving was safe. 

\ti{They make their way to the small council room, where \VARYS, \LITTLEFINGER, \PYCELLE, and \RENLY ~are sitting.}

\VARYS: Lord Stark. 

\NED: Lord Varys. 

\VARYS: I was grievously sorry to hear of your troubles on the Kingsroad. We are all praying for Prince Joffrey's full recovery. 

\NED: A shame you didn't say a prayer for the butcher's son. Renly ! You're looking well. 

\RENLY: And you look tired from the road. I told them this meeting could wait another day, but$\ldots$ 

\LITTLEFINGER: But we have a Kingdom to look after. I've hoped to meet you for some time, Lord Stark. No doubt Lady Catelyn has mentioned me. 

\NED: She has, Lord Baelish. I understand you knew my brother Brandon as well. 

\LITTLEFINGER: All too well. I still carry a token of his esteem from navel to collarbone. 

\NED: Perhaps you chose the wrong man to duel with. 

\LITTLEFINGER: It wasn't the man that I chose, my Lord. It was Catelyn Tully. A woman worth fighting for, I'm sure you'll agree. 

\PYCELLE: I humbly beg your pardon, my Lord Stark. 

\NED: Grand Maester. 

\PYCELLE: How many years has it been ? You were a young man. 

\NED: And you served another King. 

\PYCELLE: How forgetful of me. This belongs to you, now. Should we begin ? 

\NED: Without the King ? 

\RENLY: Winter may be coming, but I'm afraid the same cannot be said for my brother. 

\VARYS: His Grace has many cares. He entrusts some small matters to us that we might lighten the load. 

\LITTLEFINGER: We are the lords of small matters here. 

\RENLY: My brother instructs us to stage a tournament in honor of Lord Stark's appointment as Hand of the King. 

\LITTLEFINGER: Mmm, how much ? 

\NED: 40 000 gold dragons to the champion, 20 000 to the runner-up, 20 000 to the winning archer. 

\PYCELLE: Can the treasury bear such expense ? 

\LITTLEFINGER: I'll have to borrow it. The Lannisters will accommodate, I expect. We already owe Lord Tywin 3 million gold. What's another eighty thousand? 

\NED: Are you telling me the Crown is three million in debt? 

\LITTLEFINGER: I'm telling you the Crown is six million in debt. 

\NED: How could you let this happen? 

\LITTLEFINGER: The Master of Coin finds the money. The King and the Hand spend it. 

\NED: I will not believe Jon Arryn allowed Robert to bankrupt the realm. 

\PYCELLE: Lord Arryn gave wise and prudent advice, but I fear His Grace doesn't always listen. 

\RENLY: "Counting coppers,'' he calls it. 

\NED: I'll speak to him tomorrow. This tournament is an extravagance we cannot afford. 

\LITTLEFINGER: As you will. But still, we'd best make our plans. 

\NED: There will be no plans until I speak to Robert. Forgive me, my Lords. I had a long ride. 

\VARYS: You are the King's Hand, Lord Stark, we serve at your pleasure. 

\scene

\ti{KINGS LANDING - CERSEI'S CHAMBERS}

\ti{CERSEI is tending JOFFREY's wound}

\CERSEI: Please, it's nearly healed. 

\JOFFREY: It's ugly. 

\CERSEI: A King should have scars, you fought off a direwolf. You're a warrior like your father. 

\JOFFREY: I'm not like him. I didn't fight off anything. It bit me and all I did was scream. And the two Stark girls saw it, both of them. 

\CERSEI: That's not true. You killed the beast. You only spared the girl because of the love your father bears her father. When Aerys Targaryen sat on the Iron Throne, your father was a rebel and a traitor. Someday you'll sit on the throne and the truth will be what you make it. 

\JOFFREY: Do I have to marry her ? 

\CERSEI: Yes. She's very beautiful and young. If you don't like her, you only need to see her on formal occasions and when the time comes, to make little princes and princesses. And if you'd rather fuck painted whores, you'll fuck painted whores. And if you'd rather lie with noble virgins, so be it. You are my darling boy and the world will be exactly as you want it to be. Do something nice for the Stark girl. 

\JOFFREY: I don't want to. 

\CERSEI: No, but you will. The occasional kindness will spare you all sorts of trouble down the road. 

\JOFFREY: We allow the northerners too much power. They consider themselves our equals. 

\CERSEI: How would you handle them? 

\JOFFREY: I'd double their taxes and command them to supply ten thousand men to the royal army. 

\CERSEI: A royal army? 

\JOFFREY: Why should every lord command his own men ? It's primitive, no better than the hill tribes. We should have a standing army of men loyal to the Crown, trained by experienced soldiers$\ldots$ Instead of a mob of peasants who've never held pikes in their lives. 

\CERSEI: And if the northerners rebel? 

\JOFFREY: I'd crush them. Seize Winterfell and install someone loyal to the realm as Warden of the North. Uncle Kevan, maybe. 

\CERSEI: And these ten thousand northern troops, would they fight for you or their lord? 

\JOFFREY: For me. I'm their King. 

\CERSEI: But you've just invaded their homeland, asked them to kill their brothers. 

\JOFFREY: I'm not asking. 

\CERSEI: The North cannot be held$\ldots$ not by an outsider. It's too big and too wild. When the winter comes, the Seven gods together couldn't save you and your royal army. A good King knows when to save his strength$\ldots$ And when to destroy his enemies. 

\JOFFREY: So you agree$\ldots$ The Starks are enemies? 

\CERSEI: Everyone who isn't us is an enemy. 

\scene

\ti{KING'S LANDING - THE STARK LODGINGS}

\ti{\SANSA, \ARYA, and \SEPTAMORDANE ~are dining.  \ARYA ~is stabbing the table repeatedly}

\SEPTAMORDANE: Enough of that, young lady. Eat your food. 

\ARYA: I'm practicing. 

\SANSA: Practicing for what ? 

\ARYA: The Prince. 

\SEPTAMORDANE: Arya, stop ! 

\ARYA: He's a liar and a coward and he killed my friend. 

\SANSA: The Hound killed your friend. 

\ARYA: The Hound does whatever the Prince tells him to do. 

\SANSA: You're an idiot. 

\ARYA: You're a liar. And if you told the truth, Mycah would be alive. 

\SEPTAMORDANE: Enough! 

\ti{Enter \NED ~as \ARYA ~gets up to leave}

\NED: What's happening here ? 

\SEPTAMORDANE: Arya would rather act like a beast than a lady. 

\NED: Go to your room. We'll speak later. That's for you, love. The same dollmaker makes all of Princess Myrcella's toys. Don't you like it ? 

\SANSA: I haven't played with dolls since I was eight. May I be excused ? 

\SEPTAMORDANE: You've barely eaten a thing. 

\NED: It's all right. Go on. War was easier than daughters. 

\scene

\ti{KING'S LANDING - ARYA'S ROOM}

\sfx{Knocking}

\ti{\ARYA ~is practicing fencing}

\ARYA: Go away ! 

\NED: Arya, open the door. May I come in?  \sd{He enters} Whose sword is that ? 

\ARYA: Mine. 

\NED: Give it to me. I know this maker's mark. This is Mikken's work. Where did you get this ? This is no toy. Little ladies shouldn't play with swords. 

\ARYA: I wasn't playing. And I don't want to be a lady. 

\NED: Come here. Now what do you want with this ? 

\ARYA: It's called Needle. 

\NED: A blade with a name. And who were you hoping to skewer with Needle ? Your sister ? Do you know the first thing about sword fighting ? 

\ARYA: Stick 'em with the pointy end. 

\NED: That's the essence of it. 

\ARYA: I was trying to learn. I asked Mycah to practice with me. I asked him. It was my fault. 

\NED: No, sweet girl. You didn't kill the butcher's boy. 

\ARYA: I hate them ! I hate all of them. The Hound, the Queen and the King and Joffrey and Sansa. 

\NED: Sansa was dragged before the King and Queen$\ldots$ And asked to call the Prince a liar. 

\ARYA: So was I ! He is a liar. 

\NED: Darling, listen to me. Sansa will be married to Joffrey someday. She cannot betray him. She must take his side even when he's wrong. 

\ARYA: But how you can let her marry someone like that ? 

\NED: Look at me. You're a Stark of Winterfell. You know our words. 

\ARYA: Winter is coming. 

\NED: You were born in the long summer. You've never known anything else. But now winter is truly coming. And in the winter, we must protect ourselves, look after one another. Sansa is your sister. 

\ARYA: I don't hate her. Not really. 

\NED: I don't want to frighten you, but I won't lie to you either. We've come to a dangerous place. We cannot fight a war amongst ourselves. All right ? \sd{Handing the sword back to her} Go on. It's yours. 

\ARYA: I can keep it ? 

\NED: Try not to stab your sister with it. If you're going to own a sword, you'd better know how to use it. 

\scene

\ti{WINTERFELL - BRAN'S BEDSIDE}

\ti{\BRAN ~is in bed.  \OLDNAN ~by his bedside.  A crow flies past the window, cawing}

\OLDNAN: Don't listen to it. Crows are all liars. I know a story about a crow. 

\BRAN: I hate your stories. 

\OLDNAN: I know a story about a boy who hated stories. I could tell you about Ser Duncan the Tall. Those were always your favorites. 

\BRAN: Those weren't my favorites. My favorites were the scary ones. 

\OLDNAN: Oh, my sweet summer child. What do you know about fear ? Fear is for the winter, when the snows fall a hundred feet deep. Fear is for the long night, when the sun hides for years and children are born and live and die all in darkness. That is the time for fear, my little Lord, when the White Walkers move through the woods. Thousands of years ago there came a night that lasted a generation. Kings froze to death in their castles, same as the shepherds in their huts. And women smothered their babies rather than see them starve, and wept and felt the tears freeze on their cheeks. So is this the sort of story that you like ? In that darkness, the White Walkers came for the first time. They swept through cities and kingdoms, riding their dead horses, hunting with their packs of pale spiders big as hounds$\ldots$ 

\ti{Enter \ROBB}

\ROBB: What are you telling him now ? 

\OLDNAN: Only what the little Lord wants to hear. 

\ROBB: Get your supper. I want some time with him. One time she told me the sky is blue because we live inside the eye of a blue-eyed giant named Macomber. 

\BRAN: Maybe we do. 

\ROBB: How do you feel ? You still don't remember anything ? I've seen you climb a thousand times. In the wind, in the rain$\ldots$ A thousand times. You never fall. 

\BRAN: I did though. It's true, isn't it$\ldots$ what Maester Luwin says about my legs ? I'd rather be dead. 

\ROBB: Don't ever say that. 

\BRAN: I'd rather be dead. 

\scene

\ti{KING'S LANDING - THE BACK GATE}

\ti{\CATELYN ~and \RODRIK ~arrive at King's Landing}

\textbf{RODRIK}: Fewer eyes back here, my Lady. But still too many. 

\CATELYN: It's nine years since I've set foot in the capital. And no one knew who I was the last time I came either. 

\textbf{RODRIK}: My Lady. 

\GUARD: Welcome to King's Landing, Lady Stark. Would you mind following us ? 

\CATELYN: I would. We've done nothing wrong. 

\GUARD: We've been instructed to escort you into the city. 

\CATELYN: Instructed ? I don't know who's providing your instructions, but$\ldots$ 

\GUARD:\sd{handing her a letter, sealed with a mockingbird} Follow me, Lady Stark. 

\ti{They follow, and are brought to \LITTLEFINGER's brothel, where he is waiting}

\LITTLEFINGER: Cat!  

\CATELYN: You little worm ! You take me for some back-alley Sally you can drag into a$\ldots$ 

\LITTLEFINGER: I meant no disrespect to you of all people. 

\CATELYN: How dare you bring me here ! Have you lost your mind ? 

\LITTLEFINGER: No one will come looking for you here. Isn't that what like you wanted ? I'm truly sorry$\ldots$ about the locale. 

\CATELYN: How did you know I was coming to King's Landing ? 

\LITTLEFINGER: A dear friend told me. 

\ti{Enter \VARYS}

\VARYS: Lady Stark. 

\CATELYN: Lord Varys. 

\VARYS: To see you again after so many years is a blessing. Your poor hands. 

\CATELYN: How did you know I was coming ? 

\VARYS: Knowledge is my trade, my Lady. Did you bring the dagger with you, by any chance ? My little birds are everywhere. Even in the north. They whisper to me the strangest stories. Valyrian steel. 

\CATELYN: Do you know whose dagger this is ? 

\VARYS: I must admit I do not. 

\LITTLEFINGER: Well well, this is an historic day. Something you don't know that I do. There's only one dagger like this in all of the Seven Kingdoms. It's mine. 

\CATELYN: Yours ? 

\LITTLEFINGER: At least it was, until the tournament on Prince Joffrey's last nameday. I bet on Ser Jaime in the jousting, as any sane man would. When the Knight of the Flowers unseated him, I lost this dagger. 

\CATELYN: To whom ? 

\LITTLEFINGER: Tyrion Lannister. The Imp. 

\scene

\ti {THE WALL}

\ti{\GRENN ~and \JON ~are fighting with wooden swords surrounded by \ALLISER, \PYP, and \RAST.  \TYRION ~and \JEOR ~observe from above.   \JON ~makes short work of his opponent.}

\ALLISER: If that were a real sword, you'd be dead. Lord Snow here grew up in a castle spitting down on the likes of you. Pyp. Do you think Ned Stark's b*st*rd bleeds like the rest of us ? \sd{\PYP ~fights, and is equally quickly vanquished} Next ! \sd{\RAST ~meets a similar fate} Lord Snow, it appears you're the least useless person here. Go clean yourselves up. There's only so much I can stomach in a day. 

\ti{Exit \ALLISER}

\TYRION: A charming man. 

\JEOR: I don't need him to be charming. I need him to turn this bunch of thieves and runaways into men of the Night's Watch. 

\TYRION: And how's that going, Commander Mormont ? 

\JEOR: Slowly. A raven came for Ned Stark's son. 

\TYRION: Good news or bad ? 

\JEOR: Both. 

\ti{\TYRION ~descends towards the recruits}

\GRENN: You broke my nose, b*st*rd ! 

\JON: It's an improvement. 

\ti{\RAST ~grabs \JON's arms from behind and holds him, as \GRENN ~holds a knife to his throat}

\GRENN: If we threw you over the Wall, wonder how long it'd take you to hit. 

\PYP: I wonder if they'd find you before the wolves did. 

\GRENN: \sd{noticing \TYRION} What're you looking at, Half Man ? 

\TYRION: I'm looking at you. You've got an interesting face. Very distinctive faces. All of you. 

\RAST: What do you care about our faces ? 

\TYRION: It's just I think they would look marvellous decorating spikes in King's Landing. Perhaps I'll write my sister, the Queen, about it. 

\GRENN: We'll talk later, Lord Snow. 

\ti{Exit all but \JON ~and \TYRION}

\JON: Everybody knew what this place was and no one told me. No one but you. My father knew and left me to rot here at the Wall all the same. 

\TYRION: Grenn's father left him too$\ldots$ Outside a farmhouse when he was three. Pyp was caught stealing a wheel of cheese. His little sister hadn't eaten in three days. He was given a choice: his right hand or the Wall. I've been asking the Lord Commander about them. Fascinating stories. 

\JON: They hate me because I'm better than they are. 

\TYRION: It's a lucky thing none of them were trained by a master-at-arms like your Ser Rodrik. I don't imagine any of them have ever held a real sword before they came here. Your brother Bran. He's woken up. 

\scene {KING'S LANDING - THE THRONE ROOM}

\ti{PYCELLE enters to \NED}

\PYCELLE: Lord Stark. I meant to give you this earlier. So forgetful these days. A raven from Winterfell this morning. 

\ti{After handing him the letter, \PYCELLE ~exits, and as \NED ~is reading, \LITTLEFINGER ~enters}

\LITTLEFINGER: Good news? Perhaps you'd like to share it with your wife? 

\NED: My wife is in Winterfell. 

\LITTLEFINGER: Is she? 

\ti{They walk through the streets and arrive at his brothel}

\LITTLEFINGER: I thought that she'd be safest in here. One of several such establishments I own. 

\ti{\NED ~grabs him by the throat and shoves him against the wall.}

\NED: You're a funny man. A very funny man. 

\CATELYN: \sd{from a window} Ned! 

\ti{\NED ~lets go of \LITTLEFINGER ~and joins \CATELYN}

\LITTLEFINGER: \sd{aside} The Starks$\ldots$ Quick tempers, slow minds. 

\scene

\ti{Inside, a little later}

\LITTLEFINGER: The mere suggestion that the Queen's brother tried to kill your boy would be considered treason. 

\CATELYN: We have proof. We have the blade. 

\LITTLEFINGER: Which Lord Tyrion will say was stolen from him. The only man who could say otherwise has no throat, thanks to your boy's wolf. 

\CATELYN: Petyr has promised to help us find the truth. He's like a little brother to me. He would never betray my trust. 

\LITTLEFINGER: I'll try to keep you alive, for her sake. A fool's task, admittedly, but I've never been able to refuse your wife anything. 

\CATELYN: I won't forget this. You're a true friend. 

\LITTLEFINGER: Don't tell anyone. I have a reputation to maintain. 

\scene

\ti{KING'S LANDING - CERSEI'S CHAMBER}

\ti{\CERSEI ~and \JAIME ~have just heard about \BRAN ~waking}

\CERSEI: How could you be so stupid ? 

\JAIME: Calm down. 

\CERSEI: He's a child$\ldots$ 10 years old. What were you thinking? 

\JAIME: I was thinking of us. You're a bit late to start complaining about it now. What has the boy told them ? 

\CERSEI: Nothing. He's said nothing. He remembers nothing. 

\JAIME: Then what are you raving about? 

\CERSEI: What if it comes back to him? If he tells his father what he saw$\ldots$ 

\JAIME: We'll say he was lying. We'll say he was dreaming. We'll say whatever we like. I think we can outfox a 10-year-old. 

\CERSEI: And my husband? 

\JAIME: I'll go to war with him if I have to. They can write a ballad about us : "The War for Cersei's cunt." 

\ti{She slaps him, and he grabs hold of her, spinning her round to bring his lips to her ear.}

\CERSEI: Let me go. 

\JAIME: Never. 

\CERSEI: Let me go. 

\JAIME: The boy won't talk. And if he does, I'll kill him. Him, Ned Stark, the King$\ldots$ the whole bloody lot of them, until you and I are the only people left in this world. 

\scene

\ti{KING'S LANDING - BY THE BACK GATES}

\ti{\NED ~and \CATELYN ~are saying goodbye}

\CATELYN: I wish I could see the girls. 

\NED: It's too dangerous. 

\CATELYN: Just for a moment. 

\NED: Until we know who our enemies are$\ldots$ 

\CATELYN: I know they did it, Ned. The Lannisters. In my bones, I know it. 

\NED: Littlefinger's right. I can't do anything without proof. 

\CATELYN: And if you find the proof ? 

\NED: Then I bring it to Robert$\ldots$ And hope he's still the man I once knew. You watch yourself on the road, huh ? That temper of yours is a dangerous thing. 

\CATELYN: My temper? Gods be good, you nearly killed poor Littlefinger yesterday. 

\NED: He still loves you. 

\CATELYN: Does he? 

\NED: Off with you. 

\scene

\ti{KING'S LANDING - ROBERT'S CHAMBERS}

\ti{\ROBERT ~and \SELMY ~are chatting.  \LANCEL ~waits on \ROBERT}

\ROBERT: It's been a long time. But I still remember every face. You remember your first? 

\SELMY: Of course, your Grace. 

\ROBERT: Who was it? 

\SELMY: A Tyroshi. Never learned the name. 

\ROBERT: How'd you do it? 

\SELMY: Lance through the heart. 

\ROBERT: Quick one. Lucky for you. Mine was some Tarly boy at the Battle of Summerhall. My horse took an arrow so I was on foot, slogging through the mud. He came running at me, this dumb high-born lad, thinking he could end the rebellion with the single swing of his sword. I knocked him down with the hammer. Gods, I was strong then. Caved in his breastplate. Probably shattered every rib he had. Stood over him, hammer in the air. Right before I brought it down he shouted, ``Wait ! Wait.'' They never tell you how they all shit themselves. They don't put that part in the songs. Stupid boy. Now the Tarlys bend the knee like everyone else. He could have lingered on the edge of the battle with the smart boys and today his wife would be making him miserable, his sons would be ingrates, and he'd be waking three times in the night to piss into a bowl. Wine ! \sd{\LANCEL ~pours the last of the wine, but there's only a dribble} Lancel. Gods, what a stupid name. Lancel Lannister. Who named you ? Some halfwit with a stutter ? What are you doing ? 

\LANCEL: It's empty, your Grace. 

\ROBERT: What do you mean it's empty ? 

\LANCEL: There's no more wine. 

\ROBERT: Is that what empty means ? So get more. \sd{Exit \LANCEL} Tell your cousin to get in here. Kingslayer ! Get in here. \sd{Enter \JAIME} Surrounded by Lannisters. Every time I close my eyes I see their blond hair and their smug, satisfied faces. It must wound your pride, huh ? Standing out there like a glorified sentry. Jaime Lannister, son of the mighty Tywin$\ldots$ Forced to mind the door while your King eats and drinks and shits and fucks. So come on. We're telling war stories. Who was your first kill, not counting old men ? 

\JAIME: One of the outlaws in the Brotherhood. 

\SELMY: I was there that day. You were only a squire, 16 years old. 

\JAIME: You killed Simon Toyne with a counter riposte. Best move I ever saw. 

\SELMY: A good fighter, Toyne, but he lacked stamina. 

\ROBERT: Your outlaw$\ldots$ Any last words ? 

\JAIME: I cut his head off, so no. 

\ROBERT: What about Aerys Targaryen? What did the Mad King say when you stabbed him in the back? I never asked. Did he call you a traitor? Did he plead for a reprieve? 

\JAIME: He said the same thing he'd been saying for hours$\ldots$ "Burn them all." If that's all, your Grace$\ldots$ 

\scene

\ti{DOTHRAKI SEA}

\ti{\DAENERYS ~is riding alongside \JORAH}

\DAENERYS: Do the Dothraki buy their slaves? 

\JORAH: The Dothraki don't believe in money. Most of their slaves were given to them as gifts. 

\DAENERYS: From whom? 

\JORAH: If you rule a city and you see the horde approaching, you have two choices : pay tribute or fight. An easy choice for most. Of course, sometimes it's not enough. Sometimes a Khal feels insulted by the number of slaves he's given. He might think the men too weak or the women too ugly. Sometimes a Khal decides his riders haven't had a good fight in months and need the practice. 

\ti{DAENERYS sees a slave being savagely beaten, and seems disturbed.}

\DAENERYS: Tell them all to stop. 

\JORAH: You want the entire horde to stop? For how long? 

\DAENERYS: Until I command them otherwise. 

\JORAH: You're learning to talk like a Queen. 

\DAENERYS: Not a Queen. A Khaleesi. 

\JORAH: Annakhas dozgosores [Stop the horde.]

\ti{DAENERYS ~dismounts and is taking some time to herself in a clearing, when \VISERYS ~rides up, agitated.}

\VISERYS: You dare! You give commands to me? To me? \sd{He dismounts and grabs her by the throat} You do not command the dragon. I am Lord of the Seven Kingdoms. I don't take orders from savages or their sluts. Do you hear me? 

\ti{\RAKHARO ~comes up behind him and wraps his whip around his neck, pulling him away.}

\RAKHARO: Hash shafka zali addrivat mae, zhey Khaleesi?? [Do you want him dead khaleesi?]

\IRRI: Rakharo ask if you want him dead, Khaleesi. 

\DAENERYS: No ! 

\RAKHARO: Ishish chare acharoe hash me nem ejervae nharesoon. [Maybe the ear will listen if it is removed from the head.]

\IRRI: Rakharo say you should take ear, to teach respect. 

\DAENERYS: Please please, don't hurt him. Tell him I don't want my brother harmed. 

\IRRI: Khaleesi vos zalo meme nem vazzisa. [Khaleesi does not want him harmed.]

\ti{\RAKHARO ~releases him}

\VISERYS: \sd{to \JORAH, after getting his breath back} Kill these Dothraki dogs! I am your King! 

\JORAH: \sd{to \DAENERYS, ignoring \VISERYS} Shall we return to the Khalasar? 

\RAKHARO: \sd{to \VISERYS, leading his horse away} You walk. 

\scene

\ti{THE WALL}

\ti{\JON ~and \BENJEN ~are on top of the wall, looking North}

\BENJEN: I wanted to be here when you saw it for the first time. I'm leaving this morning. 

\JON: You're leaving ? 

\BENJEN: I'm the First Ranger. My job is out there. There have been disturbing reports. 

\JON: What kind of reports ? 

\BENJEN: The kind I don't want to believe. 

\JON: I'm ready. I won't let you down. 

\BENJEN: You're not going. You're no ranger, Jon. 

\JON: But I'm better than every other$\ldots$ 

\BENJEN: Better than no one ! Here, a man gets what he earns, when he earns it. We'll speak when I return. 

\scene

\ti{Elsewhere at the wall, but indoors, \YOREN ~and \TYRION ~are drinking}

\YOREN: A bear's balls. 

\TYRION: You're joking ? 

\YOREN: And his brains and his guts, his lungs and his heart all fried in his own fat. When you're a hundred miles north of the Wall and you ate your last meal a week ago, you leave nothing for the wolves. 

\TYRION: And how do a bear's balls taste ? 

\YOREN: A bit chewy. And what about you, my Lord ? What's the strangest thing you've eaten ? 

\TYRION: Do Dornish girls count ? So you roam the Seven Kingdoms, collaring pickpockets and horse thieves and bringing them here as eager recruits ? 

\YOREN: But it's not all of 'em's done bad things. Some of 'em's just poor lads looking for steady feed. Some of 'em's high-born lads looking for glory. 

\TYRION: They have a better chance finding feed than glory. 

\ti{Enter \BENJEN}

\BENJEN: The Night's Watch is a joke to you, is it ? Is that what we are, Lannister ? An army of jesters in black ? 

\TYRION: You don't have enough men to be an army and aside from Yoren here, none of you are particularly funny. 

\BENJEN: I hope we've provided you with some good stories to tell when you're back in King's Landing. But something to think about while you're drinking your wine down there, enjoying your brothels$\ldots$ Half the boys you've seen training will die north of the Wall. Might be a wilding's axe that gets them, might be sickness, might just be the cold. They die in pain. And they do it so plump little lords like you can enjoy their summer afternoons in peace and comfort. 

\TYRION: \sd{to \YOREN} Do you think I'm plump? Listen, Benjen$\ldots$ May I call you Benjen ? 

\BENJEN: Call me what you like. 

\TYRION: I'm not sure what I've done to offend you. I have great admiration for the Night's Watch. I've great admiration for you as First Ranger. 

\BENJEN: You know, my brother once told me that nothing someone says before the word "but'' really counts. 

\TYRION: But$\ldots$ I don't believe that giants and ghouls and White Walkers are lurking beyond the Wall. I believe that the only difference between us and the wildlings is that when that Wall went up, our ancestors happened to live on the right side of it. 

\BENJEN: You're right. The wildlings are no different from us. A little rougher maybe. But they're made of meat and bone. I know how to track them and I know how to kill them. It's not the wildlings giving me sleepless nights. You've never been north of the Wall, so don't tell me what's out there. \sd{He gets up to leave}

\YOREN: Are you going below ? Keep well, keep warm. 

\BENJEN: Enjoy the capital, brother. 

\YOREN: I always do. 

\ti{Exit \BENJEN}

\TYRION: I think he's starting to like me. Going below ? 

\YOREN: Into the tunnel and out the other side. He'll be north of the Wall for a month or two. 

\TYRION: So you're heading down to King's Landing too. 

\YOREN: Day after tomorrow. I get about half of my recruits from their dungeons. 

\TYRION: Let's share the road. I could use some decent company. 

\YOREN: I travel a bit on the grubby side, my Lord. 

\TYRION: Not this time. We'll be staying at the finest castles and inns. No one turns away a Lannister. 

\scene

\ti{DOTHRAKI SEA - DAENERYS' TENT}

\ti{\IRRI ~is plaiting \DAENERYS' hair}

\DAENERYS: At Jakah

\IRRI: Athjahakar [Pride, prowess]

\DAENERYS: At jahakar

\IRRI: Athjahakar

\DAENERYS: Athjahakar

\IRRI: Yes, Khaleesi. 

\ti{\IRRI ~starts feeling \DAENERYS's breasts}

\DAENERYS: What are you doing ? 

\IRRI: When was last time you bleed, Khaleesi ? You change, Khaleesi. Me azhasavva vezhofoon. [It's a blessing from the Great Stallion]. 

\scene

\ti{Outside the tent, \JORAH ~and \RAKHARO ~are talking}

\JORAH: For a man on horseback, the curved blade is a good thing, easier to handle. It's a good weapon for a Dothrakan. But a man in full plate, shori tawakof, the arakh won't get through the steel. That's where the broadsword has the advantage. Designed for piercing plate. 

\RAKHARO: Dothraki vos ondeo shoris tawakofi. [Dothraki don't wear steel dresses.]

\JORAH: Armor. 

\RAKHARO: Armor. Armor make a man$\ldots$ Vroz? 

\JORAH: Slow. 

\RAKHARO: Slow. 

\JORAH: It's true, but it also keeps a man alive. 

\RAKHARO: Ave anni ezzo anhaan os lajataan. Me ezzo anhaan m'athdikar assie athzhokwazar. [My father taught me how to fight. He taught me that speed defeats size.]

\JORAH:  Anha ray char m'ave yeri lajakoon hakeso. [I've heard that your father was a famous warrior.]

\RAKHARO: Me dothrakhqoyoon torga Khali Bharbo.[He was bloodrider to Khal Bharbo.] Majin ave yeri Jorah Andahli? Hash me lajakoon akka?  [And your father, Jorah the Andal ? He was a warrior also?]

\JORAH: He still is. A man of great honor. And I betrayed him. 

\ti{Enter \IRRI ~from the tent}

\IRRI:  Khaleesi zala meme adakha esinakh ajjalan. Ogi loy mawizzi.[The Khaleesi wants to eat something different tonight. Kill some rabbits.]

\RAKHARO: Vo mawizzi vekho jinne. [There are no rabbits.]

\IRRI: Ezas loy alegri h'anhaan. Mori allayafi mae, jin alegra. [Find some ducks, she likes ducks.]

\RAKHARO:  Hash yer ray tih loy alegri zhey vikeesi? Vo mawizzi, vo alegri. Hash tihi vekhi she nhare yeroon? Hash tih? [Have you seen any ducks, woman ? No rabbits, no ducks. Do you have eyes in your head ? Do you ?] 

\IRRI: Majin jano. Anha ray tih san jani. [Dog then. I have seen many dogs. ]

\JORAH: I don't think she wants to eat dog. 

\IRRI: The Khaleesi have baby inside her. It is true. She does not bleed for two moons. Her belly start to swell. 

\RAKHARO: Azhasavva vezhofoon. [A blessing from the Great Stallion. ]

\IRRI: She does not want to eat horse. 

\JORAH: I'll have the boys butcher a goat for supper. I need to ride to Qohor. 

\RAKHARO: We ride for Vaes Dothrak. 

\JORAH: Don't worry. I'll catch you. The horde's easy to find. 

\scene

\ti{DROGO'S TENT}

\ti{\DROGO ~and \DAENERYS~ are embracing}

\DAENERYS: Me rakh. [It's a boy.] 

\DROGO: Kifinosi yer nesi? [How do you know?] 

\DAENERYS: Anha sekke nesa. [I very knows].

\scene

\ti{THE WALL}

\ti{In the yard, \JON ~is helping the other recruits train.  Above, \TYRION, \AEMON, and \JEOR ~are talking}

\JON: Don't stand so still. It's harder to hit a moving target. \sd{to \PYP} Except for you. You move too much. I could just hold my sword out and let you do the work for me. 

\AEMON: How many winters have you seen, Lord Tyrion ? 

\TYRION: Eight$\ldots$ no, nine. 

\AEMON: All of them brief ? 

\TYRION: They say the winter of my birth was three years long, Maester Aemon. 

\AEMON: This summer has lasted nine. But reports from the Citadel tell us the days grow shorter. The Starks are always right eventually : winter is coming. This one will be long and dark things will come with it. 

\JEOR: We've been capturing wildlings, more every month. They're fleeing south. The ones who flee$\ldots$ say they've seen the White Walkers. 

\TYRION: Yes, and the fishermen of Lannisport say they see mermaids. 

\JEOR: One of our own rangers swore he saw them kill his companions. He swore it right up to the moment Ned Stark chopped his head off. 

\AEMON: The Night's Watch is the only thing standing between the realm and what lies beyond. And it has become an army of undisciplined boys and tired old men. There are less than a thousand of us now. We can't man the other castles on the Wall. We can't properly patrol the wilderness. We've barely enough resources to keep our lads armed and fed. 

\JEOR: Your sister sits by the side the King. Tell her we need help. 

\AEMON: When winter does come, gods help us all if we're not ready. 

\ti{Exit all but \TYRION ~and \JON.  A little later, \TYRION ~is about to leave}

\JON: I'm sorry to see you leave, Lannister. 

\TYRION: It's either me or this cold. And it doesn't appear to be going anywhere. 

\JON: Will you stop at Winterfell on your way South ? 

\TYRION: I expect I will. Gods know there aren't many feather beds between here and King's Landing. 

\JON: If you see my brother Bran, tell him I miss him. Tell him I'd visit if I could. 

\TYRION: Of course. 

\JON: He'll never walk again. 

\TYRION: If you're going to be a cripple, it's better to be a rich cripple. Take care, Snow. 

\JON: Farewell, My Lord. 

\scene

\ti{KING'S LANDING - A COURTYARD}

\ti{\ARYA ~enters to \SYRIO, who is holding two wooden swords}

\SYRIO: You are late, boy. Tomorrow you will be here at midday. 

\ARYA: Who are you ? 

\SYRIO: Your dancing master, Syrio Forel. \sd{He throws one sword, which she grabs for and misses} Tomorrow you will catch it. Now pick it up. \sd{She does so, holding it in both hands} That is not the way, boy. This is not a great sword that is needing two hands to swing it. 

\ARYA: It's too heavy. 

\SYRIO: It is heavy as it needs to be to make you strong. Just so. One hand is all that is needed. Now you are standing all wrong. Turn your body sideface. So. You are skinny. That is good. The target is smaller. Now the grip$\ldots$ Let me see. The grip must be delicate. 

\ARYA: What if I drop it ? 

\SYRIO: The steel must be part of your arm. Can you drop part of your arm ? No. Nine years Syrio Forel was first sword to the Sealord of Braavos. He knows these things. You must listen to me, boy. 

\ARYA: I'm a girl. 

\SYRIO: Boy, girl$\ldots$ You are a sword, that is all. That is the grip. You are not holding a battle-axe. You are holding$\ldots$ 

\ARYA: A needle. 

\SYRIO: Just so. Now we will begin the dance. Remember, child, this is not the dance of the Westeros we are learning$\ldots$ The knight's dance, hacking and hammering. This is the Bravo's dance$\ldots$ The water dance. It is swift and sudden. All men are made of water, do you know this ? If you pierce them, the water leaks out and they die. Now you will try to strike me. \sd{\ARYA tries, and fails repeatedly} Dead. Dead. Very dead. Come. Again, faster. 

\ti{They continue to spar, as \NED ~watches, proud but concerned}

\end{document}
