\input{preamble}
\input{ep05_cast}
\title{Episode 5 (S1E5): The Wolf and The Lion}
\author{}
\date{}
\maketitle

\input{ep05_casttable}


\scene

\textit{KING'S LANDING: SER HUGH OF THE VALE'S TENT} 

\ti{\NED ~and \SELMY ~are conversing over the body of \textbf{SER HUGH}.}

\NED: Does Ser Hugh have any family in the capital? 

\SELMY: No. I stood vigil for him myself last night. He had no one else. 

\NED: He'd never worn this armour before. 

\SELMY: Bad luck for him, going against the Mountain. 

\NED: Who determines the draw? 

\SELMY: All the knights draw straws, Lord Stark. 

\NED: Aye, but who holds the straws?

\SELMY: Life is strange. Not so many years ago we fought as enemies at the Trident. 

\NED: I'm glad we never met on the field, Ser Barristan. As is my wife. I don't think the widow's life would suit her. 

\SELMY: You're too modest. I've seen you cut down a dozen great knights. 

\NED: My father once told me you were the best he'd ever seen. I never knew the man to be wrong about matters of combat. 

\SELMY: He was a fine man, your father. What the Mad King did to him was a terrible crime. 

\NED: And that lad. He was a squire until a few months ago. How could he afford a new suit of armour? 

\SELMY: Perhaps Lord Arryn left him some money? I hear the King wants to joust today. 

\NED: Yes. That will never happen. 

\SELMY: Robert tends to do what he wants. 

\NED: If the King got what he wanted all the time, we'd still be fighting a damned rebellion. 


\scene

\textit{THE KING'S TENT} 

\ti{\NED ~enters \ROBERT'S tent. Inside, \LANCEL ~is attempting to dress him.}

\LANCEL: It's made too small, Your Grace. It won't go. 

\ROBERT: Your mother was a dumb whore with a fat ass. Did you know that? Look at this idiot! One ball and no brains. He can't even put a man's armour on him properly. 

\NED: You're too fat for your armour. 

\ROBERT: Fat? Fat, is it? Is that how you speak to your King? \sd{\ROBERT ~and \NED ~laugh. To \LANCEL ~(who is grinning)} That was funny, was it? 

\LANCEL: No, Your Grace. 

\ROBERT: No? You don't like the Hand's joke? 

\NED: You're torturing the poor boy. 

\ROBERT: You heard the Hand. The King's too fat for his armour! Go find the breastplate stretcher -- now! 

\ti{\LANCEL ~leaves}

\NED: The breastplate stretcher? 

\ROBERT: How long before he figures it out? 

\NED: Maybe you should have one invented. 

\ROBERT: All right, all right. But you watch me out there. I still know how to point a lance. 

\NED: You have no business jousting. Leave that for the young men. 

\ROBERT: Why? Because I'm king? Piss on that. I want to hit somebody! 

\NED: And who's going to hit you back? 

\ROBERT: Anybody who can. And the last man in his saddle $\dots$

\NED: Will be you! There's not a man in the Seven Kingdoms would risk hurting you. 

\ROBERT: Are you telling me those cowards would let me win? 

\NED: Aye. 

\ti{\ROBERT ~pours \NED ~a drink and offers it to him.}

\ROBERT:  Drink. 

\NED: I'm not thirsty. 

\ROBERT: Drink. Your King commands it. Gods! Too fat for my armour. 

\NED: Your squire. A Lannister boy? 

\ROBERT: A bloody idiot, but Cersei insisted. I have Jon Arryn to thank for her. "Cersei Lannister will make a good match'', he told me. "You'll need her father on your side.'' I thought being King meant I could do whatever I wanted. Enough of this! Let's go watch `em ride. At least I can smell someone else's blood.  

\ti{The king rises and starts to leave the tent.}

\NED: Robert? 

\ROBERT: What? \sd{Looking down, King Robert sees his belly protruding from his jacket} Oh! An inspiring sight for the people, eh? Come! Bow before your King! Bow, you shits! 

\scene

\textit{THE TOURNEY GROUNDS} 

\ti{Cheering crowds line both sides of the jousting track as The \MOUNTAIN ~rides down the lane, stops in front of the King's stand, opens his helmet and bows. \NED, \SANSA, \LITTLEFINGER ~and \RENLY ~sit a little way from the king.}

\NED: Where's Arya 

\SANSA: At her dancing lessons.  

\ti{\SANSA ~looks up and sees \LORAS ~who rides up and hands her a rose, but his eyes are on \RENLY.}

\SANSA: Thank you, Ser Loras. 

\ti{\LORAS ~rides over and joins his opponent, the \MOUNTAIN, in front of the King's stand. The \MOUNTAIN's horse becomes skittish and both men ride off in opposite directions toward the ends of the jousting track.}

\SANSA: \ti{(to NED)} Don't let Ser Gregor hurt him. 

\NED: Hey. 

\SANSA: I can't watch. He's going to die. 

\NED: Ser Loras rides well. 

\LITTLEFINGER: \sd{To \RENLY.} A hundred gold dragons on the Mountain. 

\RENLY: I'll take that bet. 

\LITTLEFINGER: Now what will I buy with a hundred. gold dragons? A dozen barrels of Dornish wine? Or a girl from the pleasure houses of Lys? 

\RENLY: Or you could even buy a friend. 

\ti{The trumpet sounds and both jousters ride toward one another. \LORAS' lance breaks upon the \MOUNTAIN's shield and knocks him down to the ground. \RENLY ~jumps up laughing and clapping.}

\RENLY: Such a shame, Littlefinger. It would have been so nice for you to have a friend. 

\LITTLEFINGER: And tell me, Lord Renly, when will you be having your friend? \sd{To Ned.} Loras knew his mare was in heat. Quite crafty, really. 

\SANSA: Ser Loras would never do that! There's no honour in tricks. 

\LITTLEFINGER: No honour but quite a bit of gold. 

\ti{The \MOUNTAIN ~rises from the ground, rips off his helmet and grabs his sword and with one mighty stroke, severs his horse's head. Shocked, the crowd grows quiet. Then he storms over to \LORAS, knocks him off of his horse and strikes with his sword. \LORAS' shield protects him from the blows.} 

\HOUND: Leave him be!

\ti{Drawing his own sword, the \HOUND ~jumps down from the King's stand and engages his brother in a sword fight.} 

\ROBERT: Stop this madness in the name of your King! 

\ti{The \HOUND ~drops to his knee and bows his head, while the MOUNTAIN's blade slices the air where his head was just seconds ago. He throws down his sword and stomps off through the crowd. \LORAS ~approaches the \HOUND.}

\LORAS: I owe you my life, Ser. 

\HOUND: I'm no Ser. 

\ti{\LORAS ~grabs the \HOUND's left hand with his right and raises both in the air to the cheers of a standing ovation.}

\scene

\textit{THE EASTERN ROAD} 

\ti{\CATELYN, \TYRION, \RODRIK, \BRONN, \MARILLION, ~and \STARKSOLDIER ~take a rest stop along the way to The Vale. \RODRIK ~roughly pulls a hooded and tied \TYRION ~from his horse.}

\CATELYN: Remove his hood. 

\ti{\RODRIK ~yanks the hood off of \TYRION ~and pushes him along while, \MARILLION ~strums his lute and sings until \TYRION ~comes face-to-face with \CATELYN.}

\MARILLION: \sd{Singing.}

On that eve, the captive Imp\\
Downwards from his horse did limp,\\
No more would he preen and primp,\\
In garb of red and gold. 

\TYRION: This isn't the Kings Road. You said we were riding for Winterfell. 

\CATELYN: I did.  Often and loudly. 

\TYRION: Very wise. They'll be out in droves, looking for me in the wrong place. Word's probably gotten to my father by now. He'll be offering a handsome reward. Everyone knows a Lannister always pays his debts. Would you be so good as to untie me? 

\CATELYN: And why would I do that? 

\TYRION: Why not? Am I going to run? The hill tribes would kill me for my boots. Unless a shadowcat ate me first. 

\CATELYN: Shadowcats and hill tribes are the least of your concerns. 

\TYRION: Ah $\ldots$ the Eastern Road. We're going to The Vale. You're taking me to your sister's to answer for my imagined crimes. Tell me, Lady Stark. When was the last time you saw your sister? 

\CATELYN: Five years ago. 

\TYRION: She's changed. She was always a bit touched, but now $\ldots$ you might as well kill me here. 

\CATELYN: I am not a murderer, Lannister. 

\TYRION: Neither am I! I had nothing to do with the attempt on your son's life! 

\CATELYN: The dagger found--

\TYRION: What sort of imbecile arms an assassin with his own blade? 

\RODRIK: Should I gag him? 

\TYRION: Why? Am I starting to make sense? 

\ti{Suddenly, a shot rings out and a \textbf{STARK SOLDIER} falls to the ground. \textbf{BANDITS}, brandishing axes, swords and slinging rocks, swoop in on them from all sides. \RODRIK ~grabs \CATELYN ~and guides her to a safer spot.}

\RODRIK: My Lady, this way. 

\ti{\TYRION ~watches the small intense battle as throats are slit and heads bashed in. He sees \CATELYN ~pull out a small dagger and rushes over to her.}

\TYRION: Untie me. If I die, what's the point? 

\ti{\CATELYN ~cuts \TYRION's bonds. He looks around and grabs a shield and holds it up just in time to avoid a well-aimed rock. He looks back toward \CATELYN ~and sees she's under attack, then runs over and batters the attacker with the shield. Once the attacker is down, \TYRION ~repeatedly drives the shield's edge into the man's face and neck, killing him and saving \CATELYN. The fight ends; many are dead.}

\CATELYN: Rodrik? 

\RODRIK: I'll be fine, My Lady. There's no need to bloody yourself. 

\ti{\BRONN ~sheaths his sword and walks over to \TYRION.}

\BRONN: Your first? You need a woman. Nothing like a woman after a fight. 

\TYRION: \sd{Looking at Catelyn.} Well, I'm willing if she is. 


\scene

\textit{WINTERFELL} 

\ti{\THEON ~is practicing his archery skills. \BRAN ~and \LUWIN ~are seated at a table behind \THEON. \BRAN ~is supposed to be studying but he can't keep his eyes off \THEON's target practice.}

\BRAN: The Iron Islands. Sigil -- a Kraken. Words, `We do not sow'. 

\LUWIN: Lords? 

\BRAN: The Greyjoys. 

\THEON: Famed for their skills at archery, navigation and lovemaking. 

\LUWIN: And failed rebellions. 

\ti{\LUWIN ~taps on the papers in front of them.}

\BRAN: Sigil. A stag. A crowned stag now that Robert's King. 

\LUWIN: Good. 

\BRAN: Words. `Ours is the fury'. Lords. The Baratheons. 

\LUWIN: Mm -- hmm. 

\BRAN: The Westerlands. Sigil. A lion. Words. `A Lannister always pays his debts'. 

\LUWIN: No. A common saying, but not their official motto. 

\BRAN: Lords. The Lannisters. 

\LUWIN: We're still on their words. 

\BRAN: I don't know them. 

\LUWIN: You do know them. Think. 

\BRAN: `Unbowed, unbent, unbroken'. 

\LUWIN: That's House Martell. 

\BRAN: `Righteous in wrath'.

\LUWIN: House Hornwood. 

\BRAN: `Family, duty, honour'. 

\LUWIN: Those are Tully words. Your mother's. Are we playing a game? 

\BRAN: `Family, duty, honour'.  Is that the right order? 

\LUWIN: You know it is. 

\BRAN: Family comes first? 

\LUWIN: Your mother had to leave Winterfell to protect the family. 

\BRAN: How can she protect the family, if she's not with her family? 

\LUWIN: Your mother sat by your bed for three weeks while you slept. 

\BRAN: And then she left! 

\LUWIN: When you were born, I was the one who pulled you from your mother. I placed you in her arms. From that moment until the moment she dies, she will love you. Absolutely. Fiercely. 

\BRAN: Why did she leave? 

\LUWIN: I still can't tell you, but she will be home soon. 

\BRAN: Do you know where she is now? Today? 

\LUWIN: No, I don't. 

\BRAN: Then how can you promise me she'll be home soon? 

\LUWIN: Sometimes I worry you're too smart for your own good. 

\BRAN: I'll never shoot another arrow. 

\LUWIN: And where is that written? 

\BRAN: You need legs to work a bow. 

\LUWIN: If the saddle Lord Tyrion designed actually works, you could learn to shoot a bow from horseback. 

\BRAN: Really? 

\LUWIN: Dothraki boys learn when they're four years old. Why shouldn't you? 

\scene

\textit{WINTERFELL: THEON'S QUARTERS} 

\ti{\THEON ~and \ROS ~have been fucking.}

\THEON: Shh. Keep it down. You're not supposed to be inside the castle walls. 

\ti{\THEON ~moves away and \ROS ~walks over a dresser and sits in front of the mirror.}

\ROS: I thought you were supposed to be an important person around here. 

\THEON: Important enough for the likes of you. 

\ROS: You're not the only nobleman in my life, you know. 

\THEON: Who? the Imp? I'd call him half a nobleman. 

\ROS: Jealous?

\THEON: Why should I be jealous? 

\ti{\THEON ~walks over and stands directly behind \ROS.}

\THEON: Anyone with a few coppers in his pocket can own you for the night. What's a dwarf like down below? I've always wondered. 

\ROS: Might surprise you. 

\THEON: Hmm? 

\ROS: He's good with his fingers too. And his tongue. 

\THEON: Generous tipper. I guess gold is cheap for a Lannister. 

\ROS: You are jealous. 

\THEON: I'm a Greyjoy. We've been Lords of the Iron Islands for three hundred years. There's not a family in Westeros that can look down on us, not even the Lannisters. 


\scene

\textit{KING'S LANDING: NED'S CHAMBERS} 

\ti{\NED ~is seated at his desk and watches \VARYS ~as he walks around securing the windows and doors before sitting down for a private conversation.}

\VARYS: How is your son, My Lord? 

\NED: He'll never walk again. 

\VARYS: But his mind is sound? 

\NED: So they say. 

\VARYS: A blessing then. I suffered an early mutilation myself. Some doors close forever.  Others open in the most unexpected places.  May I? \sd{\VARYS ~indicates a chair and with a nod from \NED, sits down.}

\VARYS: If the wrong ears heard what I'm about to tell you, off comes my head. And who would mourn poor Varys then? North or South, they sing no songs for spiders. But there are things you must know. You are the King's Hand and the King is a fool. Your friend, I know, but a fool, and doomed unless you save him. 

\NED: I've been in the capital a month. Why have you waited so long to tell me this? 

\VARYS: I didn't trust you. 

\NED: So why do you trust me now? 

\VARYS: The Queen is not the only one who has been watching you closely. There are few men of honour in the capital. You are one of them. I would like to believe I am another, strange as that may seem. 

\NED: What sort of doom does the King face? 

\VARYS: The same sort as Jon Arryn. The tears of Lys, they call it. A rare and costly thing, as clear and tasteless as water. It leaves no trace. 

\NED: Who gave it to him? 

\VARYS: Some dear friend, no doubt. But which one? There were many. Lord Arryn was a kind and trusting man. There was one boy.  All he was he owed to Jon Arryn. 

\NED: The squire, Ser Hugh? 

\VARYS: Pity what happened to him, just when his life seemed to be going so nicely. 

\NED: If Ser Hugh poisoned him, who paid Ser Hugh? 

\VARYS: Someone who could afford it. 

\NED: Jon was a man of peace. He was Hand for 17 years. Seventeen good years. Why kill him? 

\VARYS: He started asking questions. 


\scene

\textit{KING'S LANDING: A CORRIDOR} 

\ti{\ARYA ~chases a cat along the castle hallways.}

\ARYA: Come on. I'm not going to hurt you. 

\ti{She chases the cat through the dungeons of the Red Keep. She stops suddenly and stares at a statue of a huge dragon's skull. As she explores, she hears two men approach. Quickly, she hides within the dragon's open jaws and listens. The men are Lord \VARYS ~and Magister \ILLYRIO ~Mopatis.}

\VARYS: He's found one bastard already. He has the book. The rest will come. 

\ILLYRIO: And when he knows the truth, what will he do? 

\VARYS: The gods alone know. The fools tried to kill his son. What's worse, they botched it.  The wolf and the lion will be at each other's throats. We will be at war soon, my friend. 

\ILLYRIO: What good is war now? We're not ready. If one Hand can die, why not a second? 

\VARYS: This Hand is not the other. 

\ILLYRIO: We need time. Khal Drogo will not make his move until his son is born. You know how these savages are. 

\VARYS: `Delay,' you say. `Move fast,' I reply. This is no longer a game for two players. 

\ILLYRIO: It never was. 

\ti{\ARYA ~watches as the men leave. She emerges from the dragon's jaws and runs to the gate, only to find it locked. She runs off in another direction.}


\scene

\textit{KING'S LANDING: THE THRONE ROOM} 

\ti{\LITTLEFINGER ~stands staring up at the Iron Throne when \VARYS ~enters the room.}

\VARYS: The first to arrive and the last to leave. I admire your industry. 

\LITTLEFINGER: You do move quietly. 

\VARYS: We all have our qualities. 

\LITTLEFINGER: You look a bit lonely today. You should pay a visit to my brothel this evening. First boy is on the house. 

\VARYS: I think you're mistaking business with pleasure. 

\LITTLEFINGER: Am I? All those birds that whisper in your ear.  Such pretty little things. Trust me, we accommodate all inclinations. 

\VARYS: Oh, I'm sure. Lord Redwyne likes his boys very young, I hear. 

\LITTLEFINGER: I'm a purveyor of beauty and discretion -- both equally important. 

\VARYS: Though I suppose beauty is a subjective quality, no? Is it true that Ser Marlon of Tumblestone prefers amputees? 

\LITTLEFINGER: All desires are valid to a man with a full purse. 

\VARYS: And I heard the most awful rumor about a certain lord with a taste for fresh cadavers. Must be enormously difficult to accommodate that inclination. The logistics alone, to find beautiful corpses before they rot. 

\LITTLEFINGER: Strictly speaking, such a thing would not be in accordance with the King's laws. 

\VARYS: Strictly speaking. 

\LITTLEFINGER: Tell me. Does someone, somewhere, keep your balls in a little box? I've often wondered. 

\VARYS: Do you know, I have no idea where they are? And we had been so close. But enough about me. How have you been since we last saw each other? 

\LITTLEFINGER: Since you last saw me or since I last saw you? 

\VARYS: Now the last time I saw you, you were talking to the Hand of the King. 

\LITTLEFINGER: Saw me with your own eyes? 

\VARYS: Eyes I own. 

\LITTLEFINGER: Council business. We all have so much to discuss with Ned Stark. 

\VARYS: Everyone's well aware of your enduring fondness for Lord Stark's wife. If the Lannisters were behind the attempt on the Stark boy's life and it was discovered that you helped the Starks come to that conclusion. To think a simple word to the Queen $\ldots$ 

\LITTLEFINGER: One shudders at the thought. 

\VARYS: Ooh. `Shudders'. 

\LITTLEFINGER: But you know something? I do believe that I have seen you even more recently than you have seen me. 

\VARYS: Have you? 

\LITTLEFINGER: Yes. Earlier today, I distinctly recall seeing you talking to Lord Stark in his chambers. 

\VARYS: Was that you under the bed? 

\LITTLEFINGER: And not long after that when I saw you escorting a certain foreign dignitary. Council business? Of course you would have friends from across The Narrow Sea. You're from there yourself, after all. We're friends, aren't we, Lord Varys? I'd like to think we are. So you can imagine my burden, wondering if the King might question my friend's sympathies -- to stand at a crossroads where turning left means loyalty to a friend, turning right -- loyalty to the realm. 

\VARYS: Oh, please. 

\LITTLEFINGER: To find myself in a position where a simple word to the King-- 

\ti{\RENLY  barges into the throne room.}

\RENLY: What are you two conspiring about? Well, whatever it is, you'd best hurry up. My brother is coming. \sd{Exits} 

\LITTLEFINGER: To a small council meeting? 

\VARYS: Disturbing news from far away. Haven't you heard? 

\scene

\textit{KING'S LANDING: CASTLE GATES} 

\ti{\ARYA ~emerges from a tunnel outside the castle walls. She makes her way to the entrance of the castle, but is stopped by two guards.}

\GUARDa: Off with you. No begging. 

\ARYA: I'm not a beggar. I live here. 

\GUARDa: D'you want a smack on your ear to help you with your hearing? 

\ARYA: I want to see my father. 

\GUARDb: I want to fuck the Queen, for all the good it does me. 

\GUARDa: You want your father, boy? He's lying on the floor of some tavern, getting pissed on by his friends. 

\ARYA: My father is Hand of the King! I'm not a boy. I'm Arya Stark of Winterfell and if you lay a hand on me, my father will have both your heads on spikes! Now are you going to let me by or do I need to smack you on the ear to help with your hearing? 


\scene

\textit{KING'S LANDING: NED'S CHAMBERS} 

\ti{\NED ~is talking to \ARYA.}

\NED: You know I had half my guard out searching for you? You promised me this would stop. 

\ARYA: They said they were going to kill you. 

\NED: Who did? 

\ARYA: I didn't see them, but I think one was fat. 

\NED: Oh, Arya. 

\ARYA: I'm not lying! They said you found the bastard and the wolves are fighting the lions and the savage $\ldots$ something about the savage. 

\NED: Where did you hear this? 

\ARYA: In the dungeons, near the dragon skulls. 

\NED: What were you doing in the dungeons? 

\ARYA: Chasing a cat. 

\ti{\JORY ~knocks and then enters.}

\JORY: Pardon, My Lord. There's a Night's Watchman here begging a word. He says it's urgent. ) 

\ti{\NED ~nods, \YOREN ~enters.}

\NED: Your name, friend? 

\YOREN: Yoren, if it please. This must be your son. He has the look. 

\ARYA: I'm a girl! 

\NED: Did Benjen send you? 

\YOREN: No one sent me, My Lord. I'm here to find men for The Wall, see if there's any scum in the dungeons that might be fit for service. 

\NED: Ah, we'll find recruits for you. 

\YOREN: Thank you, My Lord. But that's not why I disturb you now. Your brother, Benjen, his blood runs black, makes him as much my brother as yours. It's for his sake I rode here so hard I damn near killed my horse! There are others riding too. The whole city will know by tomorrow. 

\NED: Know what? 

\YOREN: Best said in private, My Lord. 

\NED: \sd{to \ARYA} Go on. We'll talk more later. Jory, take her safely to her room. 

\JORY: Come along, My Lady. You heard your father. 

\ti{\JORY ~and \ARYA ~exit the chambers and walk down the hall.}

\ARYA: How many guards does my father have? 

\JORY: Here in King's Landing? Fifty. 

\ARYA: You wouldn't let anyone kill him, would you? 

\JORY: No fear on that count, little Lady. 

\ti{\NED ~closes the door to talk privately with YOREN.}

\NED: Well? 

\YOREN: It's about your wife, My Lord. She's taken the Imp. 

\ti{KINGS LANDING: COURTYARD}

\ti{The Royal \STEWARD ~hails \NED ~as he strides purposefully along a walk.}

\STEWARD: Lord Stark, your presence has been requested in the small council chamber. A meeting has been called. 

\NED: I need to see the King first -- alone. 

\STEWARD: The King is at the small council meeting, My Lord. He has summoned you. 

\NED: Is it about my wife? 

\STEWARD: No, My Lord. I believe it concerns Daenerys Targaryen. 


\scene

\textit{KING'S LANDING: THE SMALL COUNCIL CHAMBER} 

\ti{\NED ~is standing and facing  \ROBERT, \RENLY, \LITTLEFINGER, \VARYS ~AND \PYCELLE ~who are seated at the table.}

\ROBERT: The whore is pregnant. 

\NED: You're speaking of murdering a child. 

\ROBERT: I warned you this would happen. Back in the North, I warned you, but you didn't care to hear. Well, hear it now. I want `em dead, mother and child both, and that fool, Viserys as well. Is that plain enough for you? I want them both dead. 

\NED: You will dishonour yourself forever if you do this. 

\ROBERT: Honour?! I've got Seven Kingdoms to rule! One King, Seven Kingdoms. Do you think honour keeps them in line? Do you think it's honour that's keeping the peace? It's fear,fear and blood. 

\NED: Then we're no better than the Mad King. 

\ROBERT: Careful, Ned. Careful now. 

\NED: You want to assassinate a girl because the Spider heard a rumor? 

\VARYS: No rumor, My Lord. The princess is with child. 

\NED: Based on whose information? 

\VARYS: Ser Jorah Mormont. He is serving as adviser to the Targaryens. 

\NED: Mormont? You bring us the whispers of a traitor half a world away and call it fact? 

\LITTLEFINGER: Jorah Mormont's a slaver, not a traitor. Small difference, I know, to an honourable man. 

\NED: He broke the law, betrayed his family, fled our land. We commit murder on the word of this man? 

\ROBERT: And if he's right? If she has a son? A Targaryen at the head of a Dothraki army. What then? 

\NED: The Narrow Sea still lies between us. I'll fear the Dothraki the day they teach their horses to run on water. 

\ROBERT: Do nothing? That's your wise advice? Do nothing till our enemies are on our shores? You're my council. Counsel! Speak sense to this honourable fool. 

\VARYS: I understand your misgivings, My Lord. Truly, I do. It is a terrible thing we must consider, a vile thing. Yet, we who presume to rule must sometimes do vile things for the good of the realm. Should the gods grant Daenerys a son, the realm will bleed. 

\PYCELLE: I bear this girl no ill will, but should the Dothraki invade, how many innocents will die? How many towns will burn? Is it not wiser, kinder even, that she should die now so that tens of thousands might live? 

\RENLY: We should have had them both killed years ago. 

\LITTLEFINGER: When you find yourself in bed with an ugly woman, best close your eyes, get it over with. Cut her throat. Be done with it. 

\NED: I followed you into war -- twice -- without doubts, without second thoughts. But I will not follow you now. The Robert I grew up with didn't tremble at the shadow of an unborn child. 

\ROBERT: She dies. 

\NED: I will have no part in it. 

\ROBERT: You're the King's Hand, Lord Stark. You'll do as I command or I'll find me a hand who will. 

\ti{\NED ~removes the pin signifying his position as Hand of the King and tosses it onto the table in front of King \ROBERT.}

\NED: And good luck to him. I thought you were a better man. 

\ROBERT: Out! Out, damn you! I'm done with you.  Go! Run back to Winterfell! I'll have your head on a spike! I'll put it there myself, you fool! You think you're too good for this? Too proud and honourable? This is a war!


\scene

\ti{KING'S LANDING: THE HAND'S CHAMBERS}

\ti{\NED ~is quickly packing his belongings when \JORY ~enters his room.}

\NED: I'll go ahead with my daughters. Get them ready. Do it yourself. Don't ask anyone for help. 

\JORY: Right away, My Lord. Lord Baelish is here for you. 

\ti{Enter \LITTLEFINGER.}

\LITTLEFINGER: His Grace went on about you at some length after you took your leave. The word `treason' was mentioned. 

\NED: What can I do for you? 

\LITTLEFINGER: When do you return to Winterfell? 

\NED: Why? What do you care? 

\LITTLEFINGER: If you're still here come nightfall, I'll take you to see the last person Jon Arryn spoke with before falling ill. If that sort of thing still interests you. 

\NED: I don't have the time. 

\LITTLEFINGER: It won't take more than an hour. But as you please. 

\ti{\LITTLEFINGER ~turns and walks out into the hall, but he doesn't get very far before \NED ~grabs his sword and gives \JORY ~some last orders before joining him.}

\NED: Round up all the men we have and station them outside the girls' chambers. Who are your best two swords? 

\JORY: Heward and Wyl. 

\NED: Find them and meet me at the stables. 



\scene

\textit{THE VALE} 

\ti{A short distance from The Eyrie, \CATELYN ~Stark's party is met by a group of armed guards from The Vale.}

\VARDIS: You're far from home, Lady Stark. 

\CATELYN: To whom do I speak? 

\VARDIS: Ser Vardis Egan, Knight of The Vale. Is Lady Arryn expecting your visit? 

\CATELYN: There was no time to send word. 

\VARDIS: May I ask, My Lady, why he is with you? 

\CATELYN: That's why there was no time. He is my prisoner. 

\VARDIS: He doesn't look like a prisoner. 

\CATELYN: My sister will decide what he looks like. 

\VARDIS: Yes, My Lady. She will at that. 

\ti{The Eyrie guards turn and head back to the castle. \CATELYN's party follows their escorts.}

\TYRION: The Eyrie. They say it's impregnable. 

\BRONN: Give me ten good men and some climbing spikes I'll impregnate the bitch. 

\TYRION: I like you. 

\scene

\textit{THE EYRIE: THE THRONE ROOM} 

\ti{\LYSA ~sits high upon her throne. Her seven-year-old son, \ROBYN, still breast feeding, sits on her lap. \CATELYN, \TYRION, and \VARDIS ~ stand in the hall, looking up at \LYSA.}

\LYSA: You bring him here without permission? You pollute my home with his presence? \sd{To Robyn.} Your aunt has done a bad thing, Robyn, a very bad thing. You remember her, don't you? \sd{To Catelyn.} Isn't he beautiful? And strong too. Jon knew it. His last words were, `the seed is strong.' He wanted everyone to know what a good, strong boy his son would grow up to be. Look at him, the Lord of all the Vale. 

\CATELYN: Lysa, you wrote me about the Lannisters, warning me to--

\LYSA: To stay away from them! Not to bring one here! 

\ROBYN: Mummy? Is that the bad man? 

\LYSA: It is. 

\ROBYN: He's little. 

\LYSA: He's Tyrion the Imp of house Lannister. He killed your father. He murdered the Hand of the King! 

\TYRION: Oh? Did I kill him too? I've been a very busy man. 

\LYSA: You will watch your tongue! These men are knights of the Vale. Every one of the loved John Arryn. Every one of them would die for me. 

\TYRION: If any harm comes to me, my brother, Jaime, will see that they do. 

\ROBYN: You can't hurt us! No one can hurt us here! Tell him, mommy! Tell him! 

\LYSA: Shh. Shh. Shh, my sweet boy. He's just trying to frighten us. Lannisters are all liars. No one will hurt my baby. 

\ROBYN: Mummy! I want to see the bad man fly. 

\LYSA: Perhaps you will, my little love. 

\CATELYN: This man is my prisoner. I will not have him harmed. 

\LYSA: Ser Vardis, my sister's guest is weary. Take him down below so he can rest. Introduce him to Mord. 

\ti{'Down below', \MORD ~throws \TYRION ~into his cell.}

\MORD: You go sleep, dwarf man. Sleep good, little dwarf man! 

\ti{\TYRION ~surveys his three-walled cell. Open sky greets him where the fourth wall should be. The floor slants toward the opening. \TYRION ~carefully walks over to the edge and looks down at the ground far far far below.}

\scene

\textit{KING'S LANDING: RENLY'S CHAMBERS} 

\ti{\RENLY ~is seated in a chair, topless, and \LORAS ~is kneeling beside him, preparing to shave his chest.}

\LORAS: Lord Stark's lucky he still has a head. 

\RENLY: Robert will rant for a few days, but he won't do anything. He adores the man. 

\LORAS: You're jealous! 

\RENLY: Are you sure this won't hurt? 

\LORAS: Only if I slip. 

\RENLY: And you prefer me like this? 

\LORAS: Hm -- mmm ...

\RENLY: If you want hairless, maybe you should find a little boy. 

\LORAS: I want you. 

\RENLY: My brother thinks that anyone who hasn't been to war isn't a man. He treats me as if I'm a spoiled child. \sd{Off \LORAS' look.} Oh, and you're not? Loras Tyrell, the Knight of the Flowers? How many wars have you fought in? Oh, and how much did your father spend on that armour of yours? 

\LORAS: Hold still. 

\RENLY: All I ever hear from Robert and Stannis is how I'm not tough enough, how I squirm at the sight of blood. 

\LORAS: You did vomit when that boy's eye was knocked out in the melee. 

\RENLY: His eye was dangling out of the damn socket! 

\LORAS: He shouldn't have entered the melee if he didn't know how to fight. 

\RENLY: Easy for you to say. Not everyone is such a gifted swordsman. 

\LORAS: It's not a gift. No one gave it to me. I'm good because I work at it -- every day of my life since I could hold a stick. 

\RENLY: I could work at fighting all day, every day, and still never be as good as you. 

\LORAS: Yes well, I guess we'll never know. 

\ti{\LORAS ~wipes \RENLY's chest off and then raises \RENLY's ~arm to shave underneath it.}

\RENLY: Everywhere? 

\LORAS: Everywhere. So how did it end up? The Targaryen girl will die? 

\RENLY: It needs to be done, unpleasant as it is. Robert's rather tasteless about it. Every time he talks about killing her, I swear the table rises six inches. 

\LORAS: It's a shame he can't muster the same enthusiasm for his wife. 

\RENLY: He does have a deep, abiding lust for her money. You have to give it to the Lannisters. They may be the most pompous, ponderous cunts the gods ever suffered to walk the world, but they do have outrageous amounts of money. 

\LORAS: I have an outrageous amount of money. 

\RENLY: Not as much as the Lannisters. 

\LORAS: But a lot more than you. 

\RENLY: Robert's threatening to take me hunting with him. Last time we were out there for two weeks.  Tramping through the trees in the rain, day after day. All so he can stick his spear into something's flesh! Oh. but Robert loves his killing. And he's the King. 

\LORAS: Hmm.  How did that ever happen? 

\RENLY: Because he loves his killing and he used to be good at it. 

\LORAS: Do you know who should be King? 

\RENLY: Be serious. 

\LORAS: I am. My father could be your bank. I've never fought in a war before, but I'd fight for you. 

\RENLY: I'm fourth in line. 

\LORAS: And where was Robert in the line of royal succession? Joffrey is a monster. Tommen is eight. 

\RENLY: Stannis? 

\LORAS: Stannis has the personality of a lobster. 

\RENLY: He's still my older brother. 

\ti{\LORAS ~slices a small cut in \RENLY's side.}

\RENLY: What are you doing?! 

\LORAS: Look at it. 

\RENLY: You cut me! 

\LORAS: It's just blood. We've all got it in us. Sometimes a little spills. If you become King, you're going to see a lot of this. You need to get used to it. Go on. Look. People love you. They love to serve you because you're kind to them. They want to be near you. 

\ti{\LORAS ~rises and taking \RENLY ~by the hand, has him stand up as well.}

\LORAS: You're willing to do what needs to be done, but you don't gloat over it. You don't love killing. Where is it written that power is the sole province of the worst? That thrones are only made for the hated and the feared. You would be a wonderful King. 

\ti{\LORAS ~kneels down in front of \RENLY, and unfastens his pants $\ldots$}

\scene

\textit{KING'S LANDING: ROBERT'S CHAMBERS} 

\ti{\ROBERT ~is seated at his desk when \CERSEI ~enters.}

\CERSEI: I'm sorry your marriage to Ned Stark didn't work out. You seemed so good together. 

\ROBERT: I'm glad I could do something to make you happy. 

\CERSEI: Without a Hand, everything will fall to pieces. 

\ROBERT: I suppose this is where you tell me to give the job to your brother Jaime. 

\CERSEI: No. He's not serious enough. I'll say this for Ned Stark.  He's serious enough. Was it really worth it? Losing him this way? 

\ROBERT: I don't know. But I do know this.  If the Targaryen girl convinces her horselord husband to invade and the Dothraki horde crosses The Narrow Sea, we won't be able to stop them. 

\CERSEI: The Dothraki don't sail. Every child knows that. They don't have discipline. They don't have armour. They don't have siege weapons. 

\ROBERT: It's a neat little trick you do.  You move your lips and your father's voice comes out. 

\CERSEI: Is my father wrong? 

\ROBERT: Let's say Viserys Targaryen lands with forty thousand Dothraki screamers at his back. We hole up in our castles, a wise move. Only a fool would meet the Dothraki in an open field. They leave us in our castles. They go from town to town, looting and burning, killing every man who can't hide behind a stone wall, stealing all our crops and livestock, enslaving all our women and children. How long do the people of the Seven Kingdoms stand behind their absentee King, their cowardly King hiding behind high walls? When do the people decide that Viserys Targaryen is the rightful monarch after all. 

\CERSEI: We still outnumber them. 

\ROBERT: Which is the bigger number, five or one? 

\CERSEI: Five. 

\ROBERT: \sd{Holding up one hand with fingers spread, one in a fist.} Five $\ldots$ one. One army, a real army, united behind one leader with one purpose. Our purpose died with the Mad King. Now we've got as many armies as there are men with gold in their purse. And everybody wants something different. Your father wants to own the world. Ned Stark wants to run away and bury his head in the snow. 

\CERSEI: What do you want? 

\ROBERT: We haven't had a real fight in nine years. Back-stabbing doesn't prepare you for a fight. And that's all the realm is now. Back-stabbing and scheming and arse-licking and money-grubbing. Sometimes I don't know what holds it together. 

\CERSEI: Our marriage. 

\ti{King \ROBERT ~develops a hearty laugh as \CERSEI ~starts laughing as well.}

\ROBERT: Ah, so here we sit, seventeen years later, holding it all together. Don't you get tired? 

\CERSEI: Every day. 

\ROBERT: How long can hate hold a thing together? 

\CERSEI: Well, seventeen years is quite a long time. 

\ROBERT: Yes, it is. 

\CERSEI: Yes, it is. What was she like? 

\ROBERT: You've never asked about her, not once. Why not? 

\CERSEI: At first, just saying her name, even in private felt like I was breathing life back into her. I thought if I didn't talk about her, she'd just fade away for you. When I realized that wasn't going to happen, I refused to ask out of spite. I didn't want to give you the satisfaction of thinking I cared enough to ask. And eventually it became clear that my spite didn't mean anything to you, as far as I could tell, you actually enjoyed it. 

\ROBERT: So why now? 

\CERSEI: What harm could Lyanna Stark's ghost do to either of us that we haven't done to each other a hundred times over? 

\ROBERT: You want to know the horrible truth? I can't even remember what she looked like. I only know she was the one thing I ever wanted.  Someone took her away from me, and Seven Kingdoms couldn't fill the hole she left behind. 

\CERSEI: I felt something for you once, you know? 

\ROBERT: I know. 

\CERSEI: Even after we lost our first boy. For quite a while, actually. Was it ever possible for us? Was there ever a time, ever a moment? 

\ROBERT: No. Does that make you feel better or worse? 

\CERSEI: It doesn't make me feel anything. 


\scene

\textit{KING'S LANDING: LITTLEFINGER'S BROTHEL} 

\ti{\NED ~is in a room with \MHAEGEN, a prostitute and mother of King \ROBERT's illegitimate daughter, who she is holding. In an adjoining room, separated by a curtain of metal hoops, \LITTLEFINGER ~reclines on a sofa. \JORY ~stands opposite the sofa, next to the curtained doorway.}

\MHAEGEN: She looks like him, don't she, My Lord? She has his nose, his black hair. 

\NED: Aye. 

\MHAEGEN: Tell him when you see him, My Lord. If it please you $\ldots$ tell him how beautiful she is. 

\NED: I will. 

\MHAEGEN: And tell him I've been with no one else. I swear it, My Lord, by the old gods and new. I don't want no jewels or nothing, just him. The King was always good to me. 

\NED: When Jon Arryn came to visit you, what did he want? 

\MHAEGEN: He wasn't that sort of man, My Lord. He just wanted to know if the child was happy $\ldots$ healthy. 

\NED: She looks healthy enough to me. The girl shall want for nothing. 

\ti{\NED ~leaves the room through the curtain and joins \LITTLEFINGER ~in the adjoining room.}

\LITTLEFINGER: Brothels make a much better investment than ship, I've found. Whores rarely sink. 

\NED: What do you know of King Robert's bastards? 

\LITTLEFINGER: Well, he has more than you, for a start. 

\NED: How many? 

\LITTLEFINGER: Does it matter? If you fuck enough women, some of them will give you presents. 

\NED: And Jon Arryn tracked them all down. Why? 

\LITTLEFINGER: He was the King's Hand. Perhaps Robert wanted them looked after. He was overcome with fatherly love. 

\NED: \sd{To \JORY.} Come. 

\JORY: My Lord. 

\ti{\NED ~and \JORY ~exit the brothel and are swiftly surrounded by \textbf{LANNISTER GUARDS}. \JAIME ~rides up on horseback.}

\JAIME: Such a small pack of wolves. 

\JORY: Stay back, Ser! This is the Hand of the King! 

\JAIME: Was the Hand of the King. Now I'm not sure what he is. Lord of somewhere very far away. 

\LITTLEFINGER:  What's the meaning of this, Lannister? 

\JAIME: Get back inside where it's safe. I'm looking for my brother. You remember my brother, don't you, Lord Stark? Blond hair, sharp tongue, short man. 

\NED: I remember him well. 

\JAIME: It seems he had some trouble on the road. You wouldn't know what happened to him, would you? 

\NED: He was taken at my command to answer for his crimes. 

\ti{\JAIME ~draws his sword as his men start to move forward. They are stopped when \LITTLEFINGER ~steps up.}

\LITTLEFINGER: My Lords! I'll bring the City Watch! \sd{Exit.}

\JAIME: Come, Stark. I'd rather you die sword in hand. 

\JORY: If you threaten My Lord again-- 

\JAIME: Threaten? As in, `I'm going to open your Lord from balls to brains and see what Starks are made of'? 

\NED: You kill me, your brother's a dead man. 

\JAIME: You're right. \sd{To his men.} Take him alive! Kill his man! 

\ti{A short but fierce fight breaks out between the men. \JAIME ~kills \JORY, then duels with \NED ~while his guards watch. Their sword fight is brought to an abrupt end when one of the guards spears the back of \NED's leg, bringing him to his knees. Angry, \JAIME ~approaches the offending guard and knocks him out.}

\JAIME: My brother, Lord Stark $\ldots$ we want him back. 

\ti{\JAIME ~Lannister rides away as \NED ~Stark falls to his back on the ground.}

\end{document}
