\input{preamble}
\input{ep06_cast}
\title{Episode 6 (S1E6): A Golden Crown}
\author{}
\date{}
\maketitle

\input{ep06_casttable}


\scene

\textit{KING'S LANDING: NED'S CHAMBERS} 

\ti{\NED ~is lying on a bed. He wakes head to see \CERSEI ~and \ROBERT ~in front of him.}

\NED: Your pardon, your Grace. I would rise, but $\ldots$ 

\CERSEI: Do you know what your wife has done? 

\NED: She did nothing I did not command. 

\ROBERT: Who'd have thought she had it in her? 

\CERSEI: By what right dare you lay hands on my blood? 

\NED: I am the King's Hand, charged with keeping the peace $\ldots$ 

\CERSEI: You were the King's Hand. You shall now be held accountable. 

\ROBERT: Will both of you shut your mouths!? Catelyn will release Tyrion and you'll make your peace with Jaime. 

\NED: He butchered my men $\ldots$ 

\CERSEI: Lord Stark was returning drunk from a brothel when his men attacked Jaime. 

\ROBERT: Quiet, woman. 

\NED: Jaime has fled the city. Give me leave to bring him back to justice. 

\CERSEI: I took you for a king. 

\ROBERT: Hold your tongue. 

\CERSEI: He's attacked one of my brothers and abducted the other. I should wear the armour and you the gown. 

\ti{Robert slaps her.}

\CERSEI: I shall wear this like a badge of honour. 

\ROBERT: Wear it in silence or I'll honour you again. 

\ti{Exit \CERSEI.}

\ROBERT: See what she does to me? My loving wife. I should not have hit her. That was not $\ldots$ that was not kingly. 

\NED: If we don't act, there will be a war. 

\ROBERT: So tell your wife to return that little shit of an Imp to King's Landing. She's had her fun, now put an end to it. You hear me? Send a raven and put an end to it. 

\NED: And what about Jaime Lannister? What about Jaime? 

\ROBERT: I'm half a kingdom in debt to his bloody father! I don't know what happened between you and those yellow-haired shits. I don't want to know. This is what matters $\ldots$ I can't rule the Kingdoms if the Starks and the Lannisters are at each other's throats. So enough. 

\NED: As you command, your Grace. With your leave, I will return to Winterfell and set matters straight. 

\ROBERT: Piss on that. Send a raven. I want you to stay. I'm the King. I get what I want $\ldots$ I never loved my brothers. A sad thing for a man to admit, but it's true. You were the brother I chose. We'll talk when I return from the hunt. \sd{He throws the `hand's badge' at him}

\NED: The hunt?

\ROBERT: Killing things clears my head. You'll have to sit on the throne while I'm away. You'll hate it more than I do. 

\NED: The Targaryen girl?

\ROBERT: Seven hells! don't start with her again. The girl will die and I'll hear no more of it. Put on the badge. And if you ever take it off again, I swear to the Mother I'll pin the damned thing on Jaime Lannister. 


\scene

\textit{DAENERYS' TENT} 

\ti{\DAENERYS ~is holding a dragon egg. She stands up and walks towards a pot with rocks and fire burning beneath them. She places the egg on the rocks, kneels down and stares at it. \IRRI ~enters the room holding a basket.}

\IRRI: Khaleesi? 

\ti{\DAENERYS ~picks the egg up. \IRRI ~drops the basket and runs to her.}

\IRRI: Khaleesi! 

\ti{She takes the egg from \DAENERYS ~and throws it to the floor. She turns DAENERYS' hands to reveal her palms, unburnt. She looks at her, unbelieving. \DAENERYS ~turns \IRRI's hands to reveal her palms red.}

\DAENERYS: You're hurt. 


\scene

\n Bran dreams. A raven caws. Bran stands, aiming a bow. The bird flies away, and he follows it through a candle lit archway leading to the crypts. It lands on a wolf statue and caws again, then flies away, further into the crypt.

\scene

\textit{WINTERFELL: THE WOODS} 

\ti{\BRAN ~is riding, ignoring the others. \ROBB ~and \THEON ~are sitting on a bench nearby.}

\BRAN: Woohoo! 

\ROBB: Not too fast. 

\BRAN: Come on, Dancer. 

\THEON: When are you gonna tell him? 

\ROBB: Not now. 

\THEON: Blood for blood. 

\BRAN: Come on! 

\THEON: You need to make the Lannisters pay for Jory and the others. 

\ROBB: You're talking about war. 

\BRAN: Woooohoo! 

\THEON: I'm talking about justice. 

\ROBB: Only the Lord of Winterfell can call in the bannermen and raise an army. 

\THEON: A Lannister put his spear through your father's leg. The Kingslayer rides for Casterly Rock where no one can touch him $\ldots$ 

\BRAN: Woooohoo! 

\ROBB: You want me to march on Casterly Rock? 

\THEON: You're not a boy anymore. They attacked your father. They've already started the war. It's your duty to represent your House when your father can't. 

\BRAN: Come on, Dancer. 

\ti{\BRAN ~rides out of sight.}

\ROBB: And it's not your duty, because it's not your House. Where's Bran? 

\THEON: I don't know. It's not my House. 

\ti{Away from \ROBB ~and \THEON, \BRAN ~rides Dancer, slowly, deeper in the woods. He hears a sound and turns his head looking for what it is. \OSHA ~moves behind some shrubs, not far from him. He turns his head again, trying to spot something. She comes out from behind him, with three \textbf{WILDLINGS}. They approach him.}

\BRAN: Robb? 

\OSHA: All alone in the deep, dark woods. 

\BRAN: I'm not alone. My brother is with me. 

\WILDLINGa: I don't see him. Got him hidden under your cloak? 

\OSHA: That's a pretty pin. Silver. 

\WILDLINGa: We'll take the pin and the horse. Get down. Be quick about it. 

\BRAN: I can't. The saddle $\ldots$ the straps. 

\ti{The second wildling moves \BRAN's cloak to reveal straps on his leg.}

\WILDLINGa: What's wrong with you? You some kind of cripple? 

\BRAN: I'm Brandon Stark of Winterfell! If you don't let me be, I'll have you all killed! 

\ti{\WILDLINGa ~draws a knife and starts cutting the straps.}

\WILDLINGb: Cut his little cock off and stuff it in his mouth. 

\OSHA: The boy's worth nothing dead. Benjen Stark's own blood? Think what Mance would give us. 

\WILDLINGa: Piss on Mance Rayder, and piss on the North. We're going as far South as South goes. There ain't no White Walkers down in Dorne. 

\ti{\ROBB comes up behind them, holding a sword.}

\ROBB: Drop the knife. Let him go and I'll let you live. 

\ti{They fight. \ROBB ~kills \textbf{WILDLINGS} 2 and 3, and knocks \OSHA ~to the ground, but \WILDLINGa ~manages to grab \BRAN, and holds a knife to his throat.}

\BRAN: Robb! Robb! 

\WILDLINGa: \sd{To \BRAN.} Shut up! \sd{To \ROBB.} Drop the blade! 

\BRAN: No, don't. 

\WILDLINGa: Do it. 

\ti{\ROBB ~and the WILDLING stare at each other. \ROBB ~slowly places the blade on the ground.}

\ti{\WILDLINGa ~gasps suddenly. An arrow has pierced his chest. He falls down to reveal \THEON ~behind him, holding a bow. He draws another arrow, and points it at \OSHA. \ROBB ~goes to \BRAN.}

\ROBB: Are you all right? 

\BRAN: Yes. It doesn't hurt. 

\THEON: Tough little lad. In the Iron Islands, you're not a man until you've killed your first enemy. Well done. 

\ROBB: Have you lost your mind? What if you'd missed? 

\THEON: He would have killed you and cut Bran's throat. 

\ROBB: You don't have the right $\ldots$ 

\THEON: To what, to save your brother's life? It was the only thing to do, so I did it. 

\ROBB: What about her? 

\OSHA: Give me my life, my Lord, and I'm yours. 

\ROBB: We'll keep her alive. 


\scene

\textit{THE VALE OF ARRYN: SKY CELLS} 

\ti{\TYRION awakens and turns, rolling down, towards the edge of the steep floor. He stops, looking down at the misty atmosphere below, then backs away hurriedly towards the door.}

\TYRION: Mord! Turnkey! Mord! 

\ti{The door opens. \MORD ~comes in.}

\MORD: Dwarf man making noise! 

\ti{He hits \TYRION, making him back away until his back is against the wall.}

\TYRION: How would you like to be rich? 

\MORD: \sd{Hitting \TYRION ~again.} Dwarf man still making noise. 

\TYRION: My family is rich. We have gold, lots of gold. I'm prepared to give you lots of gold in-- 

\ti{\MORD ~searches \TYRION's pockets.}

\MORD: No gold! 

\TYRION: Well, I don't have it here. 

\MORD:  No gold. fuck off. 

\ti{\MORD ~leaves, locking the door.}


\scene

\textit{KING'S LANDING: TRAINING ROOM} 

\ti{\SYRIO ~closes the door and turns, with two wooden swords in hand, to walk up to \ARYA. He throws her a sword and makes a dancing stance, a foot away from her.}

\ARYA: I don't want to practice today. 

\SYRIO: No? 

\ARYA: They killed Jory. My father is hurt. I don't care about stupid wooden swords. 

\SYRIO: You are troubled. 

\ARYA: Yes. 

\SYRIO: Good! Trouble is the perfect time for training. When you are dancing in the meadow with your dolls and kittens, this is not when fighting happens. 

\ARYA: I don't like dolls and kittens

\ti{He swipes her arm with his sword.}

\SYRIO: You're not here. You're with your trouble. If you are with your trouble when fighting happens $\ldots$ 

\ti{He steps back as she advances. She parries, then he turns, around her sword, to be right in front of her, causing her to fall. She gets up and they continue.}

\SYRIO: More trouble for you. Just so. How can you be quick as a snake $\ldots$ or as quiet as a shadow $\ldots$ when you are somewhere else?

\ti{SYRIO disarms ARYA, catches her sword, and holds it to her neck.}

\SYRIO: You are fearing for your father. That is right. Do you pray to the gods? 

\ARYA: The old and the new. 

\SYRIO: There is only one God and his name is Death. And there is only one thing we say to Death. Not today. 

\ti{The practice continues.}


\scene

\textit{VAES DOTHRAK} 

\ti{\DAENERYS ~is holding a bloody heart surrounded by Dothraki warriors chanting. She sinks her teeth in, bites a chunk out, and chews it. \DROGO ~is in front of her. \VISERYS ~and \JORAH ~are off to one side.}

\VISERYS: She has to eat the whole heart? I hope that wasn't my horse. 

\ti{\DAENERYS ~continues to eat. A \PRIESTESS ~in front of her chants, moving her arms in the air.}

\JORAH: She's doing well. 

\VISERYS: She'll never keep it down. Indicating the priestess. Tell me what she's saying. 

\JORAH: The prince is riding. I have heard the thunder of his hooves. Swift as the wind he rides. His enemies will cower before him. And their wives will weep tears of blood. She's going to have a boy. 

\VISERYS: He won't be a real Targaryen. He won't be a true Dragon. 

\ti{\DAENERYS ~eats the last chunk of the heart as the \PRIESTESS ~continues to sing. She chokes and drops, one hand on the ground, the other on her mouth. She almost vomits. Then swallows the heart. \DROGO ~smiles at her.}

\PRIESTESS: Khalakka dothrae! Vezh fin saja rhaesheseres! [The prince rides. The stallion that mounts the world!] 

\JORAH: The stallion who mounts the world. The stallion is the Khal of Khals. He shall unite the people into a single Khalasar. All the people of the world will be his herd. 

\DAENERYS: Khalakka dothrae mr'anha. Ma me nem ahakee ma Rhaego! [A Prince rides inside me! And he shall be called Rhaego!] 

\CROWD: Rhaego! Rhaego! Rhaego! Rhaego! 

\VISERYS: They love her. 

\ti{\DROGO ~walks to her and lifts her up, his arms wrapped around her waist, and carries her around the platform. The \CROWD ~encircles her.}

\CROWD: Rhaego! Rhaego! Rhaego! Rhaego! 

\JORAH: She truly is a queen today. \sd{He looks beside him, but \VISERYS ~is gone.} 

\CROWD: Rhaego! Rhaego! Rhaego! Rhaego! 


\scene

\textit{DAENERYS' TENT} 

\ti{\VISERYS ~opens the chest of dragon eggs. Kneeling down, he heaves a sigh, then puts one inside a bag. As he reaches for the second, \JORAH ~enters the tent. He stands up, a quarter of his sword unsheathed, and turns.}

\JORAH: Don't let them see you carrying a sword in Vaes Dothrak. You know the law. 

\VISERYS: It's not my law 

\JORAH: They don't belong to you. 

\VISERYS: Whatever is hers is also mine. 

\JORAH: Once, perhaps. 

\VISERYS: If I sell one egg, I'll have enough to buy a ship. Two eggs, a ship and an army. 

\JORAH: And you have all three. 

\VISERYS: I need a large army. I'm the last hope of a dynasty, Mormont. The greatest dynasty this world has ever seen on my shoulders since I was five years old. And no-one has ever given me what they gave to her in that tent. Never. Not a piece of it. How can I carry what I need to carry without it? Who can rule without wealth or fear or love? You stand there, all nobility and honour. You don't think I see you looking at my little sister? Don't think I know what you want?. I don't care. You can have her. She can be Queen of the savages, and dine on the finest bloody horseparts, and you can dine on whichever parts of her you like. But let me go. 

\JORAH: You can go. You can't have the eggs. 

\VISERYS: You swore an oath to me. Does loyalty mean nothing to you? 

\JORAH: It means everything to me. 

\VISERYS: And yet here you stand. 

\JORAH: And yet here I stand. 

\ti{\VISERYS ~drops the bag and leaves the tent.}


\scene

\textit{THE VALE: SKY CELLS} 

\ti{\TYRION's hands are against the doo.r}

\TYRION: Mord! $\ldots$ Mord! $\ldots$ Mord! $\ldots$ Mord! 

\ti{As the door opens, \TYRION ~backs away. \MORD ~enters and hits him, causing him to fall.}

\MORD: Noise again! 

\TYRION: About the gold-- 

\MORD: No gold! No gold. 

\TYRION: Listen to me! Listen to me. Sometimes possession is an abstract concept. When they captured me they took my purse, but the gold is still mine. 

\MORD: Where? 

\TYRION: Where? I don't know where, but when they free me--

\MORD: You want free? \sd{Pointing outside.} Go be free. 

\TYRION: Have you ever heard the phrase `Rich as a Lannister'? Of course you have! You're a smart man. You know who the Lannisters are. I am a Lannister. Tyrion, son of Tywin! And of course, you have also heard the phrase, `A Lannister always pays his debts.' If you deliver a message from me to Lady Arryn, I will be in your debt. I will owe you gold. If you deliver the message and I live, which I very much intend to do. 

\MORD: What message? 

\TYRION: Tell her I wish to confess my crimes. 


\scene

\textit{THE VALE: THE COURT} 

\ti{\TYRION ~kneels in front of \LYSA. \ROBYN ~and \CATELYN ~are beside her. \textbf{KNIGHTS}, \VARDIS ~and \BRONN ~look on.}

\LYSA: You wish to confess your crimes? 

\TYRION: Yes my Lady. I do, my Lady. 

\LYSA: The sky cells always break them. Speak, Imp. Meet your Gods as an honest man. 

\TYRION: Where do I begin, my Lords and Ladies? I'm a vile man, I confess it. My crimes and sins are beyond counting. I have lied and cheated, gambled and whored. I'm not particularly good at violence, but I'm good at convincing others to do violence for me. You want specifics, I suppose. When I was seven, I saw a servant girl bathing in the river. I stole her robe. She was forced to return to the castle naked and in tears. If I close my eyes, I can still see her tits bouncing. When I was 10, I stuffed my Uncle's boots with goatshit. When confronted with my crime, I blamed a squire. Poor boy was flogged and I escaped justice. When I was 12, I milked my eel into a pot of turtle stew. I flogged the one-eyed snake. I skinned my sausage. I made the bald man cryy into the turtle stew, which I do believe my sister ate, at least I hope she did. I once brought a jackass and a honeycomb into a brothel.

\LYSA: Silence! 

\ROBYN: What happened next? 

\LYSA: What do you think you're doing? 

\TYRION: Confessing my crimes. 

\CATELYN: Lord Tyrion, You are accused of hiring a man to slay my son Bran in his bed, and of conspiring to murder my sister's husband Lord Jon Arryn, the Hand of the King. 

\TYRION: I'm very sorry. I don't know anything about all that. 

\LYSA: You've had your little joke. I trust you enjoyed it. Mord! Take him back to the dungeon. But this time find a smaller cell, with a steeper floor. 

\TYRION: Is this how justice is done in the Vale? You accuse me of crimes, I deny them, so you throw me into a cell to freeze and starve? Where is the King's justice? I am accused and demand a trial! 

\LYSA: If you're tried and found guilty, then by the King's own laws you will pay with your life. 

\TYRION: I understand the law. 

\LYSA: We have no executioner in the Eyrie. Life is more elegant here. Open the Moon Door. 

\ti{Two \textbf{KNIGHTS} walk to a wheel and turn it. \ROBYN ~giggles as a round door on the ground opens.}

\LYSA: You want a trial, my Lord Lannister. Very well. My son will listen to whatever you have to say, and you will hear his judgment. Then you will leave $\ldots$ By one door or the other. 

\TYRION: No need to bother Lord Robyn. I demand a trial by combat. 

\LYSA: You have that right. 

\KNIGHTa: I beg the honour. Let me be your champion. 

\KNIGHTb: The honour should be mine. For the love I bore your Lord husband, let me avenge his death. 

\KNIGHTc: I'll fight for you. 

\KNIGHTd: It'll be my honour. 

\KNIGHTe: The honour should be mine. 

\ROBYN: Make the bad man fly! 

\LYSA: Ser Vardis. You're quiet. Don't you want to avenge my husband? 

\VARDIS: With all my heart, my Lady. But the Imp is half my size. It would be shameful to slaughter such a man and call it justice. 

\TYRION: Agreed. 

\LYSA: You demanded a trial by combat. 

\TYRION: Now I demand a champion. I have that right, same as you. 

\VARDIS: I will gladly fight the Imp's champion, for you. 

\TYRION: I wouldn't be too glad, Ser. I name my brother Jaime Lannister. 

\LYSA: The Kingslayer is hundreds of miles from here. 

\TYRION: Send a raven for him. I'm happy to wait. 

\LYSA: The trial will be today. 

\TYRION: Do I have a volunteer? Anyone? Anyone? 

\LYSA: I think we can assume that no one is willing $\ldots$ 

\BRONN: I'll stand for the dwarf. 

\scene

\textit{THE VALE: COURT} 

\ti{\VARDIS ~and \BRONN ~get ready to fight.}

\ROBYN: Fight!

\ti{They fight. \VARDIS ~is pressing forward, whilst \BRONN ~dodges and hides behind pillars.}

\LYSA: Stand and fight, coward! 

\ti{The battle continues, and \BRONN ~scores the first blow.}

\TYRION: Yes! 

\LYSA: Enough, Ser Vardis! Finish him! 

\ti{\BRONN ~continued to dodge and weave, before managing to stab VADIS in the back. Mortally wounded, VADIS falls to the ground. \BRONN ~finishes him off, and throws him out of the Moon Door.}

\ROBYN: \sd{Cheerfully,to Lysa.} Is it over? 

\LYSA: You don't fight with honour!

\BRONN: No. \sd{Indicating the Moon Door} He did.

\ti{\TYRION ~walks to \MORD, who unshackles him, then walks towards \textbf{RODRIK}.}

\ROBYN: Can I make the little man fly now?

\TYRION: Not this little man. This little man is going home. \sd{To \textbf{RODRIK}.} I believe you have something of mine.

\ti{\textbf{RODRIK} ~turns to \CATELYN, standing some feet away. She nods at him. He takes a bag out of his pocket and throws it at \TYRION. \TYRION ~bows to \LYSA, and throws the bag to \MORD.}

\TYRION: A Lannister always pays his debts. 


\scene

\textit{THE KINGSWOOD} 

\ti{\ROBERT ~walks through the forest, holding a spear, \LANCEL ~just behind him, holding wine, \RENLY ~behind him, also holding a spear, and \SELMY ~behind \RENLY.}

\LANCEL: More wine, your Grace? 

\ROBERT: Now, what was I saying? 

\RENLY: A simpler time. 

\ROBERT: It was. It was. You're too young to remember. Wasn't it simpler, Selmy? 

\SELMY: It was, your Grace. 

\ROBERT: The enemy was right in the open, vicious as you like, all but sending you a bloody invitation. Nothing like today. 

\RENLY: It sounds exhilarating. 

\ROBERT: Exhilarating, yes. Not as exhilarating as those balls and masquerades you like to throw \sd{(Starts a hearty laugh as Renly swallows his irritation. Then they continue to walk, deeper in the woods)} You ever fuck a Riverlands girl? 

\RENLY: Once. I think. 

\ROBERT: You think? I think you'd remember. Back in our day, you weren't a real man until you'd fucked one girl from each of the Seven Kingdoms and the Riverlands. We used to call it `making the eight.'

\RENLY: Those were some lucky girls. 

\ROBERT: You ever make the eight, Barristan? 

\SELMY: I don't believe so, your Grace. 

\ROBERT: Those were the days. 

\RENLY: Which days, exactly? The ones where half of Westeros fought the other half and millions died? Or before that, when the Mad King slaughtered women and babies because the voices in his head told him they deserved it? Or way before that, when dragons burned whole cities to the ground?! 

\ROBERT: Easy, boy. You might be my brother, but you're speaking to the King. 

\RENLY: I suppose it was all rather heroic. If you were drunk enough and had some poor Riverlands whore to shove your prick inside and make the eight. 

\ti{\RENLY ~walks off.}

\LANCEL: More wine, your Grace? 


\scene

\textit{KING'S LANDING: THRONE ROOM} 

\ti{\NED ~is seated on the Iron Throne, with \PYCELLE ~seated on a chair to his left and \LITTLEFINGER ~to his right. A \SOUTHERNFARMER ~kneels before him. \BERIC ~is in the \CROWD.}

\SOUTHERNFARMER: They burned most everything in the Riverlands. Our fields, our granaries, our homes. They took our women, then they took `em again. When they was done, they butchered them as if they was animals. They covered our children in pitch, and lit them on fire. 

\PYCELLE: Brigands, most likely. 

\SOUTHERNFARMER: They weren't thieves. They didn't steal nothing. They even left something behind, Your Grace. 

\PYCELLE: It's the King's Hand you're addressing, not the King. The King is hunting. 

\ti{The \SOUTHERNFARMER ~throws a sack to the floor and lifts it from the bottom side. Fish fall out. People at court murmur and exlaim, appalled.}

\LITTLEFINGER: Fish. The Sigil of House Tully. \sd{To Ned, whispering} Isn't that your wife's house... Tully, my Lord Hand?

\NED: These men, were they flying a Sigil? A banner?

\SOUTHERNFARMER: None, your, your Hand. The one who was leading them, taller by a foot than any man I've ever met, saw him cut the blacksmith in two, saw him take the head off a horse with a single swing of his sword. 

\LITTLEFINGER: \sd{Still whispering to Ned.} That sounds like someone we know. The Mountain. 

\NED: \ti{(To the farmer.)} You're describing Ser Gregor Clegane. 

\PYCELLE: Why should Ser Gregor turn brigand? The man is an anointed knight. 

\LITTLEFINGER: I've heard him called Tywin Lannister's mad dog. I'm sure you have as well. \sd{To \NED, voice lowered.} Can you think of any reason the Lannisters might possibly have for being angry with your wife?

\PYCELLE: If the Lannisters were to order attacks on villages under the King's protection, it would be $\ldots$ 

\LITTLEFINGER: That would be almost as brazen as attacking the Hand of the King in the streets of the capital. 

\NED: I cannot give you back your homes or restore your dead to life, but perhaps I can give you justice, in the name of our King, Robert. Lord Beric Dondarrion. You shall have the command. Assemble one hundred men and ride to Ser Gregor's keep.

\BERIC: As you command. 

\ti{Ned stands with his stick, slightly struggling.}

\NED: In the name of Robert of the House Baratheon, the first of his name, King of the Andals and the first men, Lord of the Seven Kingdoms and protector of the realm, I charge you to bring the King's justice to the false knight Gregor Clegane and all those who shared in his crimes. I denounce him and attaint him. I strip him of all ranks and titles, of all lands and holdings, and sentence him to death.

\PYCELLE: My Lord. This is a drastic action. It would be better to wait for King Robert's return.

\NED: Grand Maester Pycelle. 

\PYCELLE: My Lord. 

\NED: Send a raven to Casterly Rock. Inform Tywin Lannister that he has been summoned to Court to answer for the crimes of his bannermen. He will arrive within the fortnight or be branded an enemy of the crown and a traitor to the realm. 

\ti{\NED ~leaves \PYCELLE ~standing. \LITTLEFINGER ~follows \NED.}

\LITTLEFINGER: A bold move, my Lord, and admirable. But is it wise to yank the lion's tail? Tywin Lannister is the richest man in all the Seven Kingdoms. Gold wins wars, not soldiers.

\NED: Then how come Robert is king and not Tywin Lannister? 


\scene

\textit{KING'S LANDING: SANSA'S ROOM} 

\ti{\SEPTAMORDANE ~and \SANSA ~are sewing.}

\SEPTAMORDANE: You wear your hair like a real southern lady now. 

\SANSA: Well, why shouldn't I? We're in the South. 

\SEPTAMORDANE: It's important to remember where you come from. I'm not sure your mother would like these new styles. 

\SANSA: My mother isn't from the North. 

\SEPTAMORDANE: I'm aware of that. 

\SANSA: Why do you care? Do you even have hair under there? 

\SEPTAMORDANE: Yes, I have hair. 

\SANSA: I've never seen it. 

\SEPTAMORDANE: Would you like to? 

\SANSA: No. Where are you from anyway? The North or the South? 

\SEPTAMORDANE: I come from a very small village in $\ldots$ 

\SANSA: Oh, wait. I just realized, I don't care. 

\SEPTAMORDANE: Sansa $\ldots$ 

\SANSA: Septa. 

\SEPTAMORDANE: Now you are being rude.

\ti{\JOFFREY ~walks into the room and \SANSA ~and \SEPTAMORDANE ~stand and curtsey.}

\SEPTAMORDANE: My Prince. 

\SANSA: My Prince. 

\JOFFREY: My Lady. I fear I have behaved monstrously the past few weeks. \sd{He shows her a necklace he's holding.} With your permission?

\ti{She turns, smiling. \JOFFREY ~puts it around her neck.}

\SANSA: It's beautiful, like the one your mother wears. 

\JOFFREY: You'll be queen someday. It's only fitting you should look the part. Will you forgive me for my rudeness? 

\SANSA: There's nothing to forgive. 

\JOFFREY: You're my Lady. One day we'll be married in the throne room. Lords and ladies from all over the Seven Kingdoms will come, from the last hearth in the North to the Salt Shore in the South, and you will be Queen over all of them. I'll never disrespect you again. I'll never be cruel to you again. Do you understand me? You're my Lady now, from this day $\ldots$ until my last day. \sd{He kisses her.}


\scene

\textit{WINTERFELL: IN THE WOODS OUTSIDE THE CASTLE} 

\ti{A horse rides a cart passed some people going the other way. \ROS ~sits at the back of the cart with some turnips beside her. \THEON ~comes up from behind riding a horse.}

\THEON: Stop! Stop! What are you doing? 

\ROS: Going to King's Landing. 

\THEON: In a turnip cart? 

\ROS: I'll find a ship heading south in White Harbor. 

\THEON: You can afford that? 

\ROS: Some of my friends are more generous than others. 

\THEON: There's a thousand girls like you in King's Landing. 

\ROS: So I'll have lots of company. 

\THEON: Yes, you'll be very popular. Until some fat lord comes to visit with a big belly and a little prick and he can't get it up so he knocks all your teeth out. 

\ROS: And what will happen to me if I stay here? Will I become Lady Greyjoy? Mistress of the Iron Islands? 

\THEON: Don't be a fool. 

\ROS: I hear Jaime Lannister attacked Lord Stark in the streets of King's Landing. Every man for a hundred miles will be marching off to war soon. Most of them will never come back. There's nothing left for me here. \sd{To the rider.} Let's go, Stefan. 

\ti{They start to ride off.}

\THEON: Let me see it one more time! 

\ROS: See what? 

\ti{\THEON ~throws a coin at \ROS. She catches it, then lifts her dress to reveal her cunt. He looks. She laughs, then covers herself.}

\THEON: I'm going to miss you. 

\ROS: I know. 


\scene

\textit{KING'S LANDING: THE HAND'S CHAMBERS} 

\ti{\NED ~walks with his stick up to \SANSA ~and \ARYA, both sitting on his bed.}

\NED: I'm sending you both back to Winterfell. 

\SANSA: What? 

\NED: Listen. 

\SANSA: What about Joffrey? 

\ARYA: Are you dying because of your leg? Is that why you're sending us home? 

\NED: What? No. 

\SANSA: Please, father. 

\ARYA: You can't. I've got my lessons with Syrio. I'm finally getting good. 

\NED: This isn't a punishment. I want you back for your own safety. 

\ARYA: Can we take Syrio back with us? 

\SANSA: Who cares about your stupid dancing teacher? I can't go. I'm supposed to marry Prince Joffrey. I love him and I'm meant to be his Queen and have his babies. 

\ARYA: Seven hells. 

\NED: When you're old enough, I'll make you a match with someone who's worthy of you, someone brave, gentle and strong.

\SANSA: I don't want someone brave, gentle and strong. I want him! He'll be the greatest King that ever was, a golden lion, and I'll give him sons with beautiful blond hair. 

\ARYA: The lion's not his sigil, idiot. He's a stag, like his father. 

\SANSA: He is not. He's nothing like that old drunk King. 

\NED: \sd{Having a lightbulb moment.} Go on girls, get your Septa and start packing your things.

\SANSA: Wait! 

\ARYA: Come on.

\SANSA: But it's not fair! 

\ti{They leave. \NED ~sits on a chair and opens a book on his desk, `The Lineages of The Great Houses of Westeros'. He turns a few pages before stopping at House Baratheon.}

\NED: Lord Orys Baratheon, black of hair. Axel Baratheon, black of hair. Lyonel Baratheon, black of hair. Steffon Baratheon, black of hair. Robert Baratheon, black of hair. Joffrey Baratheon, Golden-haired. 


\scene

\textit{VAES DOTHRAK} 

\ti{\DAENERYS, \DROGO, \QOTHO, \JORAH, \textbf{RAKHARO}, and \IRRI ~are eating, drinking and laughing together. \VISERYS ~enters, stumbling. }

\VISERYS: Daenerys! Where's my sister? 

\DAENERYS: \sd{To Jorah.} Stop him. 

\VISERYS: Where is she? Where is she? I'm here for the feast. The whore's feast? 

\ti{\JORAH ~grabs \VISERYS ~shoulder from behind.}

\JORAH: Come. 

\VISERYS: Get your hands off me! No one touches the Dragon! 

\QOTHO: Khal rhae mhar. Me ifa. [The sore-foot king. He walks.] 

\VISERYS: Khal Drogo! I'm here for the feast.

\DROGO: Nevakhi vekha ha maan. [There is a place for you.] 

\JORAH: Khal Drogo says there is a place for you. Back there. 

\VISERYS: That is no place for a king. 

\DROGO: You are no king. 

\ti{\VISERYS ~draws his sword. \JORAH ~takes a step towards him and \VISERYS ~point his blade at his face.}

\VISERYS: Keep away from me! 

\DAENERYS: Viserys! Please. 

\VISERYS: \sd{Spotting \DAENERYS.} There she is. 

\JORAH: Put the sword down. They'll kill us all! 

\VISERYS: They can't kill us. They can't shed blood in their sacred city. But I can. I want what I came for. I want the crown he promised me. He bought you. But he never paid for you. Tell him I want what was bargained for or I'm taking you back. He can keep the baby. I'll cut it out and leave it for him. 

\IRRI: Ifak asta meme zala firikhnharen, meme zala rek meme nem jer ki mae che me vesazhae khaleesies. Me asta meme vos vesazhao khalakkaes. Me asta meme azirissee khalakkaes khaleesisoon ma vannevae mae shafkea. [The foreigner says that he wants a crown, that he wants that which was traded to him or he will take back the khaleesi. He says that he will not take back the prince. He says that he will cut the prince out of the khaleesi and leave him for you.] 

\DROGO: Anha vazhak maan rek me zala. Anha vazhak maan firikhnharen hoshora ma mahrazhi aqovi affin mori atihi mae. [I will give to him what he wants. I will give to him a golden crown and men will tremble when they will see it.] 

\VISERYS: What's he saying? 

\DAENERYS: He says yes. You shall have a golden crown that men shall tremble to behold. 

\VISERYS: That was all I wanted. What was promised. \sd{He sheathes the sword.}

\DROGO: Qora mae! [Seize him!]. 

\ti{QOTHO grabs him.}

\VISERYS:  No! You cannot touch me! I am the Dragon! I'm a dragon! I want my crown! 

\DROGO: Ammeni haz jolin! [Empty that pot.] 

\ti{\textbf{RAKHARO} grabs a pot full of water and empties it. \DROGO ~piles golden goblets and plates into the pot and puts it on the fire, until it has melted down.}

\JORAH: Look away, Khaleesi. 

\DAENERYS: No. 

\VISERYS: Dany, tell them $\ldots$ Make them! Make them $\ldots$ No, you can't! Dany, please! 

\ti{\DROGO ~walks to \VISERYS ~with the pot}

\DROGO: A crown for a king. 

\ti{He pours the gold from the pot on Viserys' head.}

\VISERYS: No! Agghhh! 

\ti{\DROGO ~crouches down and looks looks in anger at Viserys' melting face. \DROGO's men release \VISERYS ~as he stops trembling. His body falls to the ground.}

\JORAH: Khaleesi. 

\DAENERYS: He was no Dragon. Fire cannot kill a Dragon. 

\end{document}

