\input{preamble}
\input{ep07_cast}
\title{Episode 7: S1E7 - You Win or You Die}
\author{}
\date{}
\maketitle

\input{ep07_casttable}


\scene

\textit{ LANNISTER ENCAMPMENT.}
\textit{ \JAIME ~enters the tent of \TYWIN ~. Tywin is (optionally) butchering a deer.} 

\JAIME: \ti{(Starts reading from a letter)} Summoned to court to answer for the crimes of your bannerman Gregor Clegane, the Mountain$\ldots$  Uh, arrive within the fortnight or be branded an enemy of the Crown.  Poor Ned Stark$\ldots$ Brave man, terrible judgment. 

\TYWIN: Attacking him was stupid.  Lannisters don't act like fools. Are you gonna say something clever? Go on, say something clever. 

\JAIME: Catelyn Stark took my brother. 

\TYWIN: Why is he still alive? 

\JAIME: Tyrion? 

\TYWIN: Ned Stark. 

\JAIME: One of our men interfered, speared him through the leg before I could finish him. 

\TYWIN: Why is he still alive? 

\JAIME: It wouldn't have been clean. 

\TYWIN: Clean. You spend too much time worrying about what other people think of you. 

\JAIME: I could care less what anyone thinks of me. 

\TYWIN: That's what you want people to think of you. 

\JAIME: It's the truth. 

\TYWIN: When you hear them whispering Kingslayer behind your back $\ldots$ doesn't it bother you? 

\JAIME: Of course it bothers me. 

\TYWIN: The lion doesn't concern himself with the opinions of the sheep.  I suppose I should be grateful that your vanity got in the way of your recklessness.  I'm giving you half of our forces $\ldots$ 30,000 men. You will bring them to Catelyn Stark's girlhood home and remind her that Lannisters pay their debts. 

\JAIME: I didn't realize you placed such a high value on my brother's life. 

\TYWIN: He's a Lannister. He might be the lowest of the Lannisters, but he's one of us. And every day that he remains a prisoner, the less our name commands respect. 

\JAIME: So the lion does concern himself with the opinions of $\ldots$  

\TYWIN: No, it's not an opinion. It's a fact.  If another House can seize one of our own and hold him captive with impunity, we are no longer a House to be feared.  Your mother's dead.  Before long I'll be dead.  And you and your brother and your sister and all of her children. All of us dead; all of us rotting in the ground.  It's the family name that lives on. It's all that lives on.  Not your personal glory, not your honor, but family.  Do you understand? You're blessed with abilities that few men possess. You are blessed to belong to the most powerful family in the kingdoms. And you are still blessed with youth. And what have you done with these blessings, huh? You've served as a glorified bodyguard for two kings $\ldots$ one a madman, the other a drunk. The future of our family will be determined in these next few months. We could establish a dynasty that will last a thousand years. Or we could collapse into nothing, as the Targaryens did. I need you to become the man you were always meant to be. Not next year. Not tomorrow. Now. 


\scene

\textit{ KING'S LANDING - PALACE GARDENS.}
\textit{ \NED ~is sitting. ~CERSEI approaches him. He needs a stick to stand.}

\CERSEI: You're in pain. 

\NED: I've had worse, My Lady. 

\CERSEI: Perhaps it's time to go home. The South doesn't seem to agree with you. 

\NED: I know the truth Jon Arryn died for. 

\CERSEI: Do you, Lord Stark? Is that why you called me here, to pose me riddles? 

\NED: \ti{(indicating the bruises on her face)} Has he done this before? 

\CERSEI: Jaime would have killed him. My brother is worth a thousand of your friend. 

\NED: Your brother$\ldots$ Or your lover? 

\CERSEI: The Targaryens wed brothers and sisters for 300 years to keep bloodlines pure. Jaime and I are more than brother and sister. We shared a womb. We came into this world together. We belong together. 

\NED: My son saw you with him. 

\CERSEI: Do you love your children? 

\NED: With all my heart. 

\CERSEI: No more than I love mine. 

\NED: And they are all Jaime's. 

\CERSEI: Thank the Gods. In the rare event that Robert leaves his whores for long enough to stumble drunk into my bed, I finish him off in other ways. In the morning, he doesn't remember. 

\NED: You've always hated him. 

\CERSEI: Hated him? I worshipped him. Every girl in the Seven Kingdoms dreamed of him, but he was mine by oath. And when I finally saw him on our wedding day in the Sept of Baelor, lean and fierce and black-bearded, it was the happiest moment of my life. Then that night he crawled on top of me, stinking of wine and did what he did $\ldots$ what little he could do $\ldots$ and whispered in my ear, Lyanna. Your sister was a corpse and I was a living girl and he loved her more than me. 

\NED: When the King returns from his hunt, I'll tell him the truth.You must be gone by then $\ldots$ you and your children.  I will not have their blood on my hands.  Go as far away as you can, with as many men as you can.  Because wherever you go, Robert's wrath will follow you. 

\CERSEI: And what of my wrath, Lord Stark?  You should have taken the realm for yourself.  Jaime told me about the day King's Landing fell.  He was sitting in the Iron Throne and you made him give it up.  All you needed to do was climb the steps yourself.  Such a sad mistake. 

\NED: I've made many mistakes in my life, but that wasn't one of them. 

\CERSEI: Oh, but it was.  When you play the Game of Thrones, you win or you die.  There is no middle ground. 


\scene

\textit{KINGS LANDING - LITTLEFINGER'S BROTHEL} 

\ti{\LITTLEFINGER ~watches as \ROS ~and \WHORE ~fuck.}

\ROS: Oh yes, oh. Oh yes yes yes. 

\LITTLEFINGER: No no no no! Is that what they teach you up in the North? And you $\ldots$ wherever you're from, do you have any idea how ridiculous you sound? Either of you understand a thing that I'm saying? 

\ROS: Yes, My Lord. 

\LITTLEFINGER: Let's start over, shall we? You be the man and you be the woman. Well, go ahead. Slowly. You're not fooling them. They just paid you. They know what you are. They know it's all just an act. Your job is to make them forget what they know. That takes time. You need to$\ldots$ Ease into it. Go ahead. Ease into it. He's winning you over in spite of yourself. You're starting to like this.  He wants to believe you. He's enjoyed his cock since he was old enough to play with it. Why shouldn't you? He knows he's better than other men. He's always known it deep down inside. Now he has proof. He's so good, he's reaching something deep inside of you that no one even knew was there, overcoming your very nature. 

\ROS: Why don't you join us, My Lord? 

\LITTLEFINGER: I'm saving myself for another. 

\ROS: What she doesn't know won't hurt her. 

\LITTLEFINGER: A stupid saying. What we don't know is usually what gets us killed. 

\ROS: She must be very beautiful. 

\LITTLEFINGER: No, not really. Impeccable bloodlines though. 

\ROS: I do believe My Lord's in love. 

\LITTLEFINGER: For many years. Most of my life really. Play with her arse. And she loved me too. I was her little confidant, her plaything. She could tell me anything, anything at all. She told me about all the horses that she liked, the castle she wanted to live in and the man that she wanted to marry.  A northerner with a jaw like an anvil.  So I challenged him to a duel.  I mean, why not? I'd read all the stories. The little hero always beats the big villain in all the stories. In the end, she wouldn't even let him kill me. He's just a boy, she said. Please don't hurt him. So he gave me a nice little scar to remember him by and off they went. 

\ROS: Is she still married to him? 

\LITTLEFINGER: Oh no. He got himself killed before the wedding And she ended up with his brother, an even more impressive specimen. She loves him, I'm afraid. And why wouldn't she? I mean, who could compare to him? He's just so$\ldots$ Good. Do you know what I learned, losing that duel? I learned that I'll never win, not that way. That's their game, their rules. I'm not going to fight them. I'm going to fuck them. That's what I know. That's what I am. And only by admitting what we are can we get what we want. 

\ROS: And what do you want? 

\LITTLEFINGER: Oh, everything, my dear. Everything there is. Now wash yourselves. Both of you are working tonight. 


\scene

\textit{WINTERFELL} 

\ti{\OSHA ~is working, \THEON ~enters}

\THEON: You're a very lucky girl. Do you know that? Where I come from, we don't show mercy to criminals.  Where I come from, if someone like you attacked a little lord? At low tide we'd lay you on your back on the beach, your hands and feet chained to four stakes.  The sea would come in closer and closer. You'd see death creeping toward you a few inches at a time. 

\OSHA: Where is it you come from? 

\THEON: The Iron Islands. 

\OSHA: They far away? 

\THEON: You've never heard of the Iron Islands? 

\OSHA: Trust me, you've never heard where I'm from neither. 

\THEON: Trust me, My Lord. You're not living in the wilderness anymore. In civilized lands, you refer to your betters by their proper titles. 

\OSHA: And what's that? 

\THEON: Lord. 

\OSHA: Why? 

\THEON: Why? What do you mean why? My father is Balon Greyjoy, Lord of the Iron Islands. 

\OSHA: What's that got to do with you? If your father's lord, how can you be lord too? 

\THEON: I will be lord after my father $\ldots$  

\OSHA: so you're not lord now? 

\THEON: No, you $\ldots$  You having a go at me? Is that it? 

\OSHA: I just don't understand how you Southerners do things. 

\THEON: I'm not a Southerner. 

\OSHA: You're from South of the wall. That makes you a Southerner to me. 

\THEON: You're an impudent little wench, aren't you? 

\OSHA: Couldn't say, My Lord. Don't know what impunent means. 

\THEON: Impudent. It means rude, disrespectful. 

\THEON: \ti{(suddenly solicitous)} Do you want to lose that chain? \sd{Takes hold of her chin, moves their faces close.}

\ti{Enter LUWIN}

\LUWIN: Theon Greyjoy! The lady is our guest. 

\THEON: I thought she was our prisoner. 

\LUWIN: Are the two mutually exclusive in your experience? 

\ti{\THEON ~leaves}

\LUWIN: Chances are I won't be nearby the next time that happens. 

\OSHA: I'm used to worse than him. I'm used to men who could chew that boy up and pick their teeth with his bones. 

\LUWIN: Why did you come here? 

\OSHA: Didn't mean to come here. Meant to get much further South than this. As far South as South goes, before the long night comes. 

\LUWIN: Why? What are you afraid of? 

\OSHA: There's things that sleep in the day and hunt at night. 

\LUWIN: Owls and Shadowcats and $\ldots$  

\OSHA: I'm not talking about Owls and Shadowcats. 

\LUWIN: The things you speak of $\ldots$ they've been gone for thousands of years. 

\OSHA: They wasn't gone, old man. They was sleeping. And they ain't sleeping no more. 


\scene

\textit{THE WALL} 

\ti{\SAM ~and \JON ~are keeping watch.}

\SAM: I miss girls. Not even talking to them. I never talked to them. Just looking at them, hearing them giggle.Don't you miss girls?

\SAM: \sd{(Seeing something in the distance)} Riders. \sd{(Unsure but decisive)} The horn. We have to blow the horn. 

\JON: Why is he alone? 

\SAM: One blast for a Ranger returning, two for Wildlings, three for $\ldots$ 

\JON: There's no rider. \sd{Horse gets closer} Whoa, boy, whoa. That's my Uncle Benjen's horse. Where's my Uncle? 


\scene

\textit{KING'S LANDING - OUTSIDE ROBERT'S CHAMBER} 

\ti{\RENLY ~enters to NED}

\RENLY: Ned! It's Robert. We were hunting $\ldots$ a boar $\ldots$  

\ti{Ignoring him, \NED ~moves towards \ROBERT's chamber.  \JOFFREY ~and \CERSEI ~attend the King, who is injured in his bed.}

\ROBERT: sd{(To Joffrey)} I should have spent more time with you, shown you how to be a man. I was never meant to be a father.

\ti{\NED ~enters}

\ROBERT: sd{(To Joffrey)} Go on.  You don't want to see this.

\ti{\JOFFREY ~leaves}

\ROBERT: sd{(To Ned)} My fault. Too much wine, missed my thrust. It stinks.  It stinks like death. Don't think I can't smell it. I paid the b*st*rd back, Ned. I drove my knife right through his brain. You ask them if I didn't. Ask them! I want the funeral feast to be the biggest the Kingdoms ever saw. And I want everyone to taste the boar that got me. Now leave us, the lot of you. I need to talk to Ned. 

\CERSEI: Robert, my sweet $\ldots$  

\ROBERT: Out, all of you! 

\ti{\CERSEI ~and anyone else leaves}

\NED: You damned fool. 

\ROBERT: Paper and ink on the table, write down what I say.  In the name of Robert of the House Baratheon, first of $\ldots$  you know how it goes.  Fill in the damn titles.  I hereby command Eddard of House Stark $\ldots$  titles, titles $\ldots$ to serve as Lord Regent and Protector of the Realm upon my death, to rule in my stead until my son Joffrey comes of age.  Give it over.  Give it to the council after I'm dead.  At least they'll say I did this right, this one thing.  You'll rule now. You'll hate it worse than I did, but you'll do it well. 

\NED: The girl $\ldots$ Daenerys. 

\ROBERT: You were right. Varys, Littlefinger, my brother$\ldots$ Worthless.  No one to tell me no but you.  Only you.  Let her live.  Stop it, if it's not too late. 

\NED: I will. 

\ROBERT: And my son$\ldots$  Help him, Ned.  Make him better than me. 

\NED: I'll$\ldots$  I'll do everything I can to honor your memory. 

\ROBERT: My memory.  King Robert Baratheon, murdered by a pig. Give me something for the pain and let me die. 

\ti{\NED ~leaves the room to meet \SELMY ~and \VARYS ~in the corridor}

\NED: Give him milk of the poppy. 

\SELMY: He was reeling from the wine.  He commanded us to step aside, but$\ldots$  I failed him. 

\NED: No man could have protected him from himself. 

\VARYS: I wonder, Ser Barristan, who gave the king this wine? 

\SELMY: His squire, from the king's own skin. 

\NED: His squire? The Lannister boy? 

\VARYS: Such a dutiful boy to make sure his Grace did not lack refreshment.  I do hope the poor lad does not blame himself. 

\NED: His Grace has had a change of heart concerning Daenerys Targaryen.  Whatever arrangements you made, unmake them. At once. 

\VARYS: I'm afraid those birds have flown. The girl is likely dead already. 


\scene

\textit{ESSOS - DROGO's TENT} 

\ti{\DAENERYS ~is braiding \DROGO's hair}

\DROGO: Vezh fin saja rhaesheseres vo zigereo adoroon shiqethi. [The stallion who mounts the world has no need for iron chairs.] 

\DAENERYS: K'asi assikhqoyisiri vezh adothrae nakhaan rhaesheseri. [According to the prophecy, the stallion will ride to the ends of the earth.] 

\DROGO: Sorfosor nakha she Havazzhifi Kazga. Vo hrazef laz yoma evethiz. [The earth ends at the black salt see.  No horse can cross the poison water.] 

\DAENERYS: Sorfosor nakho vosecchi she havazh. Sani sorfi vekha yomme havash. Sorfo athyolari anni. [The earth does not end at the sea.  There are many dirts beyond the sea.  The dirt where I was born.] 

\DROGO: Vo sorfo. Rhaeshi.  [Not dirts, lands.] 

\DAENERYS: Rhaeshi, sec. Dalen rhaggati evetha ma ale vekhi she Vaes Seris. Hrazef ido fini ovethi yomme havazh. [Lands, yes.  There are thousands of ships in the free cities.  Wooden horses that fly across the sea.] 

\DROGO:  Kisha vastoki vos alikh hrazefi ido m'adori shiqethi. [Let us speak no more of wooden horses and iron chairs] 

\DAENERYS: Me vos ador. Me$\ldots$me$\ldots$throne. [It's not a chair. It's$\ldots$it's$\ldots$throne.]. 

\DROGO: Throne. 

\DAENERYS: Ador finaan khal nevasoe$\ldots$che khaleesi. [A chair for a King to sit on, or a Queen.] 

\DROGO: Khal vos zigereo adoroon anevasoe maan. Me zigeree sajosoon disse. [A King does not need a chair, only a horse.] 


\scene

\textit{ESSOS - MARKETPLACE} 

\ti{\DAENERYS ~is walking with \JORAH, \IRRI ~and RAKHARO}

Can't you help me make him understand? 

\JORAH: The Dothraki do things in their own time, for their own reasons. Have patience, Khaleesi. We will go home, I promise you. 

\DAENERYS: My brother was a fool, I know, but he was the rightful heir to the Seven Kingdoms. Have I said something funny, Ser? 

\JORAH: Forgive me, Khaleesi, but your ancestor Aegon the Conqueror didn't seize six of the kingdoms because they were his right. He had no right to them. He seized them because he could. 

\DAENERYS: And because he had dragons. 

\JORAH: Ah well, having a few dragons makes things easier. 

\DAENERYS: You don't believe it. 

\JORAH: Have you ever seen a dragon, Khaleesi?  I believe what my eyes and ears report.  As for the rest$\ldots$ It was 300 years ago. Who knows what really happened?  Now if you'll pardon me, I'll seek out the merchant Captain, see if he has any letters for me. 

\DAENERYS: I'll come with you. 

\JORAH: No no, don't trouble yourself. Enjoy the market. I'll rejoin you soon enough. 

\ti{\JORAH ~wanders away through the market}

\BOY: Psst, Jorah the Andal.  The spider sends his greetings and his congratulations.  A royal pardon $\ldots$ you can go home now. 

\ti{Elsewhere in the market, \DAENERYS ~meets a wineseller}

\WINESELLER:  Lekhi ha khaleesisaan? M'anhoon vekha virzethi gizkhvena Dornoon, zhey erinak. At lekhi ma shafka ahakee yal hakesoon anni. [A taste for the Khaleesi?  I have a sweet red for Dorne.  One taste and you'll name your first child after me.] 

\DAENERYS: My son already has his name, but I'll try your summerwine.  Just a taste. 

\WINESELLER: My Lady, you are from Westeros. 

\IRRI: You have the honor of addressing Daenerys of the House Targaryen, Khaleesi of the riding men and princess of the Seven Kingdoms. 

\WINESELLER: \ti{(kneeling)} Princess. 

\DAENERYS: Rise.  I'd still like to taste that wine.  

\WINESELLER: That? Dornish swill.  Not worthy of a princess.  I have a dry red from the Arbor $\ldots$ nectar of the Gods.  Let me give you a cask. Uh $\ldots$ a gift. 

\DAENERYS: You honor me, Ser. 

\WINESELLER: The honor $\ldots$ the honor is all mine. There are many in your homeland that pray for your return, princess. 

\ti{He tries to hand the wine to \DAENERYS, but RAKHARO takes it}

\DAENERYS: I hope to repay your kindness someday. 

\ti{\JORAH ~reappears}

\JORAH: Rakharo, azzohi haz khogare. [Rakharo, put down that cask.] 

\DAENERYS: Huh. Is something wrong? 

\JORAH: I have a thirst.  Open it. 

\WINESELLER: The wine is for the Khaleesi. It's not for the likes of you. 

\JORAH: Open it. 

\ti{With a heavy sigh, the \WINESELLER ~does as he is told.}

\JORAH: Pour. 

\WINESELLER: It would be a crime to drink a wine this rich without at least giving it time to breathe. 

\DAENERYS: Do as he says. 

\WINESELLER: As the princess commands. [He pours a glass and hands it to Jorah.] Sweet, isn't it?  Can you smell the fruit, Ser?  Taste it, My Lord.  Tell me that that is not the finest wine that has ever touched your tongue. 

\JORAH: You first. 

\WINESELLER: Me?  I'm afraid I am not worthy of the vintage.  Besides, it is a poor wine merchant who would drink up his own wares. 

\DAENERYS: You will drink. 

\ti{The \WINESELLER ~looks as though he's about to drink, then throws the wine to the ground and makes a run for it.}

\JORAH: Stop him! 

\ti{RAKHARO tackles the \WINESELLER ~and overpowers him in short order, dragging him away.  \JORAH ~takes \DAENERYS ~gently by the arm and leads her away.}

\JORAH: Come. 


\scene

\textit{THE WALL} 

\textit{\JEOR ~ addresses the assembled Night Watch, including \JON ~and \SAM. Most of the other Night Watch characters are also there.} 

\JEOR: You came to us as outlaws, poachers, rapers, killers, thieves. You came alone, in chains, without friends nor honor. You came to us rich and you came to us poor. Some of you bear the names of proud houses, others only b*st*rd names or no names at all. It does not matter. All that is in the past. Here, on the wall, are all one house. Tonight$\ldots$  

\ti{(he continues speaking, but the camera has moved away...)} \SAM: You're allowed to look happy. You're going to be a Ranger. Isn't that what you always wanted? 

\JON: I want to find my Uncle. I know he's alive out there.  I know he is. 

\SAM: I wish I could help you, but I'm no Ranger.  It's the steward's life for me. 

\JON: There's honor in being a steward. 

\SAM: Not much, really.  But there's food. 

\JEOR: $\ldots$Here you begin anew. A man of The Night's Watch$\ldots$ Lives his life for the realm. Not for a king, or a lord, or the honor of this house or that house; not for gold nor glory nor a woman's love; but for the realm and all the people in it. You've all learned the words of the vow. Think carefully before you say them. The penalty for desertion is death. You can take your vows here tonight at sunset. Do any of you still keep the old Gods? 

\JON: I do, My Lord. 

\JEOR: You'll want to take your vow before a heart tree as your Uncle did. 

\JON: Yes, My Lord. 

\JEOR: You'll find a Weirwood a mile North of the Wall.  And your old Gods too, maybe. 

\SAM: My Lord, might I go as well? 

\JEOR: Does house Tarly keep the old Gods? 

\SAM: No, My Lord.  I was named in the light of the Seven, as my father was and his father before him. 

\JEOR: Why would you forsake the Gods of your father and your house? 

\SAM: The Night's Watch is my house now. The Seven have never answered my prayers. Perhaps the old Gods will. 

\JEOR: As you wish, lad.  You've all been assigned an order, according to our needs and your strengths.  Halder to the builders. Pyp to the stewards. Toad to the builders. Grenn to the Rangers. Samwell to the stewards. Matthar to the Rangers. Dareon to the stewards. Balian to the Rangers. Rast to the Rangers. Jon to the stewards. 

\ti{(quieter, as the focus switches to JON's reaction)} Rancer to the builders. Echiel to the builders. Gordo to the stewards. Niko to the Rangers. Escan to the Rangers. Vorkoy to the builders. Joby to the stables. Mink to the kitchens. Allo to the builders. Nelugo to the Rangers. May all the Gods preserve you. 

\WATCHMANa: Rangers with me. 

\WATCHMANb: Builders! 

\AEMON: Samwell, you will assist me in the rookery and library. Pyp, you will report to Bowen Marsh in the kitchens. Luke, report to one-eyed Joe in the stables. Dareon, we are sending you to Eastwatch. Present yourself to Borcas when you arrive. Make no comment about his nose. Jon Snow, Lord Commander Mormont has requested you for his personal steward. 

\JON: \ti{(Suppressed anger)} Will I serve the Lord Commander's meals and fetch hot water for his bath. 

\AEMON: Certainly. 

And keep a fire burning in his chambers, change his sheets and blankets daily and do everything else the Lord Commander requires of you. 

\JON: \ti{(angrily)} Do you take me for a servant? 

\AEMON: We took you for a man of The Night's Watch. But perhaps we were wrong in that. 

\JON: May I go? 

\AEMON: As you wish. 

\textit{\JON ~storms off. \SAM ~goes after him.}

\SAM: Jon, wait! Don't you see what they're doing? 

\JON: I see Ser Alliser's revenge, that's all. He wanted it and he got it. Stewards are nothing but maids! I'm a better swordsman and rider than any of you! It's not fair. 

\PYP: Fair? I was singing for a high lord at Acorn Hall when he put his hand on my leg and he wanted to see my cock. I pushed him away and he said he'd have my hands cut off for stealing their silver. So now I'm here $\ldots$ at the end of the world with no one to sing for but old men and little shits like you. I'll never see my family again. I'll never be inside a woman again. So don't tell me about fair. 

\SAM: I thought you were caught stealing a wheel of cheese for your starving sister? 

\PYP: You think I was gonna tell a bunch of strangers that a high lord tried to grab my cock? 

\SAM: Could you sing me a song, Pyp? I'd like to hear a song.  

\ti{(to JON)} Now listen to me. The old man is the Lord Commander of The Night's Watch. You'll be with him day and night. Yes, you'll clean his clothes. But you'll also take his letters, attend him at meetings, squire for him in battle. You'll know everything, be part of everything. And he asked for you himself. He wants to groom you for command. 

\JON: I just$\ldots$ I always wanted to be a Ranger. 

\SAM: I always wanted to be a Wizard. 

\ti{\JON ~bursts out laughing}

\SAM: What? No, I'm serious. So you'll stay and say your words with me? 


\scene

\textit{KINGS LANDING - A CORRIDOR IN THE PALACE} 

\ti{\RENLY ~enters to \NED ~and two of his BANNERMEN}

\RENLY: Lord Stark, a moment. Alone if you will.  He named you Protector of the Realm. 

\NED: He did. 

\RENLY: She won't care.  Give me an hour and I can put a hundred swords at your command. 

\NED: And what should I do with a hundred swords? 

\RENLY: Strike! Tonight while the castle sleeps.  We must get Joffrey away from his mother and into our custody.  Protector of the Realm or no, he who holds the King holds the Kingdom.  Every moment you delay gives Cersei another moment to prepare.  By the time Robert dies, it will be too late for the both of us. 

\NED: What about Stannis? 

\RENLY: Saving the Seven Kingdoms from Cersei and delivering them to Stannis?  You have odd notions about protecting the realm. 

\NED: Stannis is your older brother. 

\RENLY: This isn't about the bloody line of succession.  That didn't matter when you rebelled against the Mad King.  It shouldn't matter now.  What's best for the Kingdoms?  What's best for the people we rule?  We all know what Stannis is.  He inspires no love or loyalty.  He's not a King.  I am. 

\NED: Stannis is a commander.  He's led men into war twice.  He destroyed the Greyjoy fleet $\ldots$  

\RENLY: Yes, he's a good soldier. Everyone knows that.  So was Robert.  Tell me something.  Do you still believe good soldiers make good kings? 

\NED: I will not dishonor Robert's last hours by shedding blood in his halls and dragging frightened children from their beds. 


\scene

\textit{KINGS LANDING - THE HAND'S CHAMBERS} 

\ti{\NED ~is at his desk.  His \BANNERMAN ~stands before him.}

\NED: You will sail to dragonstone tonight. You will place this in the hand of Stannis Baratheon. Not his steward, not his Captain of the guard, and not his wife. Only Stannis himself. 

\BANNERMAN: Yes, My Lord. 

\ti{\LITTLEFINGER ~enters, unannounced.}

\NED: Now leave us. 

\LITTLEFINGER: \ti{(bowing)} My Lord protector. 

\NED: The King has no trueborn sons. Joffrey and Tommen are Jaime Lannister's bastards. 

\LITTLEFINGER: So when the King dies $\ldots$  

\NED: The throne passes to his brother Lord Stannis. 

\LITTLEFINGER: So it would seem. Unless $\ldots$  

\NED: There is no unless. He is the rightful heir. Nothing can change that. 

\LITTLEFINGER: And he cannot take the throne without your help. You would be wise to deny it to him and to make sure Joffrey succeeds. 

\NED: Do you have a shred of honor? 

\LITTLEFINGER: You are now Hand of the King and Protector of the Realm. All of the power is yours. You need only reach out and take it. Make peace with the Lannisters. Release the Imp. Wed your daughter to Joffrey. We have plenty of time to get rid of Stannis. And if Joffrey seems likely to cause problems when he comes into his throne, we simply reveal his little secret and seat Lord Renly there instead. 

\NED: We? 

\LITTLEFINGER: You'll need someone to share these burdens. I assure you $\ldots$ my price would be modest. 

\NED: What you suggest is treason. 

\LITTLEFINGER: Only if we lose. 

\NED: Make peace with the Lannisters, you say$\ldots$ With the people who tried to murder my boy. 

\LITTLEFINGER: We only make peace with our enemies, My Lord. That's why it's called making peace. 

\NED: No. I won't do it. 

\LITTLEFINGER: So it will be Stannis and war? 

\NED: There is no other choice. He is the heir. 

\LITTLEFINGER: So why did you call me here? Not for my wisdom, clearly. 

\NED: You promised Catelyn you would help me. The Queen has a dozen knights and a hundred men-at-arms $\ldots$ enough to overwhelm what remains of my household guard. I need the gold cloaks. The City Watch is two thousand strong and sworn to defend the King's peace. 

\LITTLEFINGER: Look at you. You know what you want me to do, you know it has to be done, but it's not honorable so the words stick in your throat. When the Queen proclaims one King and the Hand proclaims another, whose peace do the Gold Cloaks protect? Who do they follow? The man who pays them. 


\scene

\textit{THE WALL - THE GODSWOOD} 

\ti{\SAM ~and \JON ~kneel before the tree, whilst other watchmen look on.}

\textbf{JON/SAM}: Hear my words and bear witness to my vow. Night gathers and now my watch begins. It shall not end until my death.  I shall take no wife, hold no lands, father no children. I shall wear no crowns and win no glory. I shall live and die at my post. I am the sword in the darkness. I am the watcher on the walls. I am the shield that guards the realms of men. I pledge my life and honor to The Night's Watch, for this night and all the nights to come. 

\WATCHMANc: You knelt as boys. Rise now as men of The Night's Watch. Well done. Well done. 

\ti{Ghost appears with something in his mouth}

\SAM: What's he got there? 

\JON: To me, ghost. Bring it here. 

\ti{It's a severed hand}

\SAM: Gods be good! 


\scene

\textit{ESSOS - A LARGE TENT} 

\ti{The \WINESELLER ~is tied to a post. \DAENERYS ~and \JORAH ~are talking}

\DAENERYS: What will they do to him? 

\JORAH: When the Khalasar rides, he'll be leashed to a saddle, forced to run behind the horses for as long as he can. 

\DAENERYS: And when he falls? 

\JORAH: I saw a man last nine miles once. 

\DAENERYS: King Robert still wants me dead. 

\JORAH: This poisoner was the first. He won't be the last. 

\DAENERYS: I thought he'd leave me alone $\ldots$ now that my brother is gone. 

\JORAH: He will never leave you alone. If you ride to darkest Asshai, his assassins will follow you. If you sailed all the way to the Basilisk Isles, his spies would tell him. He will never abandon the hunt. You're a Targaryen $\ldots$  the last Targaryen. Your son will have Targaryen blood with 40,000 riders behind him. 

\DAENERYS: He will not have my son. 

\JORAH: He will not have you either, Khaleesi. 

\ti{\DROGO ~enters.  He approaches the \WINESELLER ~and looms threateningly, but then turns away without touching him and approaches DANY}

Zhey jalan atthirari anni. Hash azisi? [Moon of my life. Are you hurt?] Jora Andahli, okki zhille hrazef fin allayafa shafka drogikhoon anni. Me shafki. [Jorah the Andal, I heard what you did. Choose any horse you wish from my herd. It's yours.] Anha asshilak jin azh shafkea haji rekoon et shafka. [I make this gift to you for what you did.]

\ti{He makes this speech. His horsemen, ie. everyone, begins to cheer as he progresses.}

\DROGO: Ma rizhaan anni, vezh fin asaja rhaesheseres, maan anha valloshak azh akka. [And to my son, the stallion who will mount the world, I will also pledge a gift.] Maan anha vazhak jin ador shiqethi finaan neva ave maisi mae. [I will give him the iron chair that his mothers father sat upon.] Anha vazhak maan Rhaeshis Andahli. Anha, zhey Drogo, atak jin. [I will give The Lands of the Andals. I, Drogo, will do this.] Anha vidrik khalasares anni jim, finaan nakhoe rhaesheser, majin adothrak hrazef ido yomme Havazzhifi Kazga ven et vo khal avvos. [I will take my khalasar west to where the world ends and ride wooden horses across the black salt sea as no khal has done before.] Anha vaddrivak mahrazhis fini ondee khogar shiqethi ma vohharak okrenegwin mori. [I will kill the men in iron suits and tear down their stone houses.] Anha aqorisok chiories mori, vazzafrok yal mori, ma afichak vojjor samva Vaesaan Dothrak. [I will rape their women, take their children as slaves and bring their broken gods back to Vaes Dothrak.] Ki jini anha astak asqoy, anha, Drogo ki Bharbosi. [This I vow. Drogo son of Bharbo.] Ki jini anha astak asqoy hatif Maisi Krazaaji kash shieraki vitihiri asavvasoon. Asavvasoon! Asavvasoon! [I swear before the mother of mountains as the stars look down in witness. As the stars look down in witness.] 


\scene

\textit{KINGS LANDING - A CORRIDOR IN THE PALACE} 

\ti{\NED ~is walking with his BANNERMEN. He moves directly between the next three scenes.}

\PAGE: \ti{(approaching)} Lord Stark!

\BANNERMAN: Stop! 

\NED: No, all right. It's all right. Let him through. 

\PAGE: Lord Stark, King Joffrey and the Queen Regent request your presence in the Throne Room. 

\NED: King Joffrey? 

\PAGE: King Robert is gone. The Gods give him rest. 


\scene

\textit{KINGS LANDING - A COURTYARD} 

\ti{\NED ~and his \BANNERMAN ~enter to \LITTLEFINGER ~and \VARYS}

\LITTLEFINGER: All is accomplished. The City Watch is yours. 

\NED: Good. Is Lord Renly joining us? 

\VARYS: I fear Lord Renly has left the city. He rode through the old gate an hour before dawn with Ser Loras Tyrell and some 50 retainers. Last seen galloping South in some haste. 

\GOLDCLOAK: We stand behind you, Lord Stark. 

\ti{The group makes its way to...}


\scene

\textit{KINGS LANDING THRONE ROOM} 

\ti{\NED ~et all enter to \JOFFREY ~on the iron throne, \CERSEI ~beside him. \GOLDCLOAK ~and troop line the walls.}

\PAGE: \ti{(Announcing)} All hail his Grace, Joffrey of Houses Baratheon and Lannister, the first of his name, King of the Andals and the First Men, Lord of the Seven Kingdoms and Protector of the Realm. 

\JOFFREY: I command the council to make all necessary arrangements for my coronation. I wish to be crowned within the fortnight. Today I shall accept oaths of fealty from my loyal councilors. 

\NED: Ser Barristan, I believe no man here could ever question your honor. 

\ti{\NED ~hands \SELMY ~a paper}

\SELMY: King Robert's seal $\ldots$ unbroken. Lord Eddard Stark is herein named Protector of the Realm, to rule as Regent until the heir come of age. 

\CERSEI: May I see that letter, Ser Barristan?

\ti{He hands it to her}

\CERSEI: Protector of the realm. Is this meant to be your shield, Lord Stark? 

\CERSEI: \ti{(She tears the paper)} A piece of paper? 

\SELMY: Those were the King's words. 

\CERSEI: We have a new King now. Lord Eddard, when we last spoke you offered me some counsel. Allow me to return the courtesy. Bend the knee, My Lord. Bend the knee and swear loyalty to my son $\ldots$ and we shall allow you to live out your days in the gray waste you call home. 

\NED: Your son has no claim to the throne. 

\JOFFREY: Liar! 

\CERSEI: You condemn yourself with your own mouth, Lord Stark. Ser Barristan, seize this traitor. 

\NED: \ti{(to the goldcloaks)} Ser Barristan is a good man, a loyal man. Do him no harm. 

\CERSEI: You think he stands alone? 

\JOFFREY: Kill him! Kill all of them, I command it! 

\NED: Commander, take the Queen and her children into custody. Escort them back to the royal apartments and keep them there, under guard. 

\GOLDCLOAK: Men of the Watch! 

\NED: I want no bloodshed. Tell your men to lay down their swords. No one needs to die. 

\GOLDCLOAK: Now! 

\ti{THE goldcloaks turn and swiftly dispatch \NED's few remaining men}

\ti{\LITTLEFINGER rushes \NED from behind and holds a knife to his throat.}

\LITTLEFINGER: I did warn you not to trust me. 

\end{document}
