\input{preamble}
\input{ep08_cast}
\title{Episode 8 (S1E8): The Pointy End}
\author{}
\date{}
\maketitle

\input{ep08_casttable}


\scene

\textit{KING'S LANDING: A CORRIDOR} 

\ti{\SANSA ~and \SEPTAMORDANE ~are hurrying along.}

\SEPTAMORDANE: Your sister knew perfectly well we were to leave today. How she could forget$\ldots$  

\SANSA: She didn't forget. She's with her dancing master. She's with him every morning. She always comes back with scrapes and bruises. She's so clumsy. 

\sfx{Sounds of screaming and fighting.}

\SEPTAMORDANE: Hush! Go back to your room. Bar the doors and do not open them for anyone you do not know. 

\SANSA: What is it? What's happening? 

\SEPTAMORDANE: Do as I told you. Run! 

\ti{They exit seperately. \SANSA ~re-enters to the \HOUND.}

\SANSA: Stay away from me. I'll tell my father. I'll$\ldots$ I'll tell the Queen. 

\HOUND: Who do you think sent me? 


\scene

\textit{ELSEWHERE IN KING'S LANDING} 

\ti{\SYRIO ~is teaching \ARYA ~to fence.}

\SYRIO: Left high, left low. Right low, lunge right. Right. \sd{He attacks on her left as he says right, and disarms her.} Now you are dead.

\ARYA: You said right, but you went left. 

\SYRIO: And now you are a dead girl. 

\ARYA: Only `cause you lied. 

\SYRIO: My tongue lied. My eyes shouted the truth. You were not seeing. 

\ARYA: I was so. I watched, but you$\ldots$ 

\SYRIO: Watching is not seeing, dead girl. The seeing, the true seeing, that is the heart of swordplay. 

\ti{\MERYN ~and two \textbf{GUARDS} enter.}

\MERYN: Arya Stark, come with us. Your father wants to see you. 

\SYRIO: And why is it that Lord Eddard is sending Lannister men in place of his own? I am wondering. 

\MERYN: Mind your place, dancing master. This is no concern of yours. 

\ARYA: My father wouldn't send you. And I don't have to go with you if I don't want. 

\MERYN: Take her. 

\SYRIO: Are you men or snakes, that you would threaten a child? 

\MERYN: Get out of my way, little man. 

\SYRIO: I am Syrio Forel$\ldots$ 

\MERYN: Foreign bastard. 

\SYRIO:$\ldots$ And you will be speaking to me with more respect. 

\MERYN: Kill the Braavosi. Bring the girl. 

\SYRIO: Arya child, we are done with dancing for the day. Run to your father. 

\ti{\GUARDa ~and \GUARDb ~attack \SYRIO, and despite only wielding a wooden sword he disarms and trips them both.  They lie wounded on the ground.}

\MERYN: Bloody oafs. \sd{He draws his sword.}

\SYRIO: Be gone now, Arya. 

\ARYA: Come with me. Run. 

\SYRIO: The first sword of Braavos does not run. \sd{\MERYN ~attacks \SYRIO ~and destroys his wooden sword.} What do we say to the god of death? 

\ARYA: Not today. 

\SYRIO: Go. 

\ti{\ARYA ~runs.}

\scene

\sfx{Sounds of shouting and fighting.}

\ARYA: \sd{off-stage} Not today. Not today. 

\ti{\ARYA ~re-enters, still holding her wooden sword, and sees that her case has been knocked to the ground, and things are strewn around.  She drops the wooden sword and starts searching through them.}

\ARYA: Needle. 

\ti{A \BOY ~enters}

\BOY: There she is. 

\ARYA: What do you want? 

\BOY: I want you, wolf girl. Come here. 

\ARYA: Leave me be. My father's a lord. He'll reward you. 

\BOY: She'll reward me$\ldots$ the Queen! 

\ARYA: Stay away! \sd{She finally locates her sword Needle in the case.}

\ti{The \BOY ~moves to grab her, and without thinking she stabs him.}


\scene

\textit{KING'S LANDING: A CELL} 

\ti{\NED ~is in chains.  \VARYS ~enters.}

\VARYS: Lord Stark, you must be thirsty. 

\NED: Varys. 

\ti{\VARYS ~offers \NED ~a flask}

\VARYS: I promise you it isn't poison. Why is it no one ever trusts the eunuch?
\sd{He drinks from the flask, then offers it again. This time, \NED ~drinks.} Not so much, my lord. I would save the rest, if I were you. Hide it. Men have been known to die of thirst in these cells. 

\NED: What about my daughters? 

\VARYS: The younger one seems to have escaped the castle. Even my little birds cannot find her. 

\NED: And Sansa? 

\VARYS: Still engaged to Joffrey. Cersei will keep her close. The rest of your household though$\ldots$ all dead, it grieves me to say. I do so hate the sight of blood. 

\NED: You watched my men being slaughtered and did nothing. 

\VARYS: And would again, my lord. I was unarmed, unarmoured and surrounded by Lannister swords. When you look at me do you see a hero? What madness led you to tell the Queen you had learned the truth about Joffrey's birth? 

\NED: The madness of mercy. That she might save her children. 

\VARYS: Ah, the children. It is always the innocents who suffer. It wasn't the wine that killed Robert, nor the boar. The wine slowed him down and the boar ripped him open, but it was your mercy that killed the King. I trust you know you are a dead man, Lord Eddard? 

\NED: The Queen can't kill me. Cat holds her brother. The wrong brother sadly. And lost to her. 

\VARYS: Your wife has let the Imp slip through her fingers. 

\NED: If that's true, then slit my throat and be done with it. 

\VARYS: Not today, my lord. 

\NED: Tell me something, Varys. Who do you truly serve? 

\VARYS: The Realm, my lord. Someone must. \sd{exit.}


\scene

\textit{THE WALL}

\ti{\SAM, \JON, \OTHELLYARWYK, and \JEOR ~are gathered round two corpses, one missing a hand.} 

\JEOR: It's Othor, without a doubt.

\OTHELLYARWYK:  The other one's Jafer Flowers, my lord. That's the hand the wolf tore off. 

\JEOR: Any sign of Benjen or the rest of his party? 

\JON: Just these two, my lord. Been dead a while, I'd say. 

\JEOR: Mmm. 

\SAM: The smell. 

\OTHELLYARWYK: What smell? 

\SAM: There is none. If they'd be dead for a long time, wouldn't there be rot? 

\JON: We should burn them. 

\OTHELLYARWYK: That Snow's not wrong, my lord. Fire will do for them. The wildling way. 

\JEOR: I want Maester Aemon to examine them first. You may be a coward, Tarly, but you're not stupid. Get them inside. 

\OTHELLYARWYK: You heard him. 

\ti{Enter \MESSENGER.}

\MESSENGER: Lord Commander, Maester Aemon awaits you in his chambers$\ldots$ a raven from King's Landing. 

\OTHELLYARWYK: Come on, move 'em out. 


\scene

\textit{THE WALL: MORMONT'S CHAMBER} 

\ti{\JEOR ~sits at his table reading a letter.  \JON ~enters.}

\JEOR: Bring me a horn of ale, Snow, and pour one for yourself. \sd{\JON ~fetches two horns of ale.} The King is dead. 

\JON: Is there any word of my father? 

\JEOR: Sit. Lord Stark has been charged with treason. They say he conspired with Robert's brothers to deny the throne to Prince Joffrey. \sd{\JON ~reaches for the letter and studies it, then leaps up as if to leave.} I hope you're not thinking of doing anything stupid. Your duty lies here now. 

\JON: My sisters were in King's Landing too. 

\JEOR: I'm sure they'll be treated gently. 


\scene

\textit{KING'S LANDING} 

\ti{\SANSA ~sits facing \CERSEI, \PYCELLE, \LITTLEFINGER ~and \VARYS.}

\VARYS: Your father has proved to be an awful traitor, dear.

\PYCELLE: King Robert's body was still warm when Lord Eddard began plotting to steal Joffrey's rightful throne. 

\SANSA: He wouldn't do that. He knows how much I love Joffrey. He wouldn't. Please, Your Grace, there's been a mistake. Send for my father. He'll tell you$\ldots$ the King was his friend. 

\CERSEI: Sansa sweetling, you are innocent of any wrong. We know that. Yet you are the daughter of a traitor. How can I allow you to marry my son? 

\PYCELLE: A child born of a traitor's seed is no fit consort for our King. She is a sweet thing now, Your Grace, but in ten years who knows what treason she may hatch? 

\SANSA: No, I'm not. I'll be a good wife to him, you'll see. I'll be a queen just like you, I promise. I won't hatch anything. 

\LITTLEFINGER: The girl is innocent, Your Grace. She should be given a chance to prove her loyalty. 

\CERSEI: Little dove, you must write to Lady Catelyn and your brother, the eldest, what's his name?

\ti{\CERSEI ~pushes a blank piece of paper towards \SANSA.}

\SANSA: Robb. 

\CERSEI: Word of your father's arrest will reach him soon, no doubt. Best it comes from you. If you would help your father, urge your brother to keep the King's peace. \sd{She places a quill pen in front of \SANSA.} Tell him to come to King's Landing and swear his fealty to Joffrey. 

\SANSA: If$\ldots$ if I could see my father, talk to him about$\ldots$  

\CERSEI: You disappoint me, child. We have told you of your father's treason. Why would you want to speak to a traitor? 

\SANSA: I only meant that$\ldots$ What will happen to him? 

\CERSEI: That depends. 

\SANSA: On$\ldots$ on what? 

\CERSEI: On your brother. And on you. 

\ti{\CERSEI ~picks up the quill and holds it out to \SANSA, who eventually takes it.}

\scene

\textit{WINTERFELL} 

\ti{\ROBB, \LUWIN, and \THEON ~are discussing \SANSA's letter.}

\ROBB: \sd{Reading the letter.} Treason? Sansa wrote this? 

\LUWIN: It is your sister's hand, but the Queen's words. You are summoned to King's Landing to swear fealty to the new King. 

\ROBB: Joffrey puts my father in chains, now he wants his arse kissed? 

\LUWIN: This is a royal command, my lord. If you should refuse to obey$\ldots$

\ROBB: I won't refuse. His Grace summons me to King's Landing, I'll go to King's Landing. But not alone. Call the banners. 

\LUWIN: All of them, my lord? 

\ROBB: They've all sworn to defend my father, have they not? 

\LUWIN: They have. 

\ROBB: Now we see what their words are worth. 

\LUWIN: Mm.

\ti{\LUWIN ~exits.}

\THEON: Are you afraid? 

\ti{\ROBB ~holds out his hand, which is shaking.}

\ROBB: I must be. 

\THEON: Good. 

\ROBB: Why is that good? 

\THEON: It means you're not stupid. 



\scene

\textit{THE EYRIE} 

\ti{\CATELYN ~enters to \LYSA ~and \ROBYN. She waves a partly-unrolled message.}

\CATELYN: You've had this since dawn? 

\LYSA: He sent it to me, not you. I've only shown it to you as a courtesy. 

\CATELYN: A courtesy?! My husband has been taken prisoner. My son intends to declare war. 

\LYSA: A war? Your son against the Lannisters? You should go to him. Teach him patience. 

\CATELYN: Ned rots in a dungeon and you speak of patience? He is your brother by law! Does family mean nothing to you? 

\LYSA: Family means everything to me. And I will not risk Robyn's life to get caught up in another of your husband's wars. 

\ROBYN: I'm hungry. \sd{He starts unlacing the front of his mother's dress.}

\LYSA: Hush now, darling. You just ate. 

\CATELYN: You will not support us then? Do I understand you correctly? 

\ROBYN: But I'm hungry! 

\LYSA: Soon, love, soon. You're always welcome here, sister. But if you're asking me to send men from the Vale to fight$\ldots$  

\CATELYN: That is what I ask. 

\LYSA: Go on, sweet. Time for your bath. I'll feed you after. 

\ti{\ROBYN ~exits.}

\CATELYN: If you fear for the safety of your son$\ldots$  

\LYSA: Of course I fear for the safety of my son! Are you an idiot? They killed my husband. You say they shoved your boy from a window. These people will do anything. 

\CATELYN: And that is why we have to stop them. 

\LYSA: The knights of the Vale will stay in the Vale where they belong, to protect their lord. 


\scene

\textit{THE VALE} 

\ti{\BRONN ~and \TYRION ~are walking through the woods.  \TYRION ~is whistling.}

\BRONN: Will you shut up? There's hill tribes all around here. 

\TYRION: If I'm going to die, it may as well be with a song in my heart. 

\BRONN: I should just take your food and leave you here. Eh? What would you do then? 

\TYRION: Starve, most likely. 

\BRONN: You don't think I'd do it, do you? 

\TYRION: What do you want, Bronn? Gold? Women? Golden women? Stick with me and you'll have them all, for as long as I'm around and not for a moment longer. But you knew that. That is why you so valiantly took up arms to defend my honour. 

\BRONN: Fair enough.  But don't go looking for me to bend the knee and `my lord' you every time you take a shit. I'm not your toady and I'm not your friend. 

\TYRION: Though I would treasure your friendship, I'm mainly interested in your facility with murder. And if the day ever comes when you're tempted to sell me out, remember this: Whatever their price, I'll beat it. I like living. \sd{He whistles again.}

\ti{They make camp for the night.  Enter \SHAGGA, \TIMETT, and \CHELLA, stealthily.  \BRONN ~wakes.}

\BRONN: Tyrion. Tyrion. Tyrion. 

\ti{\TYRION ~wakes. \BRONN ~draws his sword. The hillfolk step out of the shadows.}

\TYRION: Come, share our fire. Help yourselves to our goat. 

\SHAGGA: When you meet your gods, you tell them Shagga son of Dolf of the Stone Crows sent you. 

\TYRION: I am Tyrion son of Tywin of clan Lannister. 

\SHAGGA: How would you like to die, Tyrion son of Tywin? 

\TYRION: In my own bed, at the age of 80 with a bellyful of wine and a girl's mouth around my cock. 

\SHAGGA: \sd{laughing} Take the half man. He can dance for the children. Kill the other one. 

\ti{The hill tribesmen draw their weapons and approach \BRONN, who prepares to fight.}

\TYRION: No no no no no! My$\ldots$ my House is rich and powerful. If you see us through these mountains, my father will shower you with gold. 

\SHAGGA: We have no use for a half man's promises.

\TYRION: Half a man maybe, but at least I have the courage to face my enemies. What do the Stone Crows do? Hide behind rocks and shiver when the knights of the Vale ride by? Are those the best weapons you could steal? Good enough for killing sheep, if the sheep don't fight back. Lannister smiths shit better steel. 

\ti{\SHAGGA ~strikes \TYRION ~across the left cheek with his axe, drawing blood.}

\SHAGGA: You think you can win us over with your trinkets? 

\ti{\TYRION ~pulls a large silver ring with a lion's head on it from the ring finger of his left hand, and hands it to \SHAGGA.  He puts it on the little finger of his right hand.}

\TYRION: That trinket is worth more than everything your tribe owns. But if you help us, Shagga son of Dolf, I will not give you trinkets. I will give you this. \sd{He spreads out his hands to encompass the surroundings.}

\SHAGGA: What is `this'? 

\TYRION: The Vale of Arryn. The Lords of the Vale have always spat upon the hill tribes. The Lords of the Vale want me dead. I believe it is time for new Lords of the Vale. 


\scene

\textit{THE WALL: THE KITCHEN} 

\ti{\JON, \SAM, and \PYP ~are preparing food.  Enter \ALLISER.}

\ALLISER: Now there's a rare sight$\ldots$ not only a bastard, but a traitor's bastard. 

\ti{After a long pause, \JON ~lunges at him with a knife.  \SAM ~and \PYP ~intercede.}

\SAM: Jon, no! 

\PYP: Jon, stop, put it down! 

\ALLISER: Blood will always tell. You'll hang for this, bastard. 

\ti{Exit \ALLISER.  Enter \JEOR.}

\JEOR: I told you not to do anything stupid. You're confined to quarters. Go. 


\scene

\textit{THE WALL: JON'S QUARTERS} 

\ti{\GHOST ~is whining and jumping at the door. \JON ~is lying down but not sleeping.}

\JON: Ghost, what's wrong?  Is something out there? 

\ti{\JON ~opens the door and follows \GHOST ~to \JEOR's room.}

\JON: Commander? \sd{To \GHOST.} Stay. \sd{\GHOST ~whines but sits down. \JON ~advances through an inner door.} Hello? Who's there? Lord Commander? 

\ti{The door slams behind him.  A \ZOMBIE ~is revealed and attacks. They fight. Outside, \GHOST ~is heard scrabbling at the door and growling. \JON ~runs the \ZOMBIE ~through, and he collapses. \JEOR ~enters}

\JEOR: Snow? 

\JON: Commander! 

\ti{The \ZOMBIE ~reanimates, and \JON ~grabs a lantern and throws it, setting the \ZOMBIE ~on fire.}

\JON: Move move! \sd{He hurries \JEOR ~out.}


\scene

\textit{COUNTRY OF THE LHAZAREEN}

\ti{The Khalasar have just conquered a Lhazareen village, and are ravishing and pillaging. \DAENERYS, \JORAH ~and \RAKHARO ~walk through, watching the carnage. They are followed by \DAENERYS' maidservants and others of her retinue.}

\DAENERYS: What did they do? 

\RAKHARO: Haesh rakhi davrae zafraan. Khal Drogo vazhoe mora azzafrokea, majin azzafroki vazhi kishaan ma hoshor ma tasokh ma tawakof. [Lamb men make good slaves. Khal Drogo will make a gift of them to the slavers, and the slavers will give us gold and silk and steel.] 

\DAENERYS: I thought the Dothraki didn't believe in money. 

\JORAH: Gold to hire ships, Princess, ships to sail to Westeros. 

\ti{Enter \MAGO, dragging \MIRRI ~onstage and preparing to rape her.}

\DAENERYS: Jorah, make them stop. 

\JORAH: Khaleesi? 

\DAENERYS: You heard me. 

\JORAH: These men have shed blood for their Khal. Now they claim their rewards. 

\RAKHARO: Me vafik, zhey khaleesi. Dothraki chomoe mae. Hash athlaqar mae zireyesee khaleesies hash anha afichak shafkea lekh moon. [She's a lamb girl, Khaleesi. The riders do her honour. If her wailing offends the Khaleesi, I will bring you her tongue.] 

\JORAH: Princess, you have a gentle heart, but this is how it's always been. 

\DAENERYS: I do not have a gentle heart, Ser. Ti mae k'asi, che Khal Drogo anesa valzerikh. [Do as I command or Khal Drogo will know the reason why.]

\ti{\RAKHARO ~approaches \MAGO ~and pulls him away from \MIRRI.  They scuffle.}

\MAGO: Me qorasokh anni! Anha afichak mae m'arakhoon! [She is my prize. I will take her with an arakh.] 

\ti{\JORAH ~puts \MIRRI's cloak back over her shoulders and helps her to her feet.}

\JORAH: Come! \sd{to \DAENERYS} What do you want done with them? 

\DAENERYS: Bring her to me. And those women there. 

\JORAH: You cannot claim them all, Princess. 

\DAENERYS: I can, and I will. 

\ti{They go before \DROGO.}

\MAGO: Me Fati! Khaleesi vazha anhaan qorasokh anni, ch'anha afichak mae m'arakhoon anni! [It's an insult! Khaleesi will give me my prize or I will take it with my arakh.] 

\DROGO: Me vastoe hatif anni; ahhazaan yer nemo vacchaki. [She will speak before me; until then you will keep yourself quiet.]  \sd{to \DAENERYS} Zhey jalan atthirari anni, Mago asta meshafka fich qorasokh mae,ohara haeshi rakhi fin qoraso me asaja mae. Asti anhaan hash jini jila. [Moon of my life, Mago says you have taken his spoils, a daughter of the lamb man who was his to mount. Tell me the truth of this.] 

\DAENERYS: Mago asta k'athjilari, zhey shekh ma shieraki anni. Anha ray qoraso san ohari asshekh majin mori nem vos osaji. [Mago speaks the truth, my sun and stars. I have claimed many daughters this day so they cannot be mounted.] 

\DROGO: Jini athvilajerar. Jin chiorisi zafra ajjin, majin kisha ataki morea ven me vallayafa kisha. [This is the way of war. These women are slaves now to do with as we please.] 

\DAENERYS: Anha nem allayafak vassandik mora. Hash dothraki shafki'th saji mora hash mori jif kemoe ma moroa. [It pleases me to keep them safe. If your riders would mount them, let them take them as wives.] 

\QOTHO: Hash hrazef gova vaf? [Does the horse mate with the lamb?] 

\DAENERYS: Zhavvorsa vadakhera ma hrazef ma vaf akkate. [The dragon feeds on horse and lamb alike.] 

\MAGO: Yer ifak. Yer assoo anna vosecchi. [You're a foreigner. You do not command me.] 

\DAENERYS: Anha Khaleesi. Anha assok yera sekosshi. [I am Khaleesi. I do command you.] 

\DROGO: Tihi kifinosi me ivezhofoe? Hazak rizh anni mra me: Vezh fini Asaja Rhaesheseres, fini nirra mae vorsasoon mae. [See how fierce she grows? That's my son inside her, the stallion that will mount the world, filling her with his fire.] Anha acharak vos ale. Zhey Mago, anha acharak vos ale. Ezas eshna gech ahilee. [I will hear no more. Mago, find somewhere else to stick your cock.] 

\MAGO: \sd{spitting on the ground and raising his arakh against \DROGO} Khal fines assoe mezhah jahakmeni vos khal. [A Khal who takes orders from a foreign whore is no Khal.] 

\ti{\QOTHO ~steps in front of \DROGO ~with his arakh raised to defend him.}

\DROGO: Ohos! Os! [Be still. Don't move]. \sd{\QOTHO ~steps back.} Anha vazhok khadoes yeroon virsalat. Anha ochomok yeraan kijinosi. [I will not have your body burned. I will not give you that honour.] \sd{He stands and approaches \MAGO ~until \MAGO's raised arakh is pressed against the left side of his bare chest, making a wound, which he ignores.} Inte vadakhie tihoa ma khewo afilki vi gadimaan. [The beetles will feed on your eyes. The worms will crawl through your lungs]. \sd{He approaches further, and \MAGO ~retreats, before suddenly attacking. \DROGO ~easily dodges the arakh.} Eyel varthasoe she ilekaan rikhoya arrekaan vekha vosi yeroon vosma tolorro! [The rain will fall on your rotting skin until nothing is left of you but bones.] 

\ti{\DROGO ~drops his weapons and charges at \MAGO.  They struggle together briefly.}

\MAGO: Atte yer eth addrivi anna. [First you have to kill me.] 

\DROGO: Jin anha ray et. [I already have.]

\ti{\DROGO ~cuts \MAGO's throat with his own arakh, then pulls his tongue out through the gash and raises it aloft for all to see. Then he throws it down and sits down again.}

\DAENERYS: \sd{rushing over to look at \DROGO's wound} Shekh ma shieraki anni zisa. [My sun and stars is hurt.] 

\DROGO: Me zisosh, zhey jalan atthirari anni. [A scratch, moon of my life.] 

\DAENERYS: Finne koalaki? [Where are the healers.] 

\DROGO: Jini osto afisi. [This is the bite of a fly.] 

\MIRRI: Anha laz rhelak dothrakes vezhvena ha zisoshaan mae. [I can help the great rider with his cut.] 

\QOTHO: Khal zigeree vo rhellay ha zafroon fini govi oqet. [The Khal needs no help from slaves who lie with sheep.] 

\DAENERYS: Me anni. Me vastoe. [She's mine. Let her speak.] 

\MIRRI: Thank you, silver lady. 

\DAENERYS: Who are you? 

\MIRRI: I am named Mirri Maz Duur. I was the godswife of this temple.  

\RAKHARO: Maegi. [Witch.] \sd{He spits on the ground.}

\MIRRI: My mother was godswife here before me. She taught me how to make healing smokes and ointments. All men are of one flock, so my people believe. The Great Shepherd sent me to Earth to heal his---

\ti{\RAKHARO ~slaps \MIRRI ~across the face.}

\RAKHARO: Ase sekke. Ase maegi izzi char. [Too many words. The witch's words poison the ears.] 

\MIRRI: Lamb or lion, his wound must be washed and sewn or it will fester. 

\DAENERYS: Azhas maan affisat zis yeri, shekh ma shieraki anni. Me azzisa anna jin tihat meyer qiyae. [Let her clean your wound, my sun and stars. It makes me hurt to see you bleed.] 

\ti{\DROGO ~finally grunts agreement and \MIRRI ~approaches to examine him.}


\scene

\textit{WINTERFELL: THE GREAT HALL}

\ti{\ROBB, \THEON, \BRAN ~and \UMBER ~are feasting together,
surrounded by Stark bannermen. \ROBB's wolf \textbf{GREY WIND} sits nearby.} 

\UMBER: For thirty years I've been making corpses out of men, boy. I'm the man you want leading the vanguard. 

\ROBB: Galbart Glover will lead the van. 

\UMBER: The bloody Wall will melt before an Umber marches behind a Glover. I will lead the van or I will take my men and march them home. 

\ROBB: You are welcome to do so, Lord Umber. \sd{He gets to his feet.} And when I am done with the Lannisters I will march back north, root you out of your keep and hang you for an oathbreaker. 

\UMBER: Oathbreaker, is it?! \sd{He leaps up and dashes his plate to the floor.} I'll not sit here and swallow insults from a boy so green he pisses grass. 

\ti{\UMBER ~makes to draw his sword. \THEON ~jumps up. \textbf{GREY WIND} runs over the table and knocks \UMBER ~to the floor, biting off two of his fingers.}

\ROBB: My lord father taught me it was death to bare steel against your liege lord. But doubtless the Greatjon only meant to cut my meat for me. 

\UMBER: \sd{Getting up.} Your meat$\ldots$ is bloody tough. 

\ti{He laughs, and gradually everyone joins in.}

\scene

\textit{WINTERFELL: BRAN'S CHAMBER} 

\ti{\BRAN ~is sleeping.  \ROBB ~enters and wakes him.}

\BRAN: What is it? What's happened? 

\ROBB: Shh, it's all right. 

\BRAN: Where are you going? 

\ROBB: South. For father. 

\BRAN: But it's the middle of the night. 

\ROBB: The Lannisters have spies everywhere. I don't want them to know we're coming. 

\BRAN: They have more men than we do. 

\ROBB: Aye, they do. 

\BRAN: Can't I come with you? I can ride now. You've seen me riding. And I won't get in the way, I---  

\ROBB: There must always be a Stark at Winterfell. Until I return that will be you. You are not to leave the castle walls while we are gone. Do you understand? Listen to Maester Luwin. Look after your little brother. 

\BRAN: I will. 

\ROBB: I'll send letters whenever I can, but if you don't hear from me, don't be scared. Until I return. 

\ti{\ROBB ~leaves, then \RICKON ~enters.}

\BRAN: How long have you been hiding out there? Robb will be looking for you to say goodbye. 

\RICKON: They've all gone away. 

\BRAN: They'll be back soon. Robb will free father and they'll come back with mother. 

\RICKON: No, they won't. \sd{He leaves.}


\scene

\textit{WINTERFELL: THE GODSWOOD} 

\ti{\BRAN ~is praying before the heart tree.}

\BRAN: Please watch over Robb. And watch over all the other men from Winterfell. And Theon too, I suppose. 

\ti{Enter \OSHA ~with shackles around her ankles.}

\OSHA: You hear them, boy? The old gods are answering you. 

\BRAN: What are you doing here? 

\OSHA: They're my gods too. Beyond the Wall, they're the only gods. Even slaves are allowed to pray. 

\BRAN: You're not a slave. 

\ti{She shakes her chains.}

\BRAN: Well, your friend did put a knife to my throat. 

\OSHA: I'm not complaining, little lord, just telling truths. 

\BRAN: What did you mean about hearing the gods? 

\OSHA: You asked them, they're answering you. Shh. Open your ears. 

\sfx{Wind whistles through the heart tree's leaves.}

\BRAN: It's only the wind. 

\OSHA: Who do you think sends the wind if not the gods? They see you, boy. They hear you. Your brother will get no help from them where he's going. The old gods have no power in the South. The weirwoods there were all cut down a long time ago. How can they watch when they have no eyes? 

\ti{Enter \HODOR, naked.}

\OSHA: Well, there's a big man. He has giants' blood in him or I'm the Queen. 

\BRAN: Go back and find your clothes, Hodor. Go dress. 

\HODOR: Hodor. \sd{He exits.}

\BRAN: Are there really giants beyond the Wall? 

\OSHA: Giants and worse than giants. I tried telling your brother, he's marching the wrong way. All these swords, they should be going north, boy. North, not south! The cold winds are rising.

\sfx{Wind rustles through the tree again.}


\scene

\textit{THE WALL} 

\ti{\JON, \SAM, \PYP ~and other men of the Night's Watch stand around a fire, on which the remains of the two ZOMBIES are burning.}

\SAM: They were touched by White Walkers. That's why they came back. That's why their eyes turned blue. Only fire will stop them. 

\JON: How do you know that? 

\SAM: I read about it in a book$\ldots$ a very old book in Maester Aemon's library. 

\JON: What else did the book say? 

\SAM: The White Walkers sleep beneath the ice for thousands of years. And when they wake up$\ldots$  

\PYP: And when they wake up, what? 

\SAM: I hope the Wall's high enough. 


\scene

\textit{ROBB'S CAMP} 

\ti{\CATELYN ~and \RODRIK ~ride towards the camp, where \ROBB, \UMBER, \GLOVER ~and other Stark bannermen are discussing strategy around a table.}

\RODRIK: Summer snows, my lady. 

\CATELYN: Robb's brought the North with him. 

\ROBB: The river lords are falling back with Jaime Lannister at their heels. And Lord Tywin is bringing around a second Lannister army from the South. Our scouts confirm it's even larger than the Kingslayer's. 

\UMBER: One army or two, the kings in the North threw back hosts ten times as large. 

\ti{\CATELYN ~and \RODRIK ~approach \ROBB.}

\ROBB: Mother!

\CATELYN: You look well. 

\UMBER: Lady Catelyn, you're a welcome sight in these troubled times. 

\GLOVER: We had thought not to meet you here, my lady. 

\CATELYN: I had not thought to be here. I would speak with my son alone. I know you will forgive me, my lords. 

\UMBER: You heard her! Move your arses! Come on, out. \sd{To \THEON} You too, Greyjoy. Are you bloody deaf? Have no fear, My Lady. We'll shove our swords up Tywin Lannister's bunghole and then it's on to the Red Keep to free Ned. 

\ti{Exit all except \CATELYN ~and \ROBB.  They embrace.}

\CATELYN: I remember the day you came into this world red-faced and squalling. And now I find you leading a host to war. 

\ROBB: There was no one else. 

\CATELYN: No one? Who were those men I saw here? 

\ROBB: None of them are Starks. 

\CATELYN: All of them are seasoned in battle. 

\ROBB: If you think you can send me back to Winterfell$\ldots$  

\CATELYN: Oh, would that I could. 

\ROBB: There was$\ldots$ a letter. From Sansa. \sd{He finds the letter and hands it to \CATELYN.}

\CATELYN: From the Queen, you mean. \sd{She reads it.} There's no mention of Arya. 

\ROBB: No. 

\CATELYN: How many men do you have? 

\ROBB: Eighteen thousand. If I go to King's Landing and bend my knee to Joffrey$\ldots$  

\CATELYN: You would never be allowed to leave. No. Our best hope$\ldots$ our only hope$\ldots$ is that you can defeat them in the field. 

\ROBB: And if I lose? 

\CATELYN: Do you know what happened to the Targaryen children when the Mad King fell?

\ROBB: They were butchered in their sleep.

\CATELYN: On the orders of Tywin Lannister. And the years have not made him kinder. If you lose, your father dies, your sisters die. We die. 

\ROBB: Well, that makes it simple then. 

\CATELYN: I suppose it does. 


\scene

\textit{THE LANNISTER CAMP} 

\ti{\TYRION, \SHAGGA, \BRONN, \TIMETT, \CHELLA ~and a host of Hill men approach the camp, where \TYWIN, ~\KEVAN ~and other Lannister men are discussing strategy.}

\TYRION: From here it might be best if Bronn and I continue alone. 

\SHAGGA: Best for Tyrion son of Tywin. Not best for me. If the half man betrays us, Shagga son of Dolf will cut off his manhood$\ldots$  

\TYRION: And feed it to the goats, yes. All right then. Time to meet my father. 

\ti{\TYRION, \SHAGGA, \BRONN, \TIMETT ~and \CHELLA ~approach \TYWIN's group.} 

\KEVAN: Tyrion. 

\TYRION: Uncle. Father. 

\TYWIN: The rumors of your demise were unfounded. 

\TYRION: Sorry to disappoint you. 

\TYWIN: And who are these$\ldots$ companions of yours? 

\TYRION: This is Shagga Son of Dolf, Chieftain of the Stone Crows. Timett son of Timett, ruler of the Burned Men. This fair maid is Chella daughter of Cheyk, leader of the Black Ears. And here we have Bronn son of$\ldots$ 

\BRONN: You wouldn't know him. 

\TYRION: May I present my lord father, Tywin son of Tytos of House Lannister, Lord of Casterly Rock and Warden of the West? Kind of you to go to war for me. 

\TYWIN: You left us no choice. The honour of the House was at stake. Your brother would never have submitted to capture so meekly. 

\TYRION: We have our differences, Jaime and I. He's braver. I'm better looking. 

\TYWIN: He's been covering himself in glory. 

\KEVAN: Jaime smashed the river lords at the Golden Tooth, and now lays siege to Riverrun, Catelyn Stark's homeland. 

\TYRION: And the Starks? Lord Eddard? 

\TYWIN:$\ldots$ is our hostage. He will lead no armies from his dungeon cell. 

\TYRION: How did my sweet sister persuade the King to imprison his dear friend Ned? 

\TYWIN: Robert Baratheon is dead. Joffrey rules in King's Landing. 

\TYRION: My sister rules, you mean. 

\KEVAN: Stark's son has called his banners. He moves south with a strong host. 

\TYWIN: A green boy. One taste of battle and he'll run back to Winterfell with his tail between his legs. 

\TYRION: Maybe. Though the boy does have a certain belligerence. You'd like him. While we're on the subject of war, I made promises to my friends here and a Lannister always pays his debts. We shall require 3,000 helms and shields, plus swords, pikes, gorgets, maces$\ldots$  

\ti{\PAGE ~enters and kneels.}

\PAGE: If it please my lord, Ser Addam bids me report that the northmen have crossed the Neck. 

\TYWIN: The wolf rushes into the lion's jaws. So be it. Kevan, command the drummers beat assembly. \sd{\KEVAN ~exits.} And send word to Jaime that I am moving against Robb Stark. 

\PAGE: At once, my lord. \sd{He exits.}

\TYWIN: \sd{Examining the Hill men carefully.} It is said that the men of the mountain clans are great warriors. Ride with me against my enemies and you shall have all my son promised you and more. 

\SHAGGA: Only if the half man fights with us. Until we hold the steel he pledged us, the little lion's life is ours. 


\scene

\textit{ROBB'S CAMP} 

\ti{\ROBB, \RODRIK, \UMBER, \THEON ~and \CATELYN ~are examining a map, on which chess pieces have been placed to indicate troop locations.}

\RODRIK: The scouts report Lord Tywin moves north. We need to get him on broken ground, put his knights at a disadvantage. 

\UMBER: No, we need to get around him and break Jaime Lannister's siege of Riverrun. Do that and the river lords will join us. 

\ROBB: To do either we need to cross the river, and the only crossing is at the Twins. 

\THEON: Lord Frey controls that bridge. Your father's bannerman. 

\CATELYN: The late Lord Frey my father calls him. At the Trident, he didn't appear until the battle was done. Some men take their oaths more seriously than others. 

\THEON: Robb's right. We need that bridge. 

\UMBER: So what's it going to be? Do we move against Jaime or Lord Tywin? 

\ti{\STARKGUARD ~enters, dragging a Lannister \SPY.}

\STARKGUARD: Your pardon, my lords. We've captured a Lannister scout. 

\ti{\ROBB ~quickly moves to conceal the map and chess pieces.}

\UMBER: Don't worry, lad. He won't be leaving this tent with his head. 

\ROBB: Where did you find him? 

\STARKGUARD: In the brush above the encampment. He looked to be counting. 

\ROBB: \sd{To \SPY.} How high did you get? 

\SPY: Twenty thousand. Maybe more. 

\RODRIK: You don't have to do this yourself. Your father would understand$\ldots$  

\ROBB: My father understands mercy, when there is room for it. And he understands honour$\ldots$ and courage. Let him go. 

\CATELYN: Robb. 

\ROBB: Tell Lord Tywin winter is coming for him. Twenty thousand northerners marching south to find out if he really does shit gold. 

\SPY: Yes, my lord. Thank you, my lord. 

\ti{The \STARKGUARD ~bundles the \SPY ~out.}

\UMBER: Are you touched, boy? Letting him go? 

\ROBB: You call me boy again. Go on. 

\ti{\UMBER ~growls and leaves.}


\scene

\textit{KING'S LANDING: THE COURTROOM}

\ti{\JOFFREY ~sits on the Iron Throne, with \PYCELLE ~on his left, reading from a proclamation. \VARYS ~and \LITTLEFINGER ~also stand on his left. \CERSEI ~is seated on the King's right, and a \HERALD ~stands on her right. The \HOUND ~stands behind the King. Members of the Kingsguard including \SELMY ~and \MERYN ~stand in a row in front of \JOFFREY, facing out into the courtroom.  Members of the City Watch stand in a row at one side. Courtiers look on, and \JANOSSLYNT ~stands before the King. \SANSA ~enters and stands among the courtiers.}

\PYCELLE: It is also the wish of His Grace that his loyal servant Janos Slynt, Commander of the City Watch, be granted the ancient seat of Harrenhal, and that his sons and grandsons shall hold this honour after him until the end of time. \sd{\JANOSSLYNT ~bows and joins the members of the City Watch.} In the place of the traitor Eddard Stark, it is the wish of His Grace that Tywin Lannister, Lord of Casterly Rock and Warden of the West, be appointed Hand of the King. Lastly, in these times of treason and turmoil, it is the view of the council that the life and safety of King Joffrey be of paramount importance. 

\CERSEI: \sd{Rising to her feet.} Ser Barristan Selmy. 

\ti{\SELMY ~leaves his place in the row of Kingsguard, and kneels before the King.}

\SELMY: Your Grace, I am yours to command. 

\CERSEI: Rise, Ser Barristan. You may remove your helm. \sd{He does so.} You have served the realm long and faithfully. Every man and woman in the Seven Kingdoms owes you thanks. But it is time to put aside your armour and your sword. It is time to rest and look back with pride on your many years of service. 

\SELMY: Your Grace, the Kingsguard is a sworn brotherhood. Our vows are taken for life. Only death relieves us of our sacred trust. 

\CERSEI: Whose death, Ser Barristan? Yours or your King's? 

\JOFFREY: You let my father die. You're too old to protect anybody. 

\SELMY: Your Grace$\ldots$ 

\CERSEI: The council has determined that Ser Jaime Lannister will take your place as Lord Commander of the Kingsguard.  

\SELMY: The man who profaned his blade with the blood of the King he had sworn to defend! 

\CERSEI: Careful, Ser. 

\VARYS: We have nothing but gratitude for your long service, good Ser. You shall be given a stout keep beside the sea, with servants to look after your every need. 

\SELMY: A hall to die in and men to bury me. \sd{Unbuckling his breastplate.} I am a knight. I shall die a knight. \sd{He throws his breastplate, helm and cloak angrily to the floor, then removes his gauntlets and adds them to the pile.}

\LITTLEFINGER: A naked knight, apparently.

\ti{Everyone except \SANSA ~and \SELMY ~laughs. \SELMY ~draws his sword, and the other members of the Kingsguard, the City Guard and the \HOUND ~all draw theirs in response.}

\SELMY: \sd{To \MERYN ~and the other Kingsguard.} Even now I could cut through the five of you like carving a cake! Here, boy! \sd{He throws his sword on the ground before \JOFFREY, next to the pile of armour.} Melt it down and add it to the others. \sd{He exits and everyone sheathes their swords.}

\HERALD: If any man in this hall has other matters to set before His Grace, let him speak now or go forth and hold his silence. 

\SANSA: Your Grace. 

\JOFFREY: Come forward, my lady. 

\ti{\SANSA ~moves to stand before the King.}

\HERALD: The Lady Sansa of House Stark. 

\CERSEI: Do you have some business for the King and the council, Sansa? 

\SANSA: I do. \sd{She kneels.} As it please Your Grace, I ask mercy for my father, Lord Eddard Stark, who was Hand of the King. 

\PYCELLE: Treason is a noxious weed. It should be torn out, root$\ldots$  

\JOFFREY: Let her speak. I want to hear what she says. 

\SANSA: Thank you, Your Grace. 

\LITTLEFINGER: Do you deny your father's crime? 

\SANSA: No, my lords. I know he must be punished. All I ask is mercy. I know my lord father must regret what he did. He was King Robert's friend and he loved him. You all know he loved him. He never wanted to be Hand until the King asked him. They must have lied to him$\ldots$ Lord Renly or Lord Stannis or somebody. They must have lied! 

\JOFFREY: He said I wasn't the King. Why did he say that? 

\SANSA: He was badly hurt. Maester Pycelle was giving him milk of the poppy. He wasn't himself. Otherwise he never would have said it. 

\VARYS: A child's faith$\ldots$ such sweet innocence. And yet they say wisdom oft comes from the mouths of babes. 

\PYCELLE: Treason is treason! 

\JOFFREY: Anything else? 

\SANSA: If you still have any affection in your heart for me, please do me this kindness, Your Grace. 

\JOFFREY: Your sweet words have moved me. But your father has to confess. He has to confess and say that I'm the King$\ldots$ or there'll be no mercy for him. 

\SANSA: He will. 

\end{document}
