\input{preamble}
\input{ep09_cast}
\title{Episode 9 (S1E9): Baelor}
\author{}
\date{}
\maketitle

\input{ep09_casttable}


\scene

\textit{KING'S LANDING: NED'S CELL} 

\ti{\VARYS ~enters to \NED ~who is chained to the wall.}

\VARYS: You've seen better days, My Lord. 

\NED: Another visit? It seems you're my last friend. 

\VARYS: No no, many still love you. Sansa came to court this morning to plead for your life. 

\NED: On her knees, begging for me, hmmm. Did you laugh with the others? 

\VARYS: You do me wrong, My Lord. Your blood is the last thing I want. 

\NED: I don't know what you want. I've given up trying to guess. 

\VARYS: When I was still a boy $\ldots$ before they cut my balls off with a hot knife $\ldots$  I traveled with a group of actors through the free cities. They taught me that each man has a role to play. The same is true at court. I am the Master of Whisperers. My role is to be sly, obsequious and without scruples. I'm a good actor, My Lord. 

\NED: Huh. Can you free me from this pit? 

\VARYS: I could. But will I? No. As I said, I'm no hero. 

\NED: What do you want? Tell me. No riddles, no stories $\ldots$ tell me, what do you want? 

\VARYS: Peace. Did you know that your son is marching south with an army of Northmen? Loyal lad $\ldots$ fighting for his father's freedom. 

\NED: Robb? He's just a boy. 

\VARYS: Boys have been conquerors before. But the man giving Cersei sleepless nights is the King's $\ldots$ the late King's brother. Lord Stannis has the best claim to the Throne, he is a proven battle commander and he is utterly without mercy. 

\NED: Stannis Baratheon is Robert's true heir. The Throne is his by rights. 

\VARYS: Tsk tsk. Sansa pleaded so sweetly for your life, it would be a shame to throw it away. Cersei is no fool. She knows a tame wolf is more use to her than a dead one. 

\NED: You want me to serve the woman who murdered my King, who butchered my men, who crippled my son? 

\VARYS: I want you to serve the realm! Tell the Queen you will confess your vile treason, tell your son to lay down his sword and proclaim Joffrey as the true heir. Cersei knows you as a man of honour. If you give her the peace she needs and promise to carry her secret to your grave, I believe she will allow you to take the Black and live out your days on the Wall with your brother and your bastard son. 

\NED: You think my life is some precious thing to me? That I would trade my honour for a few more years of $\ldots$ of what? You grew up with actors. You learned their craft and you learned it well. But I grew up with soldiers. I learned how to die a long time ago. 

\VARYS: Pity. Such a pity. What of your daughter's life, My Lord? Is that a precious thing to you? 


\scene

\textit{ROBB'S CAMP} 

\ti{\ROBB, \THEON, \CATELYN, and \UMBER ~confer outside the Twins.  \ROBB ~is reading a message attached to a dead raven.}

\ROBB: It's a birthday message to his grand-niece Walda. 

\THEON: Or so Walder Frey would have you think. 

\CATELYN: Keep shooting them down. We can't risk Lord Walder sending word of your movements to the Lannisters. 

\ROBB: He's grandfather's bannerman. We can't expect his support? 

\UMBER: Expect nothing of Walder Frey and you'll never be surprised. 

\ROBB: Look. Father rots in a dungeon. How long before they take his head? We need to cross the Trident and we need to do it now. 

\THEON: Just march up to his gates and tell him you're crossing. We've got five times his numbers. You can take the Twins if you have to. 

\UMBER: Not in time. Tywin Lannister marches north as we speak. 

\CATELYN: The Freys have held the crossing for 600 years, and for 600 years they have never failed to exact their toll. 

\ROBB: Have my horse saddled and ready. 

\UMBER: Enter the Twins alone and he'll sell you to the Lannisters. Or throw you in a dungeon. Or slit your throat. 

\ROBB: My father would do whatever it took to secure our crossing. Whatever it took. If I'm going to lead this army, I can't have other men doing my bargaining for me. 

\CATELYN: I agree. I'll go. 

\THEON: You can't! 

\CATELYN: I have known Lord Walder since I was a girl. He would never harm me. 

\UMBER: Unless there was a profit in it. 


\scene

\textit{WALDER FREY'S HALL} 

\ti{\FREY ~is holding court, flanked by his \textbf{WIFE} and sons \STEVRONFREY ~and \WALDERRIVERS.}

\FREY: What do you want? 

\CATELYN: It is a great pleasure to see you again after so many years, My Lord. 

\FREY: Oh spare me. Your boy's too proud to come before me himself. What am I supposed to do with you? 

\STEVRONFREY: Father, you forget yourself. Lady Stark is here-- 

\FREY: Who asked you? You're not Lord Frey yet, not until I die. Do I look dead to you? 

\WALDERRIVERS: Father, please $\ldots$  

\FREY: I need lessons in courtesy from you, bastard? Your mother would still be a milkmaid if I hadn't squirted you into her belly. All right, you come forward. 

\ti{\CATELYN ~steps forward, and \FREY ~kisses her hand.}

\FREY: There. Now that I've observed the courtesies, perhaps my sons will do me the honour of shutting their mouths. 

\CATELYN: Is there somewhere we can talk? 

\FREY: We're talking right now. \sd{Off her look.} Fine. Out! All of you! \ti{(To his wife.)} You too. \sd{to \CATELYN ~as the others leave.} You see that? Fifteen, she is. A little flower. And her honey's all mine. 

\CATELYN: I'm sure she will give you many sons. 

\FREY: Huh. Your father didn't come to the wedding. 

\CATELYN: He is quite ill, My Lord. 

\FREY: Didn't come to the last one either. Or the one before that. Your family has always pissed on me. 

\CATELYN: My Lord, I-- 

\FREY: Don't deny it. You know it's true. The fine Lord Tully would never marry any of his children to mine. 

\CATELYN: I'm sure there were reasons why $\ldots$  

\FREY: I didn't need reasons. I needed to get rid of sons and daughters. You see how they pile up? Why are you here? 

\CATELYN: To ask you to open your gates, My Lord, so my son and his bannermen may cross the Trident and be on their way. 

\FREY: Why should I let him? 

\CATELYN: If you could climb your own battlements, you would see that he has 20,000 men outside your walls. 

\FREY: They'll be 20,000 corpses when Tywin Lannister gets here. Don't try and frighten me, Lady Stark. Your husband's in a cell beneath the Red Keep and your son's got no fur to keep his balls warm. 

\CATELYN: You swore an oath to my father. 

\FREY: Oh yes, I said some words. And I swore oaths to the Crown too, if I remember right. Joffrey's king now, which makes your boy and his corpses-to-be nothing but rebels, it seems to me. If I had the sense the gods gave a fish, I'd hand you both over to the Lannisters. 

\CATELYN: Why don't you? 

\FREY: Stark, Tully, Lannister, Baratheon, give me one good reason why I should waste a single thought on any of you? 


\scene

\textit{THE WALL: JEOR'S CHAMBER} 

\ti{\JON ~and \JEOR ~are talking.}

\JEOR: When does Aemon think you'll be able to use that hand? 

\JON: Soon, he says. 

\JEOR: Good. You'll be ready for this then. 

\ti{He hands \JON ~a sword.} 

\JEOR: I thought a wolf was more appropriate for you than a bear, so I had a new pommel made. It's called Longclaw. Works as well for a wolf as a bear, I think. 

\JON: This is Valyrian steel. 

\JEOR: It was my father's sword, his father before him. The Mormonts have carried it for five centuries. It was meant for my son Jorah. He brought dishonour to our House, but he had the grace to leave the sword before he fled from Westeros. 

\JON: My Lord, you honour me, but I can't $\ldots$  

\JEOR: Oh, you can and you will. I wouldn't be standing here if it wasn't for you and your beast. A bloody dead man tried to kill me. So you'll take it. I'll hear no more about it. Is that understood? 

\JON: Yes, My Lord. 

\JEOR: Right. Now don't think this means I approve of this nonsense with you and Alliser Thorne. That's a man's sword, it'll take a man to wield it. 

\JON: I'll apologize to Ser Alliser tonight. 

\JEOR: No you won't. I sent him to King's Landing yesterday. The hand that your wolf tore off that thing's wrist.  I've ordered Thorne to lay it at the feet of this boy king. That should get young Joffrey's attention. And it puts a thousand leagues between you and Thorne. Now go and put your sword somewhere safe and bring me my supper. 

\JON: Yes, My Lord. 


\scene

\textit{THE WALL: IN THE YARD} 

\ti{\JON ~enters to \PYP, and \GRENN. \SAM ~is sitting in the corner.}

\PYP: Go on, let's have a look. 

\JON: At what? 

\GRENN: The sword! Show us the sword. 

\PYP: Come on, I want to have a look at it in the light. Give it here! 

\ti{\JON ~hands over the sword and they wander off with it.  \JON ~sits next to \SAM, who is looking anxious.}

\JON: What is it? 

\SAM: I can't. 

\JON: You can't what? 

\SAM: I'm really not supposed to say. 

\JON: And yet you really want to say. You want to say that $\ldots$? 

\SAM: There was a raven. I read the message to Maester Aemon. It's your brother Robb. 

\JON: What? What about him? 

\SAM: He's heading south. To war. All his bannermen have rallied to his side. They'll keep him safe. 

\JON: I should be there. I should be with him. 


\scene

\textit{BENEATH THE TWINS} 

\ti{\CATELYN ~and \ROBB ~are talking.}

\ROBB: Well? What did he say? 

\CATELYN: Lord Walder has granted your crossing. His men are yours as well, less the four hundred he will keep here to hold the crossing against any who would pursue you. 

\ROBB: And what does he want in return? 

\CATELYN: You will be taking on his son Olyvar as your personal squire. He expects a knighthood in good time. 

\ROBB: Fine, fine. And? 

\CATELYN: And Arya will marry his son Waldron when they both come of age. 

\ROBB: She won't be happy about that. And? 

\CATELYN: And when the fighting is done $\ldots$ you will marry one of his daughters. Whichever you prefer. He has a number he thinks will be $\ldots$ suitable. 

\ROBB: I see. Did you get a look at his daughters? 

\CATELYN: I did. 

\ROBB: And? 

\CATELYN: One was $\ldots$ Do you consent? 

\ROBB: Can I refuse? 

\CATELYN: Not if you want to cross. 

\ROBB: Then I consent. 


\scene

\textit{THE WALL} 

\ti{\JON enters \AEMON's chambers.}

\JON: Sam said you wanted to see me? 

\AEMON: I did indeed.  Tell me, did you ever wonder why the men of the Night's Watch take no wives and father no children? 

\JON: No. 

\AEMON: So they will not love. Love is the death of duty. If the day should ever come when your lord father was forced to choose between honour on the one hand and those he loves on the other, what would he do? 

\JON: He would do whatever was right. No matter what. 

\AEMON: Then Lord Stark is one man in 10,000. Most of us are not so strong. What is honour compared to a woman's love? And what is duty against the feel of a newborn son in your arms? Or a brother's smile? 

\JON: Sam told you. 

\AEMON: We're all human. Oh, we all do our duty when there's no cost to it. honour comes easy then. Yet sooner or later in every man's life there comes a day when it is not easy, a day when he must choose. 

\JON: And this is my day? Is that what you're saying? 

\AEMON: Oh, it hurts, boy. Oh yes. I know. 

\JON: You do not know! No one knows.  I may be a bastard, but he is my father and Robb is my brother. 

\AEMON: The Gods were cruel when they saw fit to test my vows. They waited till I was old. What could I do when the ravens brought the news from the South $\ldots$ the ruin of my House, the death of my family? I was helpless, blind, frail. But when I heard they had killed my brother's son, and his poor son $\ldots$ and the children! Even the little children. 

\JON: Who are you? 

\AEMON: My father was Maekar, the first of his name. My brother Aegon reigned after him when I had refused the Throne. And he was followed by his son Aerys, whom they called the Mad King. 

\JON: You're Aemon Targaryen. 

\AEMON: I'm a Maester of the Citadel, bound in service to Castle Black and The Night's Watch. I will not tell you to stay or go. You must make that choice yourself, and live with it for the rest of your days. As I have. 



\scene

\textit{LANNISTER CAMP} 

\ti{\TYWIN, \KEVAN, and \TYRION ~are in council.}

\KEVAN: Our scouts tell us the Stark host has moved south from the Twins with Lord Frey's levies in tow. They're a day's march north. 

\TYWIN: The boy may lack experience and sense, but he does have a certain mindless provincial courage. 

\TYRION: Ah. Oh, do continue. Didn't mean to interrupt. 

\TYWIN: I do hope your savages are going to be of some use, otherwise we've wasted good steel on them. 

\KEVAN: The great hairy one insisted he must have two battle axes $\ldots$ heavy black steel, double-sided. 

\TYRION: Shagga likes axes. 

\TYWIN: When the battle commences, you and your wildlings will be in the vanguard. 

\TYRION: The vanguard? 

\TYWIN: Mm-hmm. 

\TYRION: Me and the tribesmen on the front lines? 

\KEVAN: They do seem rather ferocious. 

\TYRION: Ferocious? Last night a Moon brother stabbed a Stone Crow over a sausage. Three Stone Crows seized the Moon brother and opened his throat. Bronn managed to keep Shagga from chopping off the dead man's cock, which was fortunate, but even still Ulf is demanding blood money, which Shagga and Gunthor refuse to pay. 

\TYWIN: When soldiers lack discipline, the fault lies with their commander. 

\TYRION: Surely there are ways to have me killed that would be less detrimental to the war effort. 

\TYWIN: There'll be no more discussion on the matter. 

\TYRION: It appears I'm not hungry after all. Excuse me, My Lords. 

\scene

\textit{LANNISTER CAMP: TYRION'S TENT} 

\ti{\TYRION ~enters to \BRONN ~and \SHAE.}

\TYRION: Where did you find one so pretty at this hour? 

\BRONN: I took her. 

\TYRION: Took her? From whom? 

\BRONN: From Ser What-his-name? I don't know. Ginger cunt three tents down. 

\TYRION: And he didn't have anything to say about it? 

\BRONN: He said something. 

\TYRION: Well, the odds of me living long enough for him to retaliate just dropped drastically. We'll be at the vanguard tomorrow. 

\BRONN: Oh well. I think I'll go and find myself one. 

\TYRION: Who are you? 

\SHAE: Who would you like me to be? 

\TYRION: What did your mother call you? 

\SHAE: Shae. What did your mother call you? 

\TYRION: My mother died giving birth to me. 

\SHAE: Is that why I'm here? So we can talk about our mothers? 

\TYRION: What sort of accent is that? 

\SHAE: Foreign. 

\TYRION: For--

\SHAE: What do you want from me? 

\TYRION: What do I want from you? I want you to share my tent. I want you to pour my wine, laugh at my jokes, rub my legs when they're sore after a day's ride. I want you to take no other man to bed for as long as we're together. And I want you to fuck me like it's my last night in this world which it may well be. 

\SHAE: And what do I get? 

\TYRION: Safety. No one will hurt you for as long as you're mine. The pleasure of my company, which I have heard is spectacular. 

\SHAE: Who told you this? Women you paid? 

\TYRION: And three: more gold than you can spend if you lived a thousand years. Do you accept my proposal? 

\SHAE: Let's start with your last night in this world. 


\scene

\textit{DOTHRAKI SEA} 

\ti{The Khalasar is riding. \DROGO ~is barely conscious. \DAENERYS, \QOTHO, and \HAGGO ~ride behind him.}

\DAENERYS: Khal anni. Shekh ma shieraki anni. Drogo. [My lord. My sun and stars. Drogo.] 

\ti{He falls, and his horse rides away.}

\DROGO: Sajo anni. Sajo anni. [My steed. My steed] 

\HAGGO: Qoy qoyi. [Blood of my blood.] 

\DROGO: Vos, anha'th dothrak. [No, I must ride.] 

\QOTHO: Me arthas hrazefoon mae. Khal fini laz vos dothrao, vos khal.  [He fell from his horse. A khal who cannor ride is no khal.] 

\DAENERYS: Me haqa, vos ale. Me zigeree mithrat. Kisha ray hezhahish chek asshekh. Kisha avimithreraki jinne. [He's tired, that's all. He needs to rest. We have ridden far enough. We will camp here.] 

\QOTHO: Jinne vos gache vimithrerat. Chiori vos assoo kisha. Vos Khaleesi akka. [This is no place to camp. A woman does not give us orders. Not even a Khaleesi.] 

\DAENERYS: Kisha avimithreraki jinne. Asti morea me Khal Drogo asso moon. Zhey Qotho. [We will camp here. Tell them Khal Drogo commanded it. Qotho.] 

\QOTHO: Shafka vos assoo anna zhey Khaleesi. [You do not command me, Khaleesi.] 

\DAENERYS: Ezi Mirri Maaz Duur. Fichi mae anhaan. [Find Mirri Maaz Duur. Bring her to me.] 

\QOTHO: Maegi? Anha afichak shafkea nharees zhey Khaleesi. [The witch? I will bring you her head, Khaleesi.] 

\DAENERYS: Fichi mae anhaan ozisa che Khal Drogo achara kifindirgi yer ziganeso anhaan. [Bring her to me unharmed or Khal Drogo will hear you defied me.] 

\ti{A little later, \DAENERYS ~tends \DROGO ~in his tent (in a corner of the stage).  \IRRI ~sits nearby.}

\DROGO: Doth $\ldots$ Dothrae $\ldots$ Ki ha $\ldots$ hammi $\ldots$ Ish nokitta $\ldots$ Qana'th $\ldots$ [Rides $\ldots$ By a yak $\ldots$ might trample $\ldots$ the black stork must $\ldots$] 

\JORAH: Khaleesi.  

\DAENERYS: Come. \sd{Enter \JORAH.} He's very strong. No one understands how strong he is. 

\JORAH: He will die tonight, Khaleesi. 

\DAENERYS: He can't. He can't. I won't let him. 

\JORAH: Even a Queen doesn't have that power. We must go quickly. I've heard there's a good port in Asshai $\ldots$  

\DAENERYS: I won't leave him. 

\JORAH: He's already gone, Khaleesi. 

\DAENERYS: Even if he dies, why would I run? I am Khaleesi and my son will be Khal after Drogo. 

\JORAH: This isn't Westeros, where men honour blood. Here they only honour strength. There will be fighting after Drogo dies. Whoever wins that fight will be the new Khal. He won't want any rivals. Your boy will be plucked from your breast and given to the dogs. 

\DAENERYS: I won't leave him. 

\sd{Enter \MIRRI, followed by \QOTHO.}

\MIRRI: The wound has festered. 

\QOTHO: Yer et jin zhey maegi. [You did this, witch.] 

\DAENERYS: Nakhi! Anha vos zalok meme nem azzisa. [Stop it. I don't want her hurt.] 

\QOTHO: Vos? Vos? Hash shafka vos zali meme nem azzisa? [No? No? You don't want her hurt?] Zali mekisha vos azzisaki shafka akka. Shafka azh jin maegaan frakhat khales kishi. [Pray we don't hurt you too. You let this witch put her hands on out Khal.] 

\JORAH: Javrathi lekh. Me zin Khaleesi shafki. [Rein in your tongue. She is still your Khaleesi.] 

\QOTHO: Kash qoy qoyi thira disse. Affin me drivoe, me vosi. [Only while blood of my blood lives. When he dies, she is nothing.] 

\DAENERYS: Anha vosoon avvos. Anha qoy zhavvorsi. [I have never been nothing. I am the blood of the dragon.] 

\QOTHO: Ei zhavvorsa drivi, zhey Khaleesi. [The dragons are all dead, Khaleesi.] 

\ti{Exit \QOTHO.}

\DAENERYS: I think you should wear your armor tonight, Ser. 

\JORAH: I think you're right. 

\ti{Exit \JORAH.}

\MIRRI: You've saved me once more. 

\DAENERYS: And now you must save him. 

\MIRRI: He's beyond the healer's skills. All I can do is ease his path. 

\DAENERYS: Save him and I will free you. I swear it. You must know a way. Some magic. 

\MIRRI: There is a spell. Some would say death is cleaner. 

\DAENERYS: Do it. Save him. 

\MIRRI: There is a price. 

\DAENERYS: You'll have gold, whatever you want. 

\MIRRI: It's not a matter of gold. This is Bloodmagic. Only death pays for life. 

\DAENERYS: My death? 

\MIRRI: No. Not your death, Khaleesi. Bring me his horse. 

\ti{\DAENERYS ~nods to \IRRI, who leaves and returns shortly with \RAKHARO ~leading the Khal's horse.}

\RAKHARO: Khaleesi, do not do this thing. Let me kill this witch. 

\DAENERYS: Kill her and you kill your Khal. 

\RAKHARO: This is Bloodmagic. It is forbidden. 

\DAENERYS: I am your Khaleesi. I tell you what is forbidden. 

\MIRRI: Go now! 

\DAENERYS: \sd{To \RAKHARO.} Take her and leave. Take her! 

\ti{\RAKHARO ~leaves with \IRRI.}

\MIRRI: You must go also, lady. Once I begin to sing, no one must enter the tent. The dead will dance here tonight. 

\DAENERYS: No one will enter. \sd{\MIRRI ~slits the horse's throat, and blood covers \DROGO ~and \DAENERYS} Bring him back to me. 

\ti{\DAENERYS ~leaves the tent, to where \JORAH, \QOTHO, and \RAKHARO ~are gathered.  Sounds of \MIRRI ~chanting, and then otherworldly noises emerge from the tent throughout this scene.}

\JORAH: What have you done? 

\DAENERYS: I have to save him. 

\JORAH: We could have been ten miles away from here by now on the way to Asshai. You would have been safe. 

\QOTHO:  Jini'th vos eo. Jini'th vos eo. [This must not be. This must not be.]

\DAENERYS: Jini vee. This must be. 

\QOTHO: Maegi. Witch. 

\RAKHARO: \sd{Putting his hands on \QOTHO's shoulder.} Mra qothoon vosaan. [Nothing good will come of this.] 

\ti{\QOTHO ~shoves \RAKHARO ~away and starts moving towards the tent.}

\DAENERYS: \sd{She tries to stop him, but he pushes her aside.} Vos! Yer laz vos. [No. You can't.]

\JORAH: Vos alle, zhey vezhak. [No further, horselord.] 

\ti{\JORAH ~and \QOTHO ~fight in single combat. \JORAH ~kills him, and then notices that \DAENERYS ~is still on the ground.}

\JORAH: Khaleesi! Are you hurt? 

\DAENERYS: The baby is coming. 

\JORAH: Fetch the midwives. 

\RAKHARO: They will not come. They say she is cursed. 

\JORAH: They'll come or I'll have their heads. 

\RAKHARO: The witch. She can bring baby. I hear her say so. 


\scene

\textit{LANNISTER CAMP: TYRION'S TENT} 

\ti{\SHAE, \TYRION ~and \BRONN ~are sitting together.  \SHAE ~and \TYRION ~are holding a lit candle beween them, which is burning their arms.}

\SHAE: Are you in agony, my lion? 

\TYRION: No. 

\SHAE: You look like you're in agony. The fire is burning your pretty soft skin. 

\TYRION: \ti{(Moving his arm and dropping the candle.)} Ahhh. Damn you, woman. Are you immune to pain? 

\SHAE: Just used to it. 

\BRONN: Drink. 

\TYRION: Let's play a new game. 

\BRONN: There's a Braavosi knife game I could teach you.

\TYRION: Does it involve the potential for losing fingers? 

\BRONN: Not if you win. 

\TYRION: No! No more fire games, no knife games. Let's do something I'm good at. 

\SHAE: What are you good at? 

\TYRION: I happen to be a great judge of character. 

\BRONN: This sounds like a boring game. 

\TYRION: It's not. Here's how it works: I make a statement about your past. If I'm right, you drink. If I'm wrong, I drink. And no lying. I'll know if you're lying. 

\SHAE: I don't want to play this game. 

\TYRION: Fine. Bronn first. Your father beat you. 

\BRONN: \ti{(Drinking.)} But my mother hit harder. 

\TYRION: You killed your first man before you were 12. 

\BRONN: It was a woman. She swung an axe at me. 

\ti{\TYRION ~drinks.}

\TYRION: You've been north of the Wall. 

\ti{\BRONN ~drinks.}

\SHAE: What brought you up there? 

\BRONN: Work. 

\TYRION: And $\ldots$ You once loved a woman many years ago, but it turned out badly so you've never let yourself love again. Oh wait, that's me. Your turn, my mysterious foreign beauty. 

\SHAE: I don't want to play. 

\TYRION: It's fun! Look at the fun we're having. Your mother was a whore. 

\SHAE: Drink. 

\TYRION: All right. Your father left the family when you were very young, never to return. 

\SHAE: Drink. 

\TYRION: And we've established the rules about lying? 

\SHAE: Drink! 

\TYRION: Mmmm. You wanted a different life. You came from somewhere and you wanted to be elsewhere. 

\BRONN: The whole shit-stained world could drink off that one. 

\TYRION: So, specifics. You wanted to be elsewhere, but how would you get there? I don't believe the life of the silent sisters is for you. So what's a lowborn girl to do? 

\SHAE: Drink. 

\TYRION: Are you sure $\ldots$ 

\SHAE: Drink! And don't talk about my mother and father ever or I will carve your eyes from your head. 

\TYRION: My dear lady, if I have offended you, I apologize. 

\SHAE: My turn. 

\TYRION: Fine fine. Ask away. Try to penetrate the enigma that is me. 

\SHAE: Who were you in love with? 

\TYRION: That's not how the game works. 

\SHAE: I don't care the way the game works. 

\BRONN: Our Lord here used to be married. 

\SHAE: Married? 

\TYRION: How did you hear that? 

\BRONN: You hear lots of things playing dice with Lannister soldiers. 

\TYRION: Another night, perhaps. 

\SHAE: Not another night. This night. 

\TYRION: It's not a pleasant story. 

\SHAE: Well maybe I will cry. 

\BRONN: I'm guessing the lady and I can tell more unpleasant stories than your Lordship. 

\TYRION: So $\ldots$ I was sixteen. My brother Jaime and I were riding when we heard a scream. She ran out onto the road, clothes half torn off with two men on her heels. Jaime scared away the men easily enough, while I wrapped her in my cloak. She was too scared to send off on her own, so while Jaime hunted down the rapers I took her to the nearest inn and fed her. Her name was Tysha. She was a wheelwright's orphan. And she was hungry $\ldots$ together we finished off three chickens and a flagon of wine. Impossible as it seems, there was a time when I was unaccustomed to wine. I forgot how afraid I was around girls, how I was always waiting for them to laugh at me or look away embarrassed or ask me about my tall handsome brother. I forgot about everything but Tysha. And somehow I found myself in her bed. 

\BRONN: For three chickens, I should hope so. 

\TYRION: It didn't last long. I didn't know what the hell I was doing. But she was good to me. She kissed me afterwards and sang me a song. And by morning I was deep enough in love to ask for her hand. A few lies, a few gold coins, one drunken Septon and there you have it $\ldots$ man and wife. For a fortnight anyway, until the Septon sobered up and told my father. 

\BRONN: I imagine that was the end of all that. 

\TYRION: Not quite. First, my father had Jaime tell me the truth. The girl was a whore, you see. Jaime had arranged the whole thing, the road, the rapers $\ldots$ all of it. He thought it was time I had a woman. After my brother confessed, my father brought in my wife and gave her to his guards. He paid her well $\ldots$  a silver for each man. How many whores command that kind of price? He brought me into the barracks and made me watch. By the end, she had so much silver that the coins were slipping through her fingers and rolling onto the floor. 

\BRONN: I would have killed the man who did that to me. 

\SHAE: You should have known she was a whore. 

\TYRION: Really? I was sixteen, drunk and in love $\ldots$  

\SHAE: A girl who was almost raped doesn't invite another man into her bed two hours later. 

\TYRION: As I said, I was young and stupid. 

\SHAE: You are still young and stupid. 


\scene

\textit{THE NEXT MORNING} 

\ti{\TYRION ~and \SHAE ~are sleeping, entwined. \BRONN ~wakes them.}

\TYRION: What is it? What do you want? 

\BRONN: You're sleeping through the war. 

\TYRION: What? 

\BRONN: They stole a night's march on us. They're a mile north. 

\TYRION: Get my squire! 

\BRONN: You don't have a squire. 

\TYRION: If I die, weep for me. 

\SHAE: You'll be dead. How will you know? 

\TYRION: I'll know. 

\ti{\TYRION ~and \BRONN ~leave the tent, and head towards his tribesmen.}

\BRONN: Stay low. 

\TYRION: Stay low? 

\BRONN: If you're lucky, no-one will notice you. 

\TYRION: I was born lucky. Tribesmen of the Vale, gather round! Stone Crows! Black Ears! Burned Men! Moon brothers! 

\HILLTRIBESMAN: And painted dogs! 

\TYRION: And painted dogs! Your dominion over the Vale begins now! Onward to claim what is yours! 

\CROWD: Half man! Half man! Half man! Half man! Half man! Half man! To battle. 

\ti{They charge.}

\n The battle rages, and TYRION is knocked out early on.  He awakens to the delightful sight of Bronn looking down at him.

\BRONN: You're a shit warrior. 

\TYRION: I'm alive? 

\BRONN: You're alive. 

\TYRION: Did we win? 

\BRONN: We wouldn't be having this conversation if we didn't. 

\TYRION: How did our tribesmen do? 

\BRONN: Yeah, good. 

\ti{They look across the battlefield, where the tribesmen are looting and butchering corpses with enthusiasm}

\TYRION: It's nice to see them getting along. 

\ti{\TYWIN ~rides up}

\TYWIN: You're wounded. 

\TYRION: Good of you to notice. I hear we won. 

\TYWIN: Hmph. The scouts were wrong. There were two thousand Stark bannermen, not twenty thousand. 

\TYRION: Did we get the Stark boy, at least? 

\TYWIN: He wasn't here. 

\TYRION: Where was he? 

\TYWIN: With his other eighteen thousand men. 

\TYRION: And where are they? 


\scene

\textit{ROBB'S CAMP} 

\ti{\RODRIK ~and \CATELYN ~are watching for \ROBB's return.}

\RODRIK: We should go, My Lady. 

\CATELYN: No! 

\RODRIK: My Lady! 

\ti{Enter \ROBB, victorious at the head of his army.  With \THEON, \UMBER, and \JAIME ~in chains.}

\ROBB: By the time they knew what was happening, it had already happened. 

\JAIME: Lady Stark. I'd offer you my sword, but I seem to have lost it. 

\CATELYN: It's not your sword I want. Give me my daughters back. Give me my husband. 

\JAIME: I've lost them too, I'm afraid. 

\THEON: Kill him, Robb. Send his head to his father. He cut down ten of our men $\ldots$ you saw him. 

\ROBB: He's more use to us alive than dead. 

\CATELYN: Take him away and put him in irons. 

\JAIME: We could end this war right now, boy, save thousands of lives. You fight for the Starks, I fight for the Lannisters. Swords or lances, teeth, nails $\ldots$ choose your weapons and let's end this here and now. 

\ROBB: If we do it your way, Kingslayer, you'd win. We're not doing it your way. 

\UMBER: Come on, pretty man. 

\ti{Exit \UMBER ~and \JAIME.}

\ROBB: I sent two thousand men to their graves today. 

\THEON: The bards will sing songs of their sacrifice. 

\ROBB: Aye. But the dead won't hear them. \sd{To all his men.} One victory does not make us conquerors. Did we free my father? Did we rescue my sisters from the Queen? Did we free the North from those who want us on our knees? This war is far from over. 


\scene

\textit{KING'S LANDING}

\ti{\ARYA ~catches a pigeon, but really would like something more wholesome to eat, like one of those pies?} 

\ARYA: Could I have one? A lemon one $\ldots$ or any of them. 

\PIESELLER: Three coppers. 

\ARYA: How about a nice fat pigeon? 

\PIESELLER: Piss off now. Go on. 

\ARYA: Do you have any stale ones from yesterday? Or any burnt ones? 

\PIESELLER: Piss off! 

\ARYA: Hey, where's everyone going? What's happening? 

\URCHIN: They're taking him to the Sept of Baelor. 

\ARYA: Who? 

\URCHIN: The Hand of the King. 

\ti{She runs to the Sept. \NED ~is brought out in chains, with \JOFFREY, \CERSEI, \PYCELLE, \SANSA, \textbf{ILYN PAYNE} and a \textbf{GUARD} looking on.}

\CROWD: Traitor! Coward! Baelor. Baelor! Traitor! Traitor! 

\NED: I am Eddard Stark, Lord of Winterfell and Hand of the King. I come before you to confess my treason in the sight of Gods and men. I betrayed the faith of my King and the trust of my friend Robert. I swore to protect and defend his children, but before his blood was cold I plotted to murder his son $\ldots$ and seize the Throne for myself. 

\CROWD: Traitor! 

\NED: Let the high Septon and Baelor the blessed bear witness to what I say: Joffrey Baratheon is the one true heir to the Iron Throne, by the Grace of all the gods, Lord of the Seven Kingdoms and Protector of the Realm. 

\PYCELLE: As we sin, so do we suffer. This man has confessed his crimes in sight of Gods and men. The Gods are just but beloved Baelor taught us they can also be merciful.  What is to be done with this traitor, Your Grace? 

\JOFFREY: My mother wishes me to let Lord Eddard join The Night's Watch. Stripped of all titles and powers, he would serve the realm in permanent exile. And My Lady Sansa has begged mercy for her father. But they have the soft hearts of women. So long as I am your King, treason shall never go unpunished. Ser Ilyn, bring me his head! 

\ti{\textbf{ILYN PAYNE} pushes \NED ~to the block, and the \textbf{GUARD} grabs \SANSA ~as she tries to reach her father.}

\SANSA: No! Stop! Please! Someone stop him! 

\CERSEI: My son, this is madness. 

\ti{\YOREN ~finds \ARYA ~and grabs hold of her.}

\YOREN: Don't look! 

\ARYA: Let me go. Let me go! 

\YOREN: Shut your mouth. Look at me. Look at me! 

\SANSA: Stop! No no! 

\ti{The axe falls.}

\end{document}
