\input{preamble}
\input{ep12_cast}
\title{Episode 12 (S2E2): The Night Lands}
\author{}
\date{}
\maketitle

\input{ep12_casttable}

\scene

\textit{YOREN'S CAMP}

\ti{\YOREN ~and \GENDRY ~are gathering wood. Elsewhere
on-stage, \JAQEN, \RORGE, and \BITER are caged up. At stage
edge, \ARYA ~finishes relieving herself, and walks back towards the
camp, past the cage.}

\JAQEN: Boy. Lovely boy.

\ARYA: What do you want?

\JAQEN: A man has a thirst. A man does not drink for a day and a night. A boy could make a friend.

\ARYA: I have friends.

\RORGE: Give us beer before I skin you.

\JAQEN: A man does not choose his companions. These two, they have no courtesy. A man must ask forgiveness.  You're called Arry? This man has the honour to be Jaqen H'ghar, once of the free city of--

\RORGE: Beer, you little shit. Get us beer!

\ARYA: You should have asked nicely.

\ti{\ARYA ~begins hitting the cage with a stick, trying to hit \RORGE, who tries to claw back. \JAQEN ~laughs at the exchange. \BITER ~looks on.}

\RORGE: Come closer and I'll shove that stick up your bunghole and fuck you bloody.

\JAQEN: A boy has more courage than sense.

\RORGE: Come here!

\ti{\RORGE ~reaches out at \ARYA. \GENDRY ~walks past and \ARYA ~joins him.}

\GENDRY: Yoren said none of us were to go near those three.

\RORGE: Come here!

\ARYA: They don't scare me.

\GENDRY: Hmm? Then you're stupid. They scare me.

\ti{\GOLDCLOAK ~rides in on horseback.}

\ARYA: What are Gold Cloaks doing so far from King's Landing?

\ti{\ARYA ~attempts to hide.}

\GENDRY: What are you doing?

\ARYA: They're looking for me.

\GOLDCLOAK: You in command here?

\YOREN: You're a long way from home.

\GOLDCLOAK: I asked you a question.

\YOREN: Aye, you did. You asked without manners and I chose not to answer.

\GOLDCLOAK: I have a royal warrant for one of these gutter rats you're transporting.

\YOREN: Well, the thing is$\ldots$ these gutter rats belong to the Night's Watch. Now, that puts them beyond the reach of kings and queens.

\GOLDCLOAK: Does it?

\ti{\GOLDCLOAK ~tries to pull out his sword. \YOREN ~quickly pulls out his dagger and puts it to the man's thigh.}

\YOREN: It's a funny thing. People worry so much about their throats that they forget about what's down low. Now I sharpened this blade before breakfast. I could shave a spider's arse if I wanted to or I could nick this artery in your leg. And once it's nicked, there's no one around here who knows how to unnick it.

\ti{\YOREN ~takes \GOLDCLOAK's sword.}

\YOREN: We'll just keep that. Good steel is always needed on the Wall. Seems you have a choice$\ldots$ you can die here at this crossroads a long way from home, or you can go back to your city and tell your Masters you didn't find what you were looking for.

\GOLDCLOAK: We're looking for a boy named Gendry. He carries a bull's head helmet. Anyone turning him over will earn the King's reward. I'll be back with more men and I'll be taking your head home along with that bastard boy.


\scene

\textit{KING'S LANDING: THE RED KEEP}

\ti{\TYRION ~walks through a room and into a hallway, whistling. As he opens the door to his room, \SHAE ~laughs, and he stops whistling. \SHAE ~and \VARYS ~are sitting at a table. \VARYS ~stands up, and \TYRION ~looks at \SHAE, and closes the door.}

\VARYS: My Lord.

\SHAE: You make me wait a long time, but your friend keeps me company.

\VARYS: We were just speaking of your bravery in the victory against the Stark auxiliary forces.

\TYRION: It was quite a battle.

\VARYS: I heard you suffered a terrible head wound. The northerners are such fearsome warriors.

\SHAE: And I tell him the story of how we meet.

\VARYS: To find so lovely a creature working in your father's kitchens$\ldots$ it almost beggars belief.

\TYRION: Strange things do happen. You should taste her fish pie.

\SHAE: I don't think Lord Varys likes fish pie.

\TYRION: How can you tell?

\SHAE: I can always tell.

\TYRION: Men like Lord Varys and me can't let our disadvantages get the best of us. We'll make a fisherman of him yet.

\VARYS: I am glad your new friend was able to accompany you to the capital. Friends are such an important part of life. Unfortunate that your father didn't want her to come. But rest easy, My Lord. I am very good at keeping secrets for my good friends.

\TYRION: Your discretion is legendary$\ldots$ where your friends are concerned.

\VARYS: How unspeakable of me to go on and on when all you want to do is rest. I will leave you. Welcome to King's Landing, my dear. This city is made brighter by your presence. We have a council meeting, My Lord.

\ti{\SHAE ~stands up, and walks away. \TYRION ~puts his hand on the door, blocking it from being opened.}

\TYRION: I don't like threats.

\VARYS: Who threatened you?

\TYRION: I'm not Ned Stark. I understand the way this game is played.

\VARYS: Ned Stark was a man of honour.

\TYRION: And I am not. Threaten me again and I'll have you thrown into the sea.

\VARYS: You might be disappointed in the results. Storms come and go, the big fish eat the little fish, and I keep on paddling. Come, My Lord. We shouldn't keep the Queen waiting.

\ti{They exit.}


\scene

\textit{SMALL COUNCIL CHAMBER}

\ti{The small council (\TYRION, \PYCELLE, \VARYS, \LITTLEFINGER) sits at their table. \ALTON ~stands nearby. \CERSEI ~is reading a letter aloud.}

\CERSEI: `From this time until the end of time, we are not part of
your realm, but a free and independent kingdom of the North.' He has
more spirit than his father, I'll give him that. \sd{tears the letter up}

\TYRION: You've perfected the art of tearing up papers. We can give him his father's bones back at least as a gesture of good faith.

\CERSEI: You'll give the Starks our reply, cousin?

\ALTON: I will, Your Grace.

\CERSEI: Did you see my brother when you were the Starks' guest?

\ALTON: I did. They have not broken his spirit, Your Grace.

\CERSEI: If you speak with him, tell him he's not been forgotten.

\ALTON: I will, Your Grace.

\TYRION: Safe travels, cousin.

\ti{Exit \ALTON.}

\TYRION: You have a deft hand with diplomacy.

\CERSEI: If that's everything$\ldots$

\PYCELLE: A$\ldots$ a raven flew in this morning from Castle Black.

\ti{\PYCELLE ~hands the letter to \TYRION, who unfurls it and begins reading.}

\VARYS: Trouble with the wildlings?

\LITTLEFINGER: That's why they're called wildlings.

\VARYS: Somewhat less wild these days. Seems they've stopped killing each other and started following this King-Beyond-the-Wall.

\CERSEI: Another king? How many is that now, five? I've lost count.

\TYRION: The Lord Commander asks that we send more men to man the Wall.

\CERSEI: Perhaps he's forgotten we're fighting a war. We have no men to spare.

\TYRION: The cold winds are rising and the dead rise with them.

\PYCELLE: The northerners are a superstitious people.

\ti{Everyone but \TYRION ~stands up to leave.}

\TYRION: According to the Commander, one of these dead men attacked him in his chambers. Mormont doesn't lie.

\ti{The others stop leaving.}

\VARYS: How do you kill a dead man?

\TYRION: Apparently you burn him.

\CERSEI: One trip to the Wall and you come back believing in grumpkins and snarks.

\TYRION: I don't know what I believe, but here's a fact for you. The Night's Watch is the only thing that separates us from what lies beyond the Wall.

\CERSEI: I have every confidence that the brave men of the Night's Watch will protect us all.

\ti{They exit. \TYRION ~leaves last.}


\scene

\textit{CRASTER'S CAMP}

\ti{\EDD, \GRENN\, \SAM ~are chopping vegetables.}

\EDD: And I said, `if the Gods wanted us to have dignity, they wouldn't make us fart when we died.'

\GRENN: We fart when we die?

\EDD: My blessed mother$\ldots$ I was holding her hand when she left this world. She farted so hard, the whole bed shook.

\ti{\EDD ~makes farting noises with his mouth as they continue to cut food. \SAM ~looks up and watches \GILLY ~walk past.}

\SAM: Seems a bit greedy for one man to have so many wives. Wouldn't two or three be enough for him?

\EDD: We were having a serious discussion.

\ti{\GRENN ~looks up to watch some of the women.}

\GRENN: Would you look at that?

\SAM: Nothing like the sight of a woman walking away.

\GRENN: I prefer watching them come towards me.

\SAM: I'm sure that's nice, too.

\GRENN: Yeah, well, there was a milkmaid named Violet on the next farm over from where I grew up. We were wrestling together from the time we were six years old. And then we got older and the wrestling, uh$\ldots$ changed.

\SAM: You were with her? How many times?

\GRENN: Well, as many times as I could.

\SAM: I wish I grew up on a farm.

\EDD: We need more potatoes. Get another sack from the sledge. Get the turnips, too.

\ti{They exit.}

\ti{A dog barks. \GILLY ~runs on stage screaming, followed by \SAM, addressing Ghost (offstage), then \GILLY.}

\SAM: No. Ghost, no. No! Ghost, away. Shoo, shoo! You all right? Did he frighten you?

\GILLY: You$\ldots$ you shouldn't touch me.

\SAM: Oh. Oh, right. I'm sorry. I just wanted to make sure you weren't hurt.

\GILLY: You're very brave.


\scene

\textit{ANOTHER PART OF THE CAMP}

\ti{\JON ~is sharpening his sword. \SAM ~\& \GILLY ~approach.}

\JON: What are you doing?

\SAM: This is Gilly. She's one of Craster's$\ldots$ daughters.

\JON: Hello, Gilly. What are you doing?

\GILLY: Sam said you could help.

\JON: I'm sorry, but Sam knows we're not supposed---

\SAM: She's pregnant. Have to take her with us when we leave.

\JON: What? What would that$\ldots$

\SAM: I know it sounds a bit mad.

\JON: No, it doesn't sound a bit mad, it's impossible.

\SAM: The Lord Commander ordered us to$\ldots$ I mean, we are sworn to protect---

\JON: Sam, we can't take---

\GILLY: Please, sir, please. I can still run if I have to.

\JON: It's just not possible.

\GILLY: I'm going to have a baby. If it's a boy---

\JON: If it's a boy, what? You want us to risk our lives for you and you won't even tell us why?

\ti{\GILLY ~looks taken aback, and then runs off.}

\SAM: Why'd you do that?

\JON: Do what? Ask her a question?

\SAM: You were cruel.

\JON: Cruel? Sam, are you in such a hurry to lose a hand?

\SAM: I didn't touch her.

\JON: No, you just want to steal her. What do you think Craster cuts off for that?

\SAM: I can't steal her. She's a person, not a goat.

\JON: We're heading deeper and deeper into wildling territory. We can't take a girl with us. Mormont wouldn't have it. And even if he would, what would we do with her? Who's going to deliver a baby, you?

\SAM: I could try. What? I've read about it. A bit.

\JON: I'm sorry, Sam. We can't help her.

\ti{\JON ~sits back down, and returns to sharpening his sword. \SAM ~walks away. When \SAM ~is gone, \JON ~sighs deeply.}


\scene

\textit{DOTHRAKI SEA}

\ti{\JORAH ~and \DAENERYS ~sit near each other, tired and weak. After
a moment, \JORAH ~sips his water and sighs. He looks up.}

\n Jorah hears, and then sees a horse approaching. It has no rider.

\JORAH: Khaleesi.

\ti{\DAENERYS ~looks up at the horse. \JORAH ~goes over to it, and
examines the saddle-bag as the narrator describes it.}

\n The horse has been painted red, and flies buzz round a bag attached
to the saddle. It has a severed head in it.

\JORAH: You don't need to see this.

\DAENERYS: He is blood of my blood.

\ti{\DAENERYS ~looks in the sack, and then quickly looks away.}

\DAENERYS: Who did this?

\JORAH: Khal Pono, perhaps. Khal Jhaqo. They don't like the idea of a woman leading a Khalasar.

\DAENERYS: They will like it far less when I am done with them.

\ti{\IRRI ~walks over and sees the head. She then falls to her knees, crying.}

\IRRI: Mori atthasish oakah moon! [No! They killed his soul.]

\DAENERYS: Affa, affa. Mori laz vos atthi oakah vosecchi. [Shh ... They cannot kill his soul.]

\IRRI: Jin tish mori! Mori ogish ven mae ven rho. Mori avvirsosh khadoes moon. Me laz odothrae kimi mae she Rhaeshi Ajjalani avvos. [They did! They butchered him like an animal. They did not burn his body. He can never join his ancestors in the night lands.]

\DAENERYS: Affa. Kisha amariki vorsqoy ha maan. Majin anha astak yeraan asqoy, me-Rakharo adothrae kimi mae ajjalan. [Shh. We will build him a funeral pyre. And I promise you, Rakharo will ride with his ancestors tonight.]

\ti{\DAENERYS ~continues to comfort \IRRI ~as she cries. \IRRI ~wails loudly.}

\scene

\newpage

\textit{THE IRON ISLANDS}

\ti{On a boat. A naked \WOMAN ~lies in bed, near where \THEON ~looks
out at the approching Iron Islands. He slowly takes his clothes off
throughout this conversation.}

\WOMAN: Is it as you remember, My Lord?

\THEON: It looks smaller.

\WOMAN: Everything looks bigger when you're a child. I remember my father's cabin felt like a palace when I was little. Now look at it.

\THEON: They'll be waiting for me on the docks.

\WOMAN: Who will?

\THEON: Anyone who matters. This is a big day for them. They haven't had much to get excited about since I left. It's a hard place, the Iron Islands. Always has been. It's cold and it's wet.

\WOMAN: Oh, I love the cold and wet.

\THEON: They say hard places breed hard men. And hard men rule the world.

\WOMAN: \ti{(Staring at his cock.)} Then you'll be king before long.

\THEON: Try smiling with your lips closed. Better.

\ti{\THEON ~stands up and roughly pushes her back onto the bed.}

\WOMAN: My father doesn't trust you Iron islanders.

\THEON: I don't blame him.

\WOMAN: He says that you're all reavers and rapers and that no matter how many women you have, you'll never be sat--- uh!

\ti{They start fucking.}

\THEON: Quit talking about your father. But he's right about us. Our wives from the Iron Islands, they're for breeding. That's not enough for us. That's why we take salt wives$\ldots$ the women we capture.

\WOMAN: Capture me. Take me with you when you go ashore. Make me your salt wife.

\THEON: Your place is on this ship.

\WOMAN: Not after you leave. Father will punish me. He'll call me a whore.

\THEON: I haven't paid you.

\ti{They continue fucking.}


\scene

\textit{LITTLEFINGER'S BROTHEL}

\ti{\LITTLEFINGER ~is spying on his customers. He hears a noise and turns around, then covers the hole he was watching through. A \CLIENT ~emerges from another room. \ROS ~can be heard crying from inside throughout this scene.}

\CLIENT: I paid good money! I'm not going to stand for this. I barely touched her. Now, you charge twice as much as every other brothel and this is what I get$\ldots$ crying.

\LITTLEFINGER: One moment, my friend. A moment.

\ti{Baelish snaps his fingers, and \RAMKA ~emerges from another room, covered only in gold jewelry. Out of sight, Baelish wipes some semen from her face with a cloth, and then turns back to the disgruntled man.}

\LITTLEFINGER: Please accept my sincerest apologies. Ramka will take good care of you.

\ti{Upon seeing \RAMKA, the man smiles. As they begin to kiss passionately, \LITTLEFINGER ~goes over to see \ROS, curled up on the bed, crying. He walks over to her, putting a hand on her back, and then sits next to her.}

\ROS: I'm sorry, My Lord.

\LITTLEFINGER: Shh, shh. Did he hurt you?

\ROS: No, My Lord. It's Mhaegen.

\LITTLEFINGER: Who?

\ROS: She works for you. She's the one$\ldots$ the Goldcloaks, they killed her baby.

\LITTLEFINGER: Ah, yes. That was$\ldots$ poorly handled. Sometimes those with the most power have the least grace.

\ROS: I can't stop thinking about it. I can't sleep. That poor little baby.

\LITTLEFINGER: You know, you remind me of another girl, a lovely thing I once acquired from a Lysene pleasure house$\ldots$ beautiful, like yourself, and intelligent, like yourself. But she wasn't happy. She cried often. I asked her why, but we didn't have the kind of rapport that you and I have. Yes, it was quite sad. Girls from the Lysene pleasure houses are expensive, extremely expensive. And this one wasn't making me any money. I hate bad investments. Really, I$\ldots$ I do. They haunt me. I had no idea how to make her happy, no idea how to mitigate my losses. A very wealthy patron, he offered me a tremendous amount of money to let him transform this lovely, sad girl. To use her in ways that$\ldots$ would never occur to most men. And you know what occurs to most men. I would not say he succeeded in making her happy, but my losses were definitely mitigated. Take tonight off to mourn Mhaegen's child. I'll see you tomorrow. And you'll be happy?

\ti{\ROS ~nods.}

\LITTLEFINGER: That makes me happy.


\scene

\textit{TYRION'S DINING ROOM}

\ti{\TYRION ~and \JANOSSLYNT ~are seated at the table. \PODRICK ~is waiting on them.}

\PODRICK: More wine?

\ti{\PODRICK ~spills it as he pours.}

\JANOSSLYNT: Damn it, boy!

\PODRICK: Apologies, My Lord.

\TYRION: Leave us, Podrick. I believe we know how to pour our own wine.

\ti{Exit \PODRICK; Enter \BRONN ~unseen.}

\JANOSSLYNT: That's your new squire? I could've found you a proper lad.

\TYRION: Myself, I prefer the improper ones.

\JANOSSLYNT: Mm, that's a good red. Dornish?

\TYRION: You know your wines, My Lord.

\JANOSSLYNT: That I do. A fine dinner, My Lord.

\TYRION: Call me Tyrion, please. I'm sure you're getting used to fine dinners, now that you're a lord.

\JANOSSLYNT: Maybe I'll hire this cook of yours.

\TYRION: Wars have been started for less.

\ti{They both laugh. \JANOSSLYNT ~sips his wine.}

\TYRION: I heard there was some trouble in Littlefinger's brothel the other night.

\JANOSSLYNT: Mm, nasty business. Had to be done.

\TYRION: Yes, of course. The City Watch must keep the peace, only I hadn't realized peace depended on killing babies.

\JANOSSLYNT: Orders are orders.

\TYRION: Quite right. Especially the Queen's orders.

\JANOSSLYNT: I never said they were the Queen's orders.

\TYRION: No, but who else would want to murder King Robert's bastards? She's always been a jealous woman.

\JANOSSLYNT: You know your sister better than I do.

\TYRION: You've heard the awful rumors about my brother and sister?

\JANOSSLYNT: I don't listen to filth.

\TYRION: That's good of you, but you have heard them. I suppose people who do believe that filth consider Robert's bastards to be better claimants to the throne than Cersei's children.

\JANOSSLYNT: Joffrey is my king. The rest doesn't interest me.

\TYRION: I appreciate your loyalty. Tell me, when your men slaughtered Ned Stark's men in the throne room, did you give the order?

\JANOSSLYNT: I did. And I would again. The man was a traitor. He tried to buy my loyalty.

\TYRION: The fool. He had no idea you were already bought.

\JANOSSLYNT: Are you drunk? I'll not have my honour questioned by an Imp!

\TYRION: I'm not questioning Your honour, Lord Janos. I'm denying its existence.

\JANOSSLYNT: If you think I'll stand here and take this from you, dwarf$\ldots$

\TYRION: Dwarf? Mm, you should have stopped at Imp. And, yes, you will stand here and take it from me, unless you'd like to take it from my friend here.

\ti{\TYRION ~gestures towards \BRONN}

\TYRION: I intend to serve as Hand of the King until my father returns from the war. And seeing as you betrayed the last Hand of the King, well, I just wouldn't feel safe with you lurking about.

\JANOSSLYNT: What are you to---My friends at court will not allow this! The Queen herself has granted$\ldots$

\TYRION: The Queen Regent. And you're a fool to believe she is your friend.

\JANOSSLYNT: We shall hear what Joffrey has to say about this.

\TYRION: No. We shan't.

\ti{\TYRION ~nods at \BRONN, who gestures for some \textbf{GOLDCLOAKS} to enter the room.}

\TYRION: There's a ship leaving for Eastwatch-by-the-Sea tonight. From there I'm afraid it's rather a long walk to Castle Black. I hope you enjoy the Wall. I found it surprisingly beautiful$\ldots$ In a brutal, horribly uncomfortable sort of way.

\BRONN: The lads will escort you. The streets aren't safe at night, My Lord.

\JANOSSLYNT: These men are under my command! I command you to arrest this cutthroat.

\TYRION: His name is Bronn and he is the new commander of the City Watch.

\BRONN: Boys.

\ti{The \textbf{GOLDCLOAKS} in the room escort \JANOSSLYNT ~out. \JANOSSLYNT ~begins shouting as they take him.}

\JANOSSLYNT: I have friends at court, powerful friends! The King himself made me a lord!

\ti{\JANOSSLYNT ~is escorted off-stage. \BRONN ~sits down, and \TYRION ~pours him a cup of wine.}

\TYRION: To the new Commander.

\ti{\TYRION ~and \BRONN ~clink their glasses together. Then they both sip.}

\TYRION: If I told you to murder an infant girl, say, still at her mother's breast, would you do it without question?

\BRONN: Without question? No. I'd ask, `How much?'


\scene

\textit{YOREN'S CAMP}

\ti{\LOMMY, \HOTPIE, \ARYA ~are talking while they wash up in the river.}

\LOMMY: If they come back, I say we yield. Gendry's the one they want. Don't want to get caught in the middle of a battle.

\HOTPIE: I ain't afraid of no battles.

\ARYA: If you got within a mile of a battle, you'd fill your pants.

\HOTPIE: I've seen lots of battles. I saw---

\ARYA: Liar.

\HOTPIE: I saw a man kill another man just outside a tavern in Flea Bottom. Stabbed him right in the neck.

\LOMMY: Two men fighting isn't a battle.

\HOTPIE: They had armour on.

\ARYA: So?

\HOTPIE: So, if they've got armour on, it's a battle.

\LOMMY: No, it isn't.

\HOTPIE: What does a dyer's apprentice know about battles anyway?

\ti{\GENDRY ~walks over to them.}

\ARYA: Gendry's an armourer's apprentice. Hot pie, tell Gendry what makes a fight into a battle.

\HOTPIE: It's, um, when they've got armour on.

\GENDRY: Now, who told you that?

\HOTPIE: A knight.

\GENDRY: How'd you know he was a knight?

\HOTPIE: Well, it was `cause he got armour on.

\GENDRY: You don't have to be a knight to have armour. Any idiot can buy armour.

\HOTPIE: How do you know?

\GENDRY: `Cause I sold armour.

\ti{\LOMMY ~nudges \HOTPIE, and they both get up and leave. \ARYA ~stops washing and stands up, walking over to \GENDRY.}

\ARYA: What do the Goldcloaks want with you?

\GENDRY: No idea.

\ARYA: You're a liar.

\GENDRY: You know, you shouldn't insult people that are bigger than you.

\ARYA: Then I wouldn't get to insult anyone.

\GENDRY: I don't care what any of them want. No good's ever come of their questions.

\ARYA: No good's ever come? Who asked questions before?

\GENDRY: How can someone so small be such a huge pain in my ass?

\ARYA: Who asked questions?

\GENDRY: The Hand of the King. Hands of the King. Lord Arryn came first a few weeks before he died, and then Lord Stark came a few weeks before he died.

\ARYA: Lord Stark?

\GENDRY: See? Asking me questions is bad luck. You'll probably be dead soon.

\ARYA: What did they ask about?

\GENDRY: My mum.

\ARYA: Who's your mum?

\GENDRY: Just my mum$\ldots$ Worked in a tavern, died when I was little.

\ARYA: And who was your father?

\GENDRY: Could've been one of those gold-hatted bastards, for all I know. What about you anyway? You thought they were after you. Why? Did you kill someone or is it just because you're a girl?

\ARYA: I'm not a girl.

\GENDRY: Yes, you are. Do you think I'm as stupid as the rest of them?

\ARYA: Stupider. The Night's Watch doesn't take girls, everyone knows that.

\GENDRY: Yeah, that's true, but you're still a girl.

\ARYA: I am not!

\GENDRY: Yeah? Well, pull your cock out and take a piss, then.

\ARYA: I don't need to take a piss. \sd{Pause} Lommy and Hot Pie can't know. No one can know.

\GENDRY: Well, they won't, not from me.

\ARYA: My name's not Arry. It's Arya$\ldots$ of House Stark. Yoren is taking me home to Winterfell.

\GENDRY: He was your father$\ldots$ the Hand, the traitor!?

\ARYA: He was never a traitor. Joffrey is a liar.

\GENDRY: So you're a highborn, then. You're a lady.

\ARYA: No. I mean, yes. My mother was a lady and my sister$\ldots$

\GENDRY: Yeah, but you were a lord's daughter and you lived in a castle and you$\ldots$ look, all that about cocks, I should never have said$\ldots$ and I've been pissing in front of you and everything.  I should be calling you `My Lady'.

\ARYA: Do not call me `My Lady'.

\GENDRY: As My Lady commands.

\ti{\ARYA ~shoves him.}

\GENDRY: Well, that was unladylike.

\ti{\ARYA ~pushes \GENDRY ~to the ground. He laughs, and she stomps off.}


\scene

\newpage

\textit{THE IRON ISLANDS}

\ti{The busy docks. \THEON ~stands in a rowboat as is comes up against the side of a wall. He gets out and walks up some stairs. An \OLDMAN ~spots him.}

\OLDMAN: What's she carrying?

\THEON: Myrish oranges, wine from the Arbor$\ldots$ And the heir to Pyke and the Iron Islands. \sd{\OLDMAN ~does not respond.} The only living son of Balon Greyjoy. \sd{\OLDMAN ~is not impressed.} Me.

\OLDMAN: I don't like wine. Woman's drink.

\THEON: I need to get to Pyke.

\ti{The man looks up, but makes no move or response. \THEON ~looks annoyed and pulls out some coins.}

\OLDMAN: I'll find you a horse.

\ti{The man takes the coins and walks away. \THEON ~watches as the rowboat that took him there leaves. He looks down. Enter \YARA.}

\YARA: I'm heading that way. I can take you there.

\THEON: I bet you can.

\YARA: Have you been at sea long? Or were there just no women where you came from?

\THEON: None like you.

\YARA: You don't know what I'm like.

\THEON: Maybe you don't know what you're like. Maybe you need someone to teach you. Do you know who I am?

\YARA: You think I offer free rides to every man in jewelry, Lord Greyjoy?

\ti{\YARA ~and \THEON ~pass the \OLDMAN ~as they are walking. He is leading a horse. \THEON ~gives him some more coins.}

\THEON: Have my things sent up to the castle. \ti{(\YARA ~and \THEON ~ride on horseback on a beach. \YARA ~is at the reins.)} You should give me the reins. I'm a better rider than you. I've been on horseback for the past nine years.

\YARA: Nine years? Do you still know your way around a ship? Have these hands ever touched a rope?

\THEON: Don't you worry about my hands. The sea is in my blood.

\ti{He starts fondling her.}

\YARA: Your blood will be in the sea if I don't watch where I'm going.

\THEON: I have a proposal for my father, one that will make him king again, and me after him. You may get to stay in a castle tonight if you're lucky.

\YARA: Is that an offer from my future king?

\THEON: An order from your future king. You can tell your grandchildren about this night.

\YARA: I don't imagine it will be a story fit for children.


\scene

\textit{INSIDE PYKE}

\ti{\BALON ~sits in front of a fireplace. \THEON ~enters the room.}

\THEON: Father.

\BALON: Nine years, is it? They took a frightened boy. What have they given back?

\THEON: A man. Your blood and your heir.

\BALON: We shall see. Stark had you longer than I did.

\THEON: Lord Stark is gone.

\BALON: And how do you feel about that?

\THEON: What's done is done. I've brought you a proposal from Robb Stark.

\BALON: Who gave you those clothes? Was it Ned Stark's pleasure to make you his daughter?

\THEON: If my clothes offend you, I will change them.

\BALON: You will. That bauble `round your neck ... did you pay the iron price for it or the gold? \sd{\THEON ~looks down.} I asked a question. Did you pull it from the neck of a corpse you made or did you buy it to match your fine clothes? Iron or gold?

\THEON: Gold.

\BALON: I'll not have my son dressed as a whore.

\ti{\BALON ~reaches out and rips the bauble off. \THEON's cloak falls to the ground.}

\BALON: My fears have come true$\ldots$ the Starks have made you theirs.

\THEON: My blood is salt and iron.

\BALON: Yet the Stark boy sends you to me like a trained raven clutching his message.

\THEON: The offer he makes is one I proposed.

\BALON: He heeds your counsel?

\THEON: I've lived with him, hunted with him, fought at his side. He thinks of me as a brother.

\BALON: No, not here, not in my hearing. You will not name him brother, this son of the man who put your true brothers to the sword. Or have you forgotten your own blood?

\THEON: I forget nothing. I remember my brothers. And I remember when my father was a king.

\BALON: I see.

\THEON: I destroy Robb Stark's enemies for him and he will make me king of the Iron Islands once again. I will lead the attack myself.

\BALON: Oh, you will?

\THEON: I'm your son, your only living heir. Who else?

\ti{Enter \YARA.}

\THEON: I told you to wait outside. How did you get past the guards?

\YARA: Anything with a cock is easy to fool.

\BALON: My dear.

\THEON: Yara?

\YARA: So good to see you, brother. This is a homecoming I'll tell my grandchildren about.

\THEON: She can't lead an attack!

\BALON: And why not?

\THEON: You're a woman!

\YARA: You're the one in skirts.

\BALON: This isn't Winterfell, boy. Your sister took over command of your eldest brother's ship after your new father killed him.

\textbf{BALON/YARA/THEON}: \ti{(But \THEON ~joins in a little late.)} What is dead may never die.

\BALON: The only nights she's spent off these islands have been spent on the sea. She's commanded men. She's killed men. She knows who she is.

\ti{\BALON ~leans down and burns the letter in the fire. \YARA ~smirks at \THEON.}

\BALON: No man gives me a crown. I pay the iron price. I will take my crown, for that is who I am. That is who we have always been.

\ti{\BALON ~walks away. \YARA ~follows him. \THEON ~turns around to watch them leave.}

\THEON: You won't stand a chance against the Lannisters on your own.

\BALON: Who said anything about the Lannisters?


\scene

\textit{DRAGONSTONE}

\ti{\DAVOS ~and \SALLADHOR ~walk on a beach. \MATTHOS ~follows closely behind them.}

\DAVOS: You'll have your gold when we take the treasury at King's Landing.

\SALLADHOR: All these kings fighting for the throne, and this Stannis has the smallest army. Why would I bet on the man with the worst chance?

\DAVOS: Because you're a smart gambler. Stannis has proved himself in war twice. His baby brother has never set foot on a battlefield. Neither has the false King Joffrey.

\SALLADHOR: And yet they both have larger armies.

\DAVOS: Stannis has just begun the fight. His Bannermen will rally to his cause. There's no man in the Seven Kingdoms more honourable than Stannis Baratheon or more worthy of loyalty.

\SALLADHOR: What is the world coming to when smugglers must vouch for the honour of kings?

\MATTHOS: Mind your words, pirate.

\DAVOS: Matthos.

\SALLADHOR: You think I'm insulted? I am a pirate. I'm an excellent pirate. I don't sail for promises.

\DAVOS: Of course you do. Every time you leave harbour, you're leaving on a promise$\ldots$ a promise that somewhere on the sea, somebody's got some gold and you can take it from him.

\SALLADHOR: That's a promise that always comes true.

\DAVOS: As is mine. You're not a young man, Salladhor. And correct me if I'm wrong$\ldots$ most pirates don't grow old.

\SALLADHOR: Only the clever ones.

\DAVOS: You want to spend your last few years on the sea stealing from Pentoshi cheesemongers and Meereenese silk merchants? Then go. They're out there waiting for you. That's easy. What I'm offering you is hard. Come with me and plunder the greatest city in Westeros. You'll be the richest man in Lys and the most famous. They'll be singing songs about you as long as men have voices to sing.

\SALLADHOR: Salladhor Saan is a good name for songs.

\DAVOS: It is.

\SALLADHOR: One thing$\ldots$ I want the Queen.

\DAVOS: The Queen?

\SALLADHOR: Cersei. I want her. I'll sail with your fleet, all thirty of my ships. And if we don't drown at the bottom of Blackwater Bay, I will fuck this blonde Queen and I'll fuck her well.

\MATTHOS: This war isn't about you. We're not attacking King's Landing so that you can rape the Queen.

\SALLADHOR: I'm not going to rape her. I'm going to fuck her.

\MATTHOS: As if she would just let you.

\SALLADHOR: You don't know how persuasive I am. I've never tried to fuck you.

\MATTHOS: Stannis is the rightful king and the Lord of Light, the one true God---

\SALLADHOR: I've been all over the world, my boy, and everywhere I go, people tell me about the true gods. They all think they found the right one. The one true God is what's between a woman's legs, and better yet, a Queen's legs.

\ti{\MATTHOS ~walks away angrily. \SALLADHOR ~turns back to \DAVOS.}

\SALLADHOR: I never thought you'd have a true believer for a son.

\DAVOS: Eh, he's young yet. I promise you the gold. I promise you the glory. I cannot promise you the Queen.

\SALLADHOR: You believe your king can win?

\DAVOS: He is the one true King.

\SALLADHOR: You Westerosi are funny people. A man chops off your fingers and you fall in love with him.

\ti{They laugh.}

\SALLADHOR: I'll sail with you, Davos Seaworth. You're the most honest smuggler I ever met. Make me rich.

\DAVOS: Get me to the gates of King's Landing and I will.

\ti{They shake hands. \DAVOS ~pats \SALLADHOR ~on the back as he walks away. \DAVOS ~and \MATTHOS ~eye each other as \SALLADHOR ~walks past. \MATTHOS ~walks back over to his father.}

\MATTHOS: When will the King have us sail?

\DAVOS: As soon as his god wills it.

\MATTHOS: He's my God, too, and yours, but you are too blind to see. Let me teach you how to read.

\DAVOS: Oh, you and your mother.

\MATTHOS: It won't take long. You already know the letters. The holy books are much more persuasive than I can be.

\DAVOS: I wish I had a god, truly. I'm not mocking you, but I've seen men pray to every god there is: pray for wind, pray for rain, pray for home. None of it works.

\MATTHOS: But you always came home.

\DAVOS: I wasn't praying.

\MATTHOS: No, but I was. Every night that you were at sea, I lit a candle and I prayed for you.

\DAVOS: You want me to have a god? Fine. King Stannis is my god. He raised me up and blessed me with his trust. He gave you a future I could never have imagined. You know how to read. You'll be a knight someday. You think a fire god commanded all that? It was Stannis, only Stannis.

\MATTHOS: Stannis is my king, but he's only a man.

\DAVOS: Don't tell him that.

\ti{\DAVOS ~rides away and \MATTHOS ~watches. In the background, \SALLADHOR's boat is in the water.}


\scene

\textit{TYRION'S ROOM IN KING'S LANDING}

\ti{\TYRION ~sits at a table with a cup of wine. \CERSEI ~paces in front of him.}

\CERSEI: Lord Janos Slynt was commander of the City Watch. You had no right to exile him.

\TYRION: I have every right. I am the King's Hand.

\CERSEI: You're serving as the King's Hand till father gets here. I am Queen Regent.

\TYRION: Listen to me, Queen Regent. You're losing the people. Do you hear me?

\ti{\CERSEI ~laughs}

\CERSEI: The people. You think I care?

\TYRION: You might find it difficult to rule over millions who want you dead. Half the city will starve when winter comes. The other half will plot to overthrow you. And your gold-plated thugs just gave them their rallying cry: `The Queen slaughters babies'. You don't even have the decency to deny it.

\ti{\CERSEI ~looks down and walks toward the window. \TYRION ~looks down, and then up at her.}

\TYRION: It wasn't you who gave the order, was it? Joffrey didn't even tell you. Did he tell you? I imagine that would be even worse.

\CERSEI: He did what needed to be done. You want to be Hand of the King? You want to rule? This is what ruling is$\ldots$ lying on a bed of weeds, ripping them out by the root, one by one, before they strangle you in your sleep.

\TYRION: I'm no king, but I think there's more to ruling than that.

\CERSEI: I don't care what you think! You've never taken it seriously. You haven't, Jaime hasn't. It's all fallen on me.

\TYRION: As has Jaime, repeatedly, according to Stannis Baratheon.

\CERSEI: You're funny. You've always been funny$\ldots$ But none of your jokes will ever match the first one, will they? You remember? Back when you ripped my mother open on your way out of her and she bled to death?

\TYRION: She was my mother, too.

\CERSEI: Mother gone$\ldots$ For the sake of you. There's no bigger joke in the world than that.

\ti{\CERSEI ~storms out.}


\scene

\textit{DRAGONSTONE}

\ti{\DAVOS ~moves some ships around on a model map of Westeros as \MATTHOS ~looks on. \STANNIS ~enters with \MELISANDRE.}

\DAVOS: Your Grace.

\MATTHOS: Your Grace.

\STANNIS: How did you fare with your pirate?

\DAVOS: Salladhor Saan will join our fleet$\ldots$ thirty ships. His men know how to fight.

\STANNIS: In my experience, pirates prefer fighting unarmed men.

\DAVOS: It does seem the wiser choice.

\STANNIS: There won't be a choice this time. Do you trust him?

\DAVOS: Salladhor Saan is an old friend. I've known him thirty years. I've never trusted him, but once he gets the smell of gold, he never stops.

\STANNIS: Well, if he does his job, he'll have his share. Leave us.

\DAVOS: At once, Your Grace.

\ti{\DAVOS ~walks away, followed by \MATTHOS. As \MATTHOS ~passes her, \MELISANDRE ~stops him.}

\MELISANDRE: The Lord of Light shines through you, young warrior.

\ti{She then whispers something in his ear. When she is done, \MATTHOS ~and \DAVOS ~leave the room.}

\DAVOS: Come.

\STANNIS: What did you say to him?

\MELISANDRE: I told him death by fire is the purest death.

\STANNIS: Why?

\MELISANDRE: Because it is true. You're troubled, my king.

\STANNIS: Yeah.

\MELISANDRE: These armies are toys for the Lord of Light.

\STANNIS: Tell your lord to burn them, then.

\MELISANDRE: I tell him nothing. I pray for his commands and I obey.

\STANNIS: My little brother has a hundred thousand men according to the scouts, men whose allegiance rightly belongs to me.

\MELISANDRE: You must have faith.

\STANNIS: Faith? In a real war, the side with the greater number wins nine times out of ten.

\MELISANDRE: Then we must be the tenth.

\STANNIS: I cannot defeat my brother in the field. And I can't take King's Landing without the men he's stolen.

\MELISANDRE: I have seen the path to victory in the flames. But first, you must give yourself to the Lord of Light.

\STANNIS: I've said the words, damn you. I burnt the idols.

\MELISANDRE: You must give all of yourself.

\ti{\MELISANDRE ~disrobes next to \STANNIS. He looks over and then looks away.}

\STANNIS: I have a wife. I took a vow.

\MELISANDRE: She's sickly, weak. Shut away in a tower. She disgusts you. And she's given you nothing$\ldots$ no sons, only stillborns, only death. I will give you a son, my king.

\STANNIS: A son?

\ti{They begin kissing. \MELISANDRE ~takes off what remained of her clothes. \STANNIS ~lays her on the table and they begin fucking, knocking many of the wooden models off of the table.}


\scene

\textit{BEYOND THE WALL}

\ti{\JON ~is sitting by a fire. He hears a noise and looks behind himself, seeing \CRASTER ~walking away from the camp with a baby. \JON ~gets up to follow \CRASTER ~and investigate, and walks into the woods. He begins hearing strange noises, and hides when he sees \CRASTER ~walking back, without the baby. When \CRASTER ~is out of sight, he runs in the direction \CRASTER ~came from. He sees a figure lean down and pick up the baby. He is then startled by \CRASTER, who puts his hand on \JON's shoulder, and then knocks \JON ~out.}

\end{document}
