\input{preamble}
\input{ep15_cast}
\title{Episode 15 (S2E5): The Ghost Of Harrenhal}
\author{}
\date{}
\maketitle

\input{ep15_casttable}




\scene

\textit{RENLY'S TENT} 

\ti{\RENLY ~and \CATELYN ~are talking. \BRIENNE ~is attending \RENLY.}

\RENLY: You swear it? 

\CATELYN: By the mother. My son has no interest in the Iron Throne. 

\RENLY: Then I see no reason for hostility between us. Your son can go on calling himself King in the North, the Starks will have dominion over all lands north of Moat Cailin, provided he swears me an oath of fealty. 

\CATELYN: And the wording of this oath? 

\RENLY: The same Ned Stark swore to Robert eighteen years ago. Cat, their friendship held the kingdoms together. 

\CATELYN: And in return for my son's loyalty? 

\RENLY: In the morning I'll destroy my brother's army. When that's done, Baratheon and Stark will fight their common enemy together, as they have done many times before. 

\CATELYN: Our two houses have always been close, which is why I am begging you to reconsider this battle. Negotiate a peace with your brother. 

\RENLY: Negotiate with Stannis? You heard him out there. I'd have better luck debating the wind. Please bring my terms to your son. I believe we are natural allies. I hope he feels the same. Together we could end this war in a fortnight. 

\ti{Melisandre's dark shadow enters the tent, takes the form of \STANNIS, and stabs \RENLY ~in the neck. \RENLY ~starts choking.}

\BRIENNE: No! 

\ti{\RENLY ~falls down dead.}

\BRIENNE: No. 

\ti{She kneels at \RENLY's side.}

\ti{\GUARD ~rushes in.}

\GUARD: \sd{Charging at Brienne.} You'll die for this. 

\CATELYN: No, wait, it wasn't her! 

\ti{\BRIENNE ~fights and kills that \GUARD ~and several others. Then kneels again and sobs over \RENLY's corpse. \CATELYN ~comforts her.}

\CATELYN: We've got to leave. They'll hang you for this. Now! 

\BRIENNE: I won't leave him. 

\CATELYN: You can't avenge him if you're dead. 

\ti{\CATELYN ~pulls \BRIENNE ~up, and towards a door.}

\BRIENNE: Not that way. 

\ti{They go out a different way.}


\scene

\textit{RENLY'S TENT, LATER}

\ti{\LORAS ~is watching over the body. \MARGAERY ~is pacing.} 

\MARGAERY: We need to go home. Loras. 

\ti{Enter \LITTLEFINGER.}

\LITTLEFINGER: My Lord, My Lady. 

\LORAS: Get out. 

\LITTLEFINGER: Stannis will be here in an hour. When he arrives, Renly's bannermen will flock to him. Your former companions will fight for the privilege of selling you to their new king. 

\ti{\LORAS ~draws his sword, threatening \LITTLEFINGER.}

\LORAS: And you want that privilege for yourself. 

\LITTLEFINGER: You will note that I am standing here talking to you, not Stannis. 

\MARGAERY: There's no time for this. 

\LORAS: Ride back to Highgarden, sister. I'm not running from Stannis. 

\MARGAERY: Brienne of Tarth murdered Renly. 

\LORAS: I don't believe that. You don't believe that. Who gained the most from our king's death? 

\LITTLEFINGER: Stannis. 

\LORAS: I will put a sword through his righteous face. 

\MARGAERY: You can't stay here. 

\LORAS: He would have been a true king, a good king. 

\LITTLEFINGER: Tell me, Ser Loras, what do you desire most in this world? 

\LORAS: Revenge. 

\LITTLEFINGER: I have always found that to be the purest of motivations, but you won't have a chance to put your sword through Stannis, not today. You'll be cut to pieces before he sets foot on solid ground. If it is justice that you want, be smart about it. 

\MARGAERY: You can't avenge him from the grave. Bring the horses. Please. 

\ti{Exit \LORAS.}

\ti{\MARGAERY ~regards the body.}

\MARGAERY: He was very handsome. 

\LITTLEFINGER: He was, Your Grace. 

\MARGAERY: Your Grace? Calling yourself king doesn't make you one. And if Renly wasn't a king, I wasn't a queen. 

\LITTLEFINGER: Do you want to be a queen? 

\MARGAERY: No. I want to be the Queen. 

\ti{They exchange a look, then exit.}


\scene

\textit{KING'S LANDING} 

\ti{\TYRION ~and \CERSEI ~are talking, and drinking.}

\CERSEI: Killed? By whom? 

\TYRION: Accounts differ. Most seem to implicate Catelyn Stark in some way. 

\CERSEI: Really? Who'd have thought? 

\TYRION: Some say it was one of his own Kingsguard, while still others say it was Stannis himself who did it after negotiations went sour. 

\CERSEI: Whomever did it, I say well done. 

\TYRION: It's not what Varys says. He says Renly's army is flocking to support Stannis, which would give Stannis superiority over us on both land and sea. 

\CERSEI: Littlefinger says we can outspend him three to one. 

\TYRION: And I say father raised you to have too much respect for money. Stannis Baratheon is coming for us, sooner rather than later. 

\CERSEI: Aren't there other things you should be doing, like sealing my daughter in a crate so you can ship her away? 

\TYRION: She'll be safer in Dorne. 

\CERSEI: Yes, I know how concerned you are for her safety. 

\TYRION: It so happens that I am. Myrcella is a sweet, innocent girl and I don't blame her at all for you. 

\CERSEI: So clever. Aren't you always so clever with your schemes and your plots? 

\TYRION: Schemes and plots are the same thing. They are going to attack us. We need to be ready. 

\CERSEI: No need to concern yourself over it. The King is taking personal charge of siege preparations. 

\TYRION: May I ask specifically what the King has in mind? 

\CERSEI: You may specifically or you may ask vaguely. The answer will be the same. 

\TYRION: It's important that we talk about this. 

\CERSEI: It's the King's royal prerogative to withhold sensitive information from his councilors. 

\ti{Exit \TYRION. Then exit \CERSEI, smiling.}


\scene

\textit{A SMALL ENCLOSED COMPARTMENT} 

\ti{\LANCEL ~and \TYRION ~are talking in low voices. \BRONN ~is keeping guard outside.}

\LANCEL: It's wildfire. 

\TYRION: Wildfire? You wouldn't lie to me, would you, cousin? 

\LANCEL: No. 

\TYRION: That's a lie right there. 

\LANCEL: It is not a lie. Why would I lie? 

\TYRION: Tell me, if the vile allegations against my brother and sister are true, do you think it will make Jaime more likely to kill you or less likely? When I tell him you're fucking her, I mean. 

\LANCEL: I'm telling you the truth. 

\TYRION: The smart money would be on more likely. 

\LANCEL: She's making wildfire. 

\TYRION: But then perhaps his own unnatural urges will give him sympathy for yours. 

\LANCEL: The alchemists' guild is being commissioned. 

\TYRION: I suppose there's only one way to find out. 

\LANCEL: They have thousands of pots already stored in their vaults. They are planning to launch them from the city walls into Stannis's ships and armies. Please. 

\TYRION: When did she tell you this? 

\LANCEL: I heard her talking with the Pyromancer. And the other night after I left her, she went to meet him. I swear to you. 

\TYRION: Swear to me on what? 

\LANCEL: On my life. 

\TYRION: But I don't care about your life. 

\LANCEL: In the Light of the Seven, by all that is holy and right, I, Lancel Lannister, do solemnly vow $\ldots$  

\TYRION: All right, all right. Enough. Even torturing you is boring. Just get out. Oh, Lancel, tell my friend Bronn to please kill you if anything should happen to me. 

\ti{\BRONN ~kicks him on his way out.}

\LANCEL: Please kill me if anything should happen to Lord Tyrion. 

\BRONN: It will be my pleasure. 


\scene

\textit{STANNIS' CAMP} 

\ti{\STANNIS ~is striding, \DAVOS ~trying to keep up.}

\DAVOS: Your Grace. 

\STANNIS: What is it? 

\DAVOS: Your Grace. I'm sorry about your brother, Your Grace. I wanted to let you know that people grieve for him. Your Grace. 

\STANNIS: Fools love a fool. 

\DAVOS: Your Grace. 

\STANNIS: I grieve for him as well $\ldots$ for the boy he was, not the man he grew to be. 

\DAVOS: I need to speak to you about what I saw in that cave. 

\STANNIS: I thought I made it clear to you there'd be no need to speak to me on this matter. 

\DAVOS: Your Grace, I-- 

\STANNIS: I've never known you to need to hear a thing twice. 

\DAVOS: And I've never known you to hide from the truth. 

\STANNIS: You've come to lecture me on truth? 

\DAVOS: I've come to tell you that what I saw $\ldots$  

\STANNIS: All my brother's bannermen have come to my side. Except the Tyrells, who fled like cowards. They won't be able to resist us now. Soon I shall be sitting on the Iron Throne. 

\DAVOS: Nothing is worth what this will cost you, not even the Iron-- 

\STANNIS: I'll hear no more about it. 

\ti{They arrive into Stannis' tent.}

\STANNIS: When do we sail for King's Landing? 

\DAVOS: As soon as I've consolidated my troops. 

\STANNIS: We'll make short work of the Lannisters' fleet. Once Blackwater Bay is cleared, we'll deliver our troops to their doorstep and take the city. 

\DAVOS: And will you bring Lady Melisandre with you? 

\STANNIS: That's not your concern. 

\DAVOS: If you take King's Landing with her by your side, the victory will be hers. 

\STANNIS: I never thought I'd have reason to doubt your loyalty. Was I wrong? 

\DAVOS: Loyal service means telling hard truths. 

\STANNIS: Oh, truth again. All right, what's the truth? The hard truth? 

\DAVOS: She's a foreigner preaching her foreign religion. Some believe she whispers orders in your ear and you obey. 

\STANNIS: What do you believe? 

\DAVOS: You won those bannermen from Renly. Don't lose them to her. 

\STANNIS: We set out for King's Landing without Lady Melisandre. And you lead the fleet into Blackwater Bay. 

\DAVOS: Your Grace, I'm honoUred, but my time on the sea was spent evading ships, not attacking them. The other lords won't be happy. 

\STANNIS: Most of those lords should consider themselves lucky I don't hang them for treason. Hard truths cut both ways, Ser Davos. 

\ti{\DAVOS ~bows and exits, followed by \STANNIS.}


\scene

\textit{KING'S LANDING: MARKET} 

\ti{\TYRION ~and \BRONN ~are walking and talking.}

\TYRION: Stannis has more infantry, more ships, more horses. What do we have? 

\BRONN: There's that mind of yours you keep going on about. 

\TYRION: Well, I've never actually been able to kill people with it. 

\BRONN: Good thing. I'd be out of a job. What about your father? 

\TYRION: He hasn't sent a raven in weeks. He's very busy. Being repeatedly humiliated by Robb Stark is time-consuming. We won't be able to hold the city against Stannis, not the way Joffrey's planning on holding it. 

\ti{Enter a \PROTESTER, preaching from above. \TYRION ~and \BRONN ~watch and listen.}

\PROTESTER: Corruption, yes. We are swollen, bloated, foul. Brother fornicates with sister in the bed of Kings and we're surprised when the fruit of their incest is rotten? Yes, a rotten king. 

\ti{\PROTESTER ~continues waving arms and mouthing words, but we need to hear the following over him.}

\TYRION: It's hard to argue with his assessment. 

\BRONN: Not after what he did to your birthday present. 

\TYRION: The King is a lost cause. It's the rest of us I'm worried about now. 

\PROTESTER: A dancing king, prancing down his bloodstained halls to the tune of a twisted demon monkey. 

\TYRION: You have to admire his imagination. 

\BRONN: He's talking about you. 

\TYRION: What? Demon monkey? 

\BRONN: People think you're pulling the King's strings. They blame you for the city's ills. 

\TYRION: Blame me? I'm trying to save them. 

\BRONN: You don't need to convince me. 

\TYRION: Demon monkey. 


\scene

\textit{THE DOCKS} 

\ti{\THEON ~enters and proudly beholds the Sea Bitch. Then \LORREN ~and \DAGMER ~enter with other crew members.}

\THEON: You're the crew of the Sea Bitch? I'm your commander. Welcome. 

\ti{They all ignore him and load things into a boat.}

\THEON: Stop. Stop! Your Captain commands you to stop. 

\LORREN: Where are we heading, Captain? 

\THEON: The Stony Shore to raid their villages. There'll be spoils in it for you, and women, if you do your jobs well. 

\LORREN: And who decides if we've done our jobs well? 

\THEON: I do. Your Captain. 

\LORREN: I have been reaving and raping since before you left Balon's balls, Captain. Don't reckon I've got much use for your ideas on how to do it. Don't reckon I've got much use for a captain at all. I'm thinking I can do the job of captain real well myself. All I need is a ship. You wouldn't know where I could find myself a ship now, would you? 

\THEON: You could do that, take the ship, head out on your own. And I will hunt you down, drag you back here in chains, and hang you for a traitor. 

\ti{Everyone laughs. Enter \YARA, also laughing.}

\YARA: Stop. We yield. Congratulations on your first command. 

\THEON: Thank you. Kind of you to come see me off. 

\YARA: Oh, I'm not here for you. I was just on my way to Red Harbor. I've got 30 ships. There's nowhere to put them here. Too narrow. 

\THEON: You'd better get out there. Wouldn't want them to set sail without you. 

\YARA: That would never happen. My crew would wait on deck for a year if I asked them to. This lot, though$\ldots$ Enjoy the Stony Shore. 

\ti{\YARA ~leaves, so do YORREN and the others, except \DAGMER, who goes up to \THEON.}

\DAGMER: Come on, I'll take you out. 

\THEON: Who are you? 

\DAGMER: Dagmer, your first mate. 

\THEON: Why aren't you with the rest of them? Or did they send you to row me out and dump me halfway in the sea? That would be good for a laugh. 

\DAGMER: They're not gonna respect you until you prove yourself. 

\THEON: And how am I supposed to prove myself by pillaging piss-poor fishing villages? 

\DAGMER: You're not. 

\THEON: And yet that's the task my father has given me to prove that I'm a true Iron Islander. 

\DAGMER: They're all Iron Islanders. Do they do as they're told or do they do as they like? 

\THEON: The Stony Shore's not far from Torrhen's Square. 

\DAGMER: The seat of the House of Tallhart $\ldots$ a more impressive prize than a few fishermen's daughters. What, you don't think we could take it? 

\THEON: No, we could. We could never hold it for more than a few days. As soon as Winterfell got word that we'd taken Torrhen's Square, the Starks would send their men to take it back. And then $\ldots$ take me to my ship. 


\scene

\textit{HARRENHAL} 

\ti{\TYWIN ~is chairing a council of war, including \AMORY ~and \REGINALD. \ARYA ~is listening while cleaning cups on another part of the stage.}

\REGINALD: The Starks have overextended their lines. Now that summer's over, they'll have a hard time keeping their men and horses fed. 

\TYWIN: The Starks understand winter better than we ever will. The cold won't beat them. 

\AMORY: Our spies report growing discontent among the northern lords. They want to return home and gather the harvest before the crops turn. 

\TYWIN: And I'm sure if those same spies snuck into our own encampments, they would report growing discontent amongst the southern lords. 

\REGINALD: This is war; No one's content. 

\TYWIN: We've underestimated the Stark boy for too long. He has a good mind for warfare, his men worship him. And as long as he keeps winning battles, they'll keep believing he is King in the North. You've been waiting for him to fail. He is not going to fail, not without our help. So how do we stop him? 

\REGINALD: We've worked through the night, My Lord. Perhaps we'd profit from some sleep. 

\TYWIN: As I think you would, Reginald. And because you're my cousin, I might even let you wake from that sleep. Go, I'm sure your wife must miss you. 

\REGINALD: My wife's in Lannisport. 

\TYWIN: Well, then you'd better start riding. Go before I change my mind and send her your head. If your name wasn't Lannister, you'd be scrubbing out pots in the cook's tent. Go! 

\ti{\ARYA ~brings over a jug of wine and goes to pour.}

\TYWIN: Not wine, water. We'll be here for some time. 

\ti{She bows her head and goes to get it, but he calls her back.}

\TYWIN: Girl. Where are you from? 

\ARYA: Maidenpool, My Lord. 

\TYWIN: And who are the Lords of Maidenpool? Remind me. 

\ARYA: House Mooton, My Lord. 

\TYWIN: And what is their Sigil? 

\ti{She doesn't know.}

\TYWIN: A red salmon. I think a Maidenpool girl would remember that. You're a northerner, aren't you? 

\ti{She nods.}

\TYWIN: Good. One more time, where are you from? 

\ARYA: Barrowton, My Lord. House Dustin. Two crossed longaxes beneath a black crown. 

\TYWIN: And what do they say of Robb Stark in the North? 

\ARYA: They call him the young wolf. 

\TYWIN: And? 

\ARYA: They say he rides into battle on the back of a giant Direwolf. They say he can turn into a wolf himself when he wants. They say he can't be killed. 

\TYWIN: And do you believe them? 

\ARYA: No, My Lord. Anyone can be killed. 

\ti{The exchange a look.}

\TYWIN: Fetch that water. 


\scene

\textit{A CORRIDOR IN HARRENHAL} 

\ti{\ARYA ~is carrying a jug. She walks past a man. It turns out to be \JAQEN, better dressed now.}

\JAQEN: A girl says nothing. A girl keeps her mouth closed. No one hears, and friends may talk in secret, yes? A boy becomes a girl. 

\ARYA: I was always a girl. 

\JAQEN: And I was always aware. But the girl keeps secrets. It is not for a man to spoil them. 

\ARYA: You're one of them now. I should have let you burn. 

\JAQEN: And you fetch water for one of them now. Why is this right for you and wrong for me? 

\ARYA: I didn't have a choice. 

\JAQEN: You did. I did. And here we are. A man pays his debts. A man owes three. 

\ARYA: Three what? 

\JAQEN: The Red God takes what is his, lovely girl. And only death may pay for life. You saved me and the two I was with. You stole three deaths from the Red God. We have to give them back. Speak three names and the man will do the rest. Three lives I will give you $\ldots$ no more, no less, and we're done. 

\ARYA: I can name anyone and you'll kill him? 

\JAQEN: A man has said. 

\ARYA: The one who tortures everyone. 

\JAQEN: A man needs a name. 

\ARYA: I don't know his name. They call him the Tickler. 

\JAQEN: That is enough. Go now, girl. Your master is thirsty. 

\ti{They exit, each in the direction they were going previously.}


\scene

\textit{BEYOND THE WALL} 

\ti{The Night's Watch are marching. \JEOR ~and \JON ~are in the lead, followed by \SAM, then \GRENN ~and \EDD.}

\JEOR: He's not here yet. He'd have seen us, blown the horn. 

\JON: When will he come? 

\JEOR: The Halfhand does things in his own time. 

\JON: My uncle told me stories about him. 

\JEOR: Most of them are true. 

\JON: I heard the Halfhand spent half of last winter beyond the wall. 

\JEOR: The whole winter. He was north of the Skirling Pass when the snows came. Had to wait for the thaw. 

\JON: So it is possible for someone to survive out here on their own. 

\JEOR: Well, possible for the Halfhand. 

\SAM: Beautiful, isn't it? Gilly would love it here. 

\EDD: There's nothing more sickening than a man in love. 

\ti{They stop and make their camp.}

\SAM: The fist of the First Men. Think of how old this place is $\ldots$ before the Targaryens defeated the Andals, before the Andals took Westeros from the First Men. 

\EDD: Before I die, please, stop talking. 

\SAM: Thousands and thousands of years ago, the First Men stood here where we're standing all through the long night. What do you think they were like, the First Men? 

\EDD: Stupid. Smart people don't find themselves in places like this. 

\JON: I think they were afraid. I think they came here to get away from something. And I don't think it worked. 

\ti{A horn sounds.}

\GRENN: Wildlings? 

\JON: One blast is for rangers returning. Wildlings is two blasts. 

\EDD: So you got to stand there waiting, wondering. One blast for friends, two for foes. 

\SAM: And three for White Walkers. 

\ti{They all look at him.}

\SAM: It's been a thousand years, but that's the only time they blow the horn three times. 

\GRENN: But if it's been a thousand years, how do you know? 

\SAM: Well $\ldots$ 

\textbf{GRENN/EDD}: I read it in a book. 

\JON: Look. It's Qhorin Halfhand. 

\EDD: Aye, we'll live another day. Hurrah. 


\scene

\textit{THE ALCHEMISTS' GUILD}

\ti{\HALLYN ~is showing \TYRION ~and \BRONN ~the wildfire.} 

\HALLYN: Take care, My Lord. 

\TYRION: I remember reading an old sailor's proverb $\ldots$ piss on wildfire and your cock burns off. 

\HALLYN: Oh, I have not conducted this experiment. It could well be true. The substance burns so hot, it melts wood, stone, even steel, and, of course, flesh. The substance burns so hot, it melts flesh like tallow. After the dragons died, wildfire was the key to the Targaryen power. 

\ti{\BRONN ~scoffs.}

\TYRION: My companion takes issue. 

\BRONN: If I could tell you how many crazy old men I've seen pushing carts around army camps making grand claims about jars full of pig shit $\ldots$ no offense meant. 

\HALLYN: Our order does not deal in pig shit. The substance is fire given form. And we have been perfecting it since the days of Maegor. 

\BRONN: To do what? 

\HALLYN: The jars are put in catapults and flung at the enemy. 

\TYRION: How much do you have? 

\ti{\HALLYN ~starts getting a key to unlock the wildfire store.}

\BRONN: If you could get real soldiers to man the catapults, then maybe you'd hit your target one time in ten, but all the real soldiers are in the Riverlands with your father. 

\HALLYN: My Lord, this man is insulting. 

\ti{He unlocks a door and they are walking while \BRONN ~speaks.}

\BRONN: I don't know if you've ever seen a battle, old man, but things can get a bit messy. `Cause when we're flinging things at Stannis, he's flinging them right back at us. Men die, men shit themselves, men run, which means pots falling, which means fire inside the walls, which means the poor cunts trying to defend the city end up burning it down. 

\TYRION: My friend remains unconvinced. 

\HALLYN: He would not dare insult my order whilst Aerys Targaryen lived. 

\BRONN: Well, he's not living anymore. And all his pots of wildfire didn't help him, did they? Men win wars, not magic tricks. 

\ti{\HALLYN ~unlocks another door. They stare at the pots of wildfire.}

\HALLYN: We have been working tirelessly day and night ever since your royal sister commanded us to do so. Our present count stands at 7,811, enough to burn Stannis Baratheon's fleet and armies both. 

\BRONN: This is a shit idea. 

\TYRION: I'm afraid I have to concur with my advisor, wisdom Hallyne. The contents of this room could lay King's Landing low. You won't be making wildfire for my sister any longer. You'll be making it for me. 


\scene

\textit{QARTH} 

\ti{\DAENERYS ~and \DOREAH ~are playing with DROGON. In the background, \IRRI ~is sorting out some clothes. \DAENERYS ~gives DROGON a little bit of meat.}

\DAENERYS: Dracarys. 

\ti{Drogon squeaks.}

\DAENERYS: Dracarys. 

\ti{Drogon hisses, and takes the meat. \DAENERYS ~and \DOREAH ~laugh.}

\DAENERYS: He'll be able to feed himself from now on. 

\ti{\DAENERYS ~walks toward \IRRI. \DOREAH ~goes to feed DROGON some more meat.}

\DAENERYS: Let him sleep, Doreah. 

\DOREAH: Yes, Khaleesi. 

\DAENERYS: He loves you. 

\ti{\IRRI ~looks a bit jealous.}

\IRRI: \ti{Gesturing to a bodice, then a shoe.} Anha soqe akka jin sacchey essheyi. Qisi tim, anha arrisse vemishikh jinoon akka. [I rewove this part of the top. And I fixed the heel on this one.] 

\DAENERYS: Thank you, my friend. 

\ti{\DOREAH ~picks up the Qartheen dress to show it.}

\DOREAH: Did you see the dress Xaro had made for you? They say he's the wealthiest man in Qarth. 

\IRRI: It is known. 

\DOREAH: And if Qarth is the wealthiest city in Essos$\ldots$  

\DAENERYS: The last time a rich man gave me a dress, he was selling me to Khal Drogo. 

\IRRI: Me dothralates she Rhaeshi Ajjalani ayyeyaan. [May he ride through the Night Lands forever.] 

\DAENERYS: Xaro is our host, but we know nothing about him. Men like to talk about other men when they're happy. 

\ti{\DOREAH ~and \DAENERYS ~laugh.}

\DOREAH: You would look like a real princess in Xaro's-- 

\IRRI: She's not a princess. She's a Khaleesi. But you should wear it, Khaleesi. You are their guest. It would be rude not to. 


\scene

\textit{XARO'S GARDEN} 

\ti{A party. Guests mingle. \DAENERYS ~is talking to a \QARTHEENWOMAN.}

\QARTHEENWOMAN: And you must visit the night market. The Qartheen night market is like no night market you've ever seen. 

\DAENERYS: It sounds wonderful. 

\QARTHEENWOMAN: The Meereens think they have a night market. I will take you there myself. 

\ti{\MALAKKO and \KOVARRO ~start arguing in Dothraki in the background. \JORAH ~is with them.}

\DAENERYS: Please excuse me for a moment. 

\ti{She goes over to join them.}

\DAENERYS: What are they doing? 

\JORAH: Malakko says the statue is too heavy to carry. Kovarro says that Malakko is an idiot. They can pry out the gems, the rest is pure gold. Very soft. He can chop off as much as we can carry. 

\KOVARRO: Che ivvisaki mae. Disisse. [Or melt it. Very simple.] 

\DAENERYS: Kisha nevaki mae! Yer laz vos vefenari mae, vos tavi mae, vos ivvisi mae. [We are his guests! You can not pry it, nor chop it, nor melt it.] 

\KOVARRO: Vosecchi, zhey khaleesi! Kisha vayoki athezaraan kishi. [Of course not, Khaleesi! We will await our departure. 

\DAENERYS: Kash athezar kishi vos akka. [During our departure, not even.] 

\KOVARRO: Vos arrek? Kifindirgi? [Not then? Why?] 

\DAENERYS: Hash idrik kishi vijazero kisha Athasaroon Virzetha hash yer zali zifichelat moon? Anha acharak vos alikh. [Our host saved us from the Red Waste and you want to steal from him? I will hear no more.] 

\ti{\KOVARRO ~and \MALAKKO ~wander off. \DAENERYS ~and \JORAH ~start walking together.}

\DAENERYS: My brother used to say the only thing the Dothraki knew how to do was steal things better men have built. 

\JORAH: It's not the only thing. They're quite good at killing the better men. 

\DAENERYS: That's not the kind of queen I'm going to be. 

\ti{Enter \PYAT.}

\PYAT: Mother of Dragons. On behalf of the warlocks of Qarth, I welcome you. A demonstration? 

\ti{He puts a gem into her hand, and holds it.}

\PYAT: Take this gem. Look at it. Into its depths. So many facets. Look closely enough and you can see yourself in them. 

\ti{The crowd gasps.}

\PYAT: Often more than once. Should you grow tired of Xaro's baubles and trinkets, it would be an honour to host you at the House of the Undying. You're always welcome, Mother of Dragons. 

\ti{Exit \PYAT. The crowd applauds. Enter \XARO.}

\XARO: My apologies. Pyat Pree is one of the Thirteen. It was customary for me to extend him an invitation. Customs die slow deaths in Qarth. 

\DAENERYS: What is the House of the Undying? 

\XARO: It is where the warlocks go to squint at dusty books and drink shade of the evening. It turns their lips blue and their minds soft $\ldots$ so soft, they actually believe their parlor tricks are magic. 

\ti{\XARO ~leads \DAENERYS ~off. Enter \QUAITHE, a woman in a full mask, to \JORAH.}

\QUAITHE: You watch over her. 

\JORAH: Do I know you? 

\QUAITHE: I know you. Jorah Mormont of Bear Island. 

\JORAH: Who are you? 

\QUAITHE: I'm no one. But she is the Mother of Dragons. She needs true protectors now more than ever. They shall come day and night to see the wonder born into the world again. And when they see, they shall lust, for dragons are fire made flesh. And fire is power. 

\ti{\QUAITHE ~turns and goes.}


\scene

\textit{A WOODLAND CLEARING} 

\ti{\BRIENNE ~and \CATELYN ~have stopped to rest.}

\BRIENNE: It looked like Stannis. 

\CATELYN: To me it just looked like $\ldots$ a shadow in the shape of a man. 

\BRIENNE: In the shape of Stannis. 

\CATELYN: We should reach my son's camp tomorrow. 

\BRIENNE: Will you stay there long, My Lady? 

\CATELYN: Only long enough to tell Robb what I have seen. After that, I will leave for Winterfell. My two youngest need me. I've been away from them for far too long. 

\BRIENNE: I never knew my mother. 

\CATELYN: I'm sorry. My own mother died on the birthing bed when I was very young. 

\BRIENNE: It's a bloody business. 

\CATELYN: What comes after is even harder. 

\BRIENNE: Once you're safely back amongst your own people, will you give me leave to go, My Lady? 

\CATELYN: You mean to kill Stannis. 

\BRIENNE: I swore a vow. 

\CATELYN: But Stannis has a great army around him. His own guards are sworn to keep him safe. 

\BRIENNE: I'm as good as any of them. I should never have fled. 

\CATELYN: Renly's death was no fault of yours. You served him bravely. 

\BRIENNE: I only held him that once as he was dying. 

\CATELYN: He's gone, Brienne. You serve nothing and no one by following him into the earth. Renly's enemies are Robb's enemies as well. 

\BRIENNE: I do not know your son, My Lady $\ldots$ but I could serve you if you would have me. You have courage. Not battle courage, perhaps, but, I don't know, a woman's kind of courage. And I think that when the time comes, you will not hold me back. Promise me that you will not hold me back from Stannis. 

\CATELYN: When the time comes, I will not hold you back. 

\ti{\BRIENNE ~lays her sword in front of her to make the formal oath.}

\BRIENNE: Then I am yours, My Lady. I will shield your back and give my life for yours if it comes to that. I swear it by the Old Gods and the new. 

\ti{\CATELYN ~takes her hand.}

\CATELYN: I vow that you shall always have a place in my home and at my table and that I shall ask no service of you that might bring you dishonour. I swear it by the Old Gods and the new. 

\ti{Exeunt.}


\scene

\textit{WINTERFELL} 

\ti{\BRAN ~is giving an audience. \LUWIN ~attends him on his left. On his right, \RICKON ~is bored and chopping at the table with his pocket knife.}

\FARMER: $\ldots$ and it's not just thieves, My Lord. There's wolves in them hills now, more than I've ever seen. They come down in the night and they kill my sheep. My three sons is away fighting for your brother, My Lord. They'll fight, keep fighting till they're told to go home. I have no one to man my flock now. Only me. I can't keep watch all day and all night. 

\BRAN: We can send two orphan boys from Winterstown home with you to help watch over your flock if you can give them room and board. 

\FARMER: My wife always prayed for more children. We'll look after them. Thank you, My Lord. And may the Gods bless you and yours. 

\BRAN: \sd{To \RICKON.} Stop it. \sd{To \LUWIN.} If that's everyone, I'm going to go for a ride before dark. 

\LUWIN: Good. 

\BRAN: Hodor. 

\HODOR: Hodor. 

\ti{Enter \RODRIK.}

\RODRIK: Bran $\ldots$ Lord Stark. Torrhen's Square is under siege. 

\LUWIN: Torrhen's Square is barely forty leagues from here. How can the Lannisters strike so far north? 

\RODRIK: Might be a raiding party led by the Mountain. Might be Sellswords paid by Tywin Lannister. 

\BRAN: We have to help them. 

\RODRIK: Most of the fighting men are away with Robb, but I can gather two hundred decent men. 

\LUWIN: Do you need so many? 

\BRAN: If we can't protect our own bannermen, why should they protect us? Go, Ser Rodrik. Take the men you need. 

\RODRIK: Won't take long, My Lord. Southerners don't do well up here. 


\scene

\textit{WINTERFELL: COURTYARD} 

\ti{\HODOR ~is carrying \BRAN. \OSHA ~is walking beside them.}

\BRAN: So, what does it mean? 

\OSHA: Ask your Maester Luwin. He's the one studying books all the time. 

\BRAN: I did ask him. He'd never heard of a three-eyed raven. 

\OSHA: Must not mean anything, then. 

\BRAN: You're lying. 

\OSHA: You might be a little lord, but don't you call me a liar. 

\BRAN: You know what it means. 

\OSHA: I never said I didn't. 

\BRAN: You didn't give me an honest answer. 

\OSHA: That's not the same as being a liar. 

\BRAN: Well, it's not far off. 

\OSHA: So, you've been dreaming of a three-eyed raven again? In the Godswood, you told me you didn't dream. Now who's a liar? What did you see in your dream? Something bad? Tell me, boy. 

\BRAN: I dreamt that the sea came to Winterfell. I saw waves crashing against the gates and the water came flowing over the walls $\ldots$ flooded the castle. Drowned men were floating here in the yard. Ser Rodrik was one of them. 

\OSHA: The sea is hundreds of miles away. 

\BRAN: I know. It's just a stupid dream. 

\OSHA: I've got to get these potatoes to the kitchen. Otherwise they'll put me in chains again. 

\BRAN: Osha. The three-eyed raven, what do they say about it north of the wall? 

\OSHA: They say all sorts of crazy things north of the wall. 


\scene

\textit{BEYOND THE WALL} 

\ti{\HALFHAND, \JEOR, \SAM, \GRENN, \JON ~and others are looking up.}

\HALFHAND: There. 

\JEOR: Where? 

\HALFHAND: On that Mountain. 

\SAM: I don't see very well. 

\JON: A fire. 

\HALFHAND: There's a fire. The people sitting around it have better eyes than yours or mine. When they see us coming, that fire becomes a signal. Gives Mance Rayder plenty of time to throw a party in our honour. 

\JEOR: How many wildlings have joined him? 

\HALFHAND: From what we can tell, all of them. Mance has gathered them all like deer against the wolves. They're almost ready to make their move. 

\JON: Where? 

\HALFHAND: Somewhere safe. Somewhere south. Can't just march into their midst. And we can't wait for them here with nothing but a pile of stones to protect us. 

\JEOR: You saying we should fall back to the Wall? 

\HALFHAND: Mance was one of us once. Now he's one of them. He's gonna teach them our way of doing things. They'll hit us in force. And they won't run away when we hit back. They're gonna be more organized than before, more disciplined more like us. So we need to be more like them, do things their way. Sneak in, kill Mance, and scatter them to the winds before they can march on the Wall. And to do that $\ldots$ 

\JEOR: We need to get rid of those lookouts. 

\HALFHAND: It's not a job for four hundred men. I need to move fast and silent. Harker, Stonesnake, Borba. 

\JON: Lord Commander, I'd like to join Lord Qhorin. 

\HALFHAND: I've been called lots of things, but that might be my first Lord Qhorin. 

\JEOR: You're a steward, Snow, not a ranger. 

\JON: I've fought and killed a Wight. How many rangers can say that? 

\HALFHAND: He's the one? 

\JEOR: Aye. You killed a Wight. You also let an old man beat you bloody and take your sword. 

\ti{Scattered laughter.}

\HALFHAND: Craster? In the boy's defense, that's a tough old goat. 

\SAM: I could take up Jon's duties while he's gone, My Lord. It would be no trouble. 

\JEOR: Well, I hope you make a better ranger than you do a steward. Go on. 


\scene

\textit{QARTH} 

\ti{\DAENERYS ~and \XARO ~are walking along a corridor.}

\XARO: So, tell me, how long has your manservant been in love with you? 

\DAENERYS: He's not my manservant and he's not in love with me. He's my advisor, my friend. 

\XARO: Unlikely. I can almost always tell what a man wants. 

\DAENERYS: And what about what a woman wants? 

\XARO: Much more complicated. You, for example, what do you want? 

\DAENERYS: To cross the Narrow Sea and take back the Iron Throne. 

\XARO: Why? 

\DAENERYS: Because I promised my Khalasar I'd protect them and find them a safe home. 

\XARO: \sd{Laughing.} You want to conquer the Seven Kingdoms for the Dothraki? 

\DAENERYS: I want them because they're mine by right. The Iron Throne is mine and I will take it. 

\XARO: Ah, a conqueror. 

\DAENERYS: And how did you get all of this? Did someone give it to you? 

\XARO: No. I come from nothing. I hit the docks like a piece of cargo, except someone normally cares what happens to cargo. 

\DAENERYS: So you wanted more than you had and you took it. You're a conqueror, too. you're just less ambitious. 

\ti{\XARO ~laughs.}

\XARO: Mmm. 

\DAENERYS: What do you want, Xaro Zhoan Daxos? At the gates of the city, you bled for me. Why? 

\XARO: I will show you why. 

\ti{He takes her hand and leads her to a door, which he strikes with his sword.}

\XARO: The door and the vault is made of Valyrian stone. The hardest steel does not make a mark. I offered the greatest locksmiths in Qarth their weight in gold if they could break into it. I made the same offer to the greatest thieves. They all went home empty-handed. The only thing that can open this door is this key. 

\ti{He holds up the pendant he wears.}

\DAENERYS: And behind the door? 

\ti{\XARO ~chuckles.}

\DAENERYS: And it can all be mine? 

\XARO: All? Let us say half. More than enough to buy horses, ships, armies $\ldots$ enough to go home. 

\DAENERYS: All I have to do? 

\XARO: Is marry me. 

\DAENERYS: That was a romantic proposal. 

\XARO: I've already married once for love, but the Gods stole her from me. I come from nothing. My mother and father never owned a pair of shoes. But marry me and I will give you the Seven Kingdoms and our children will be princes and princesses. See? I have more ambition than you thought. The time is right, Daenerys Targaryen, first of your name. Robert Baratheon is dead $\ldots$ 

\ti{They exchange a look.}


\scene

\textit{A ROOM IN QARTH} 

\ti{\DAENERYS ~and \JORAH ~are arguing.}

\JORAH: If you cross the sea with an army you bought-- 

\DAENERYS: The Seven Kingdoms are at war with one another. Four false kings destroying the country. 

\JORAH: To win Westeros, you need support from Westeros. 

\DAENERYS: The usurper is dead. The Starks fight the Lannisters, and Baratheons fight each other. 

\JORAH: According to your new friend who earned your trust by cutting his hand? 

\DAENERYS: The time to strike is now. We need to find ships and an army or we'll spend the rest of our lives rotting away at the edge of the world. 

\JORAH: Rich men do not become rich by giving more than they get. They'll give you ships and soldiers and they'll own you forever. Moving carefully is the hard way, but it's the right way. 

\DAENERYS: And if I'd listened to that advice outside the gates of Qarth, we'd all be dead by now. 

\JORAH: I know the opportunity before you seems like the last you'll ever have, but you must--  

\DAENERYS: Do not speak to me like I'm a child. 

\JORAH: I only want-- 

\DAENERYS: What do you want? Tell me. 

\JORAH: To see you on the Iron Throne. 

\DAENERYS: Why? 

\JORAH: You have a good claim. A title. A birthright. But you have something more than that. You may cover it up and deny it, but you have a gentle heart. You would not only be respected and feared, you would be loved. Someone who can rule and should rule. Centuries come and go without a person like that coming into the world. There are times when I look at you and still can't believe you're real. 

\DAENERYS: So what would you have me do as my advisor? 

\JORAH: Make your own way. Find your own ship. You only need one. The allies we need are in Westeros, not Qarth. 

\DAENERYS: And how do I get the ship? 

\JORAH: I'll find it for you. A sound ship with a good captain. 

\DAENERYS: I look forward to meeting him. 

\JORAH: Khaleesi. 

\ti{\JORAH ~bows his head and goes. \DAENERYS ~follows.}


\scene

\textit{HARRENHAL} 

\ti{\GENDRY ~is forging a sword. \ARYA ~is watching. He swings it around.}

\ARYA: You should stand sideface. 

\GENDRY: Sideface? 

\ARYA: Sideways. 

\GENDRY: Why? 

\ARYA: Smaller target. 

\GENDRY: Am I fighting someone? 

\ARYA: You're practicing for a fight. You should practice right. 

\ti{Offstage scream. \TICKLER ~falls from a great height. There is general chaos -- see lines below. \ARYA ~looks up and sees \JAQEN, who touches his face as though tracing a teardrop.}

\VOICES: Guards! 

Help. 

Did you see anything? 

Go up there. Go and see where he fell from. 

Go up the back. 

That is strange. 

Move away. 

Stand back. 

He's dead. 

\end{document}
