\input{preamble}
\input{ep19_cast}
\title{Episode 19 (S2E9): Blackwater}
\author{}
\date{}
\maketitle
\newcommand{\SGNS}{\textbf{SERVING GIRL}}
\newcommand{\SERI}{\textbf{SER ILYN}}

\input{ep19_casttable}


\scene

\textit{STANNIS' FLAGSHIP}

\ti{The fleet is sailing to King's Landing, at night. \MATTHOS ~and \DAVOS ~are on the poop deck.} 

\MATTHOS: The tide's against us. 

\DAVOS: Aye, but we have the wind. She'll blow us straight to the gates. 

\MATTHOS: You're coming home. 

\DAVOS: King's Landing hasn't been home for twenty years. I spent most of my life dodging the Royal Fleet. And now I'm sailing right at them. 

\MATTHOS: This is the Royal Fleet.  And you're not a smuggler anymore, you're the high captain. 

\DAVOS: Of course there are several Royal Fleets at the moment. 

\MATTHOS: Not after tonight. When the sun rises, Stannis will sit on the Iron Throne and you will be his Hand. 

\DAVOS: Gods be good. 

\MATTHOS: God. Father, there is only one and he watches over us. 

\DAVOS: But not over them? 

\MATTHOS: Over all of us. The people of King's Landing did not choose the false King Joffrey Baratheon. They will be glad to see his head on a spike. 

\DAVOS: Well, first we have to put it there. 

\MATTHOS: Our ships outnumber theirs ten to one. Our army outnumber theirs five to one. 

\DAVOS: Those walls have never been breached. And the men guarding the walls, when they see you, they don't see a liberator. They see a stranger come to set their city on fire. 

\MATTHOS: I have faith in the Lord of Light. I have faith in our cause. And I have faith in my captain. 


\scene

\textit{THE HAND'S CHAMBERS}

\ti{\TYRION ~and \SHAE ~are in bed.} 

\SHAE: Are you afraid, my lion? 

\TYRION: If the city falls, Stannis will burn every Lannister he can find. Of course I'm afraid. 

\SHAE: I won't let them hurt you. 

\TYRION: I'm a Lannister. I don't have a choice in all this. But it's not your war. 

\SHAE: It is now.

\ti{She straddles him.} 

\TYRION: You can't fuck your way out of everything. 

\SHAE: I have so far. Do you remember what you said when you met me in your tent? That I should make love to you like it was your last day on this
earth.

\ti{They kiss.}


\scene

\textit{CERSEI'S CHAMBER.}

\ti{\PYCELLE ~and \CERSEI ~are talking.} 

\PYCELLE: As you know, Your Grace, it is not only the sworn duty of a Maester to carry out the wishes of the house he serves, but also to offer guidance and counsel in times of war. 

\CERSEI: Your words are always wise and measured. If you could---  

\PYCELLE: If anything, a Maester's duties become more urgent in times of war and turmoil. I remember back in the days of king---  

\CERSEI: You brought me something? 

\PYCELLE: Yes. \sd{Hands her a small bottle.} Essence of Nightshade is as dangerous as it is efficacious. A single drop in a cup of wine suffices to soothe ragged nerves. Three drops will bring on a deep and dreamless sleep. 
Ten drops, however$\ldots$  

\CERSEI: I know what ten drops will bring. 

\PYCELLE: Your Grace, if I may ask---  

\CERSEI: You may not. You must have a lot of work to do. I'm sure many brave men will need your wisdom soon. 

\PYCELLE: Yes. A siege is very---  

\CERSEI: Be careful on the stairs, Grand Maester. There are so many. 

\PYCELLE: Your Grace.


\scene

\textit{A TAVERN IN KING'S LANDING}

\ti{\WHORE ~is sat on \BRONN's lap. \textbf{SER MANDON} is sat at a nearby table. Everyone has been drinking.} 

\textbf{BRONN/LANNISTERS}: \sd{Singing, a little drunkenly.} 

    And so he spoke, and so he spoke, \\
    That lord of Castamere, \\
    But now the rains weep o'er his hall, \\
    With no one there to hear. \\
    Yes now the rains weep o'er his hall, \\
    And not a soul to hear.

\BRONN: \sd{Toasting.} To the boys! 

\ti{Cheers.}

\textbf{SER MANDON}: Where'd you learn the Lannister song? 

\BRONN: Drunk Lannisters. 

\ti{Laughter.}

\WHORE: You've got a pretty voice. 

\BRONN: Thank you very much. \sd{Removes her clothes during the next bit of dialogue --- \textbf{WHORE} is naked by the `Third time' remark below}

\WHORE: And I like your nose. How many times you break it? 

\BRONN: Well, now let's see. First time I was five. Me mom smacked me with an iron poker. 

\WHORE: Ooh. 

\BRONN: Oh, it wasn't me she was aiming at. She was trying for me little brother. Now he was a real pest. Second time I was nine. Got in a scrap with a few older boys. They won. Third time$\ldots$ \sd{Eyeing her up.} Eh, you don't want to know about the third time. 

\WHORE: Poor nose. 

\BRONN: Don't feel sorry for him. He'll be halfway up your arse before the night's through. 

\ti{Enter \HOUND.}

\BRONN: Welcome, friend. This round's on me. \sd{to \WHORE.} I don't think he likes me. 

\HOUND: You think you're a hard man? 

\BRONN: I know it. It's warm in here. We've got beautiful women and good brown ale. Plenty for everyone. And all you want is to put one of us in the cold ground with no women to keep us company. 

\HOUND: Oh, there's women in the ground. I put some there myself. So have you. You like fucking and drinking and singing. But killing$\ldots$ killing's the thing you love. You're just like me. Only smaller. 

\BRONN: And quicker. Eh? 

\HOUND: Your Lord Imp is going to miss you. 

\ti{\BRONN ~steps towards the \HOUND, covertly reaching for a knife. They stare each other down.}

\BRONN: Aye. I expect he will someday. 

\sfx Bell tolling.

\BRONN: One more drink before the war? Shall we? 


\scene

\textit{THE HAND'S CHAMBER}

\ti{\PODRICK ~is arming \TYRION, who is walking to \VARYS.} 

\VARYS: I've always hated the bells. They ring for horror$\ldots$ a dead king, a city under siege. 

\TYRION: A wedding. 

\VARYS: Exactly. Podrick, is that it? 

\TYRION: Is that it? Nice touch. As if you don't know the name of every boy in town. 

\VARYS: I'm not entirely sure what you're suggesting. 

\TYRION: I'm entirely sure you're entirely sure what I'm suggesting. 

\VARYS: Do you trust him? 

\TYRION: Oddly enough, I do. 

\VARYS: Good. The map you asked for. \sd{Spreads it out on a table.}

\TYRION: There must be twenty miles of tunnels beneath the city. 

\VARYS: Closer to fifty. The Targaryens built this city to withstand a siege and to provide escape if necessary. 

\TYRION: I'm not escaping. Strange as it sounds, I'm the captain of the ship. And if the ship goes down, I go with her. 

\VARYS: That is good to hear. Though I'm sure many captains say the same while their ship is afloat. You look well suited for battle, My Lord. 

\TYRION: Well, I'm not. 

\VARYS: For all our sakes, I hope you are wrong. My little birds tell me that Stannis Baratheon has taken up with a Red Priestess from Asshai. 

\TYRION: What of it? 

\VARYS: You don't believe in the old powers, My Lord? 

\TYRION: Blood spells, curses, shape-shifting$\ldots$ what do you think? 

\VARYS: I think you believe in what you see and in what those you trust have seen. You probably don't entirely trust me. 

\TYRION: Mm, don't take it personally. I don't entirely trust myself. 

\VARYS: And yet I have seen things and heard things$\ldots$  things you have not, things I wish I had not. I don't believe I've ever told you how I was cut. 

\TYRION: No, I don't believe you have. 

\VARYS: One day I will. The dark arts have provided Lord Stannis with his armies and paved his path to our door. For a man in service to such powers to sit on the Iron Throne, I can think of nothing worse. And tonight, I believe you are the only man who can stop him. 

\ti{\PODRICK ~gives \TYRION ~his axe.}


\scene

\textit{STANNIS' FLAGSHIP.}

\ti{\MATTHOS ~and \DAVOS, as before.} 

\sfx Bells tolling

\MATTHOS: They're welcoming the new king. 

\DAVOS: I've never known bells to mean surrender. They want to play music with us? Let's play. Drums. 

\MATTHOS: \sd{Shouting.} Drums! 

\sfx Drums


\scene

\textit{KING'S LANDING: GREAT HALL.}

\ti{\TYRION ~and \BRONN.} 

\TYRION: Remember, wait till the ships---  

\BRONN: The ships are in the bay. 

\TYRION: They must be far enough in so they won't be---

\BRONN: I know what in means. Do you know how to use that? 

\TYRION: I chopped wood once. No, I watched my brother chopping wood. 

\BRONN: I saw you kill a man with a shield. You'll be unstoppable with an axe. Don't get killed. 

\TYRION: Nor you, my friend. 

\BRONN: Oh, are we friends now? 

\TYRION: Of course we are. Just because I pay you for your services doesn't diminish our friendship. 

\BRONN: Enhances it, really. 

\TYRION: Oh, enhances. Fancy word for a sellsword. 

\BRONN: Been spending time with fancy folks. 

\ti{Enter \SANSA ~and \SHAE; also \JOFFREY ~at the other end of the hall.}

\TYRION: Lady Sansa and, uh, Sheila. 

\SHAE: Shae. 

\TYRION: Shae, yes. Surely my sister has asked you to join the other highborn ladies in Maegor's holdfast. 

\SANSA: She has, My Lord, but King Joffrey sent for me to see him off. 

\JOFFREY: \sd{Calling to her.} Sansa. 

\TYRION: He's a great romantic, my nephew. 

\JOFFREY: Sansa, come here. 

\SANSA: I will pray for your safe return, My Lord. 

\TYRION: Will you? 

\SANSA: Just as I pray for the King's. 

\ti{\SANSA ~moves away, towards \JOFFREY.}

\TYRION: \sd{To \SHAE.} Stay safe, My Lady. 

\SHAE: And you, my lion. 

\JOFFREY: Your king rides forth to battle. You should see him off with a kiss. My new blade \sd{Unsheathes it.} Hearteater I've named it. Kiss it \sd{\SANSA ~does so}. You'll kiss it again when I return and taste my Uncle's blood.

\SANSA: Will you slay him yourself? 

\JOFFREY: If Stannis is fool enough to come near me. 

\SANSA: So you'll be outside the gates fighting in the Vanguard? 

\JOFFREY: A king doesn't discuss battle plans with stupid girls. 

\SANSA: I'm sorry, Your Grace. You're right, I'm stupid. Of course you'll be in the Vanguard. They say my brother Robb always goes where the fighting is thickest. And he is only a pretender. 

\JOFFREY: Your brother's turn will come. Then you can lick his blood off Hearteater, too. 

\ti{Exit \JOFFREY.}

\SHAE: Some of those boys will never come back. 

\SANSA: Joffrey will. The worst ones always live. 

\SHAE: Shh. Come, My Lady. 


\scene

\textit{KINGS LANDING: THE RAMPARTS.}

\ti{\TYRION ~is looking out over the bay. Enter \LANCEL, \JOFFREY, \HOUND ~to him.} 

\LANCEL: Where's our fleet? 

\TYRION: On the way. 

\JOFFREY: Why isn't it here now? They're coming. Hound, tell the Hand that his King has asked him a question. 

\HOUND: The King has asked you a question. 

\TYRION: Ser Lancel, tell the Hound to tell the king that the Hand is extremely busy. 

\LANCEL: The Hand of the King would like me to tell you to tell the King$\ldots$  

\JOFFREY: If I tell the Hound to cut you in half, he'll do it without a second thought. 

\TYRION: That would make me the Quarterman. It just doesn't have the same ring to it. Cut me in half and I won't be able to give the signal. No signal, no plan. No plan and Stannis Baratheon sacks this city, takes the Iron Throne, puts your pinched little head atop a gate somewhere. It might be quite amusing, except that my head would be up there, too. I've never much liked my head, but I don't want to see it removed just yet. 


\scene

\textit{STANNIS' FLAGSHIP}

\ti{\DAVOS ~and \MATTHOS, as before.} 

\DAVOS: Where are their ships? 

\MATTHOS: It is wise to attack at night. We took them by surprise. 

\DAVOS: Lord Varys knows what you had for breakfast three days ago.  There are no surprises here. 

\MATTHOS: If it's true there is dissension in their ranks, maybe their sailors have mutinied. 

\DAVOS: Maybe. 


\scene

\textit{KINGS LANDING: MAEGOR'S HOLDFAST.}

\ti{\SANSA ~and \SHAE ~are in one corner; elsewhere \CERSEI ~sits, attended on by \SGNS. \SERI ~stands to one side.} 

\SANSA: I don't know why she wants me here. She's always saying how stupid I am. She hates me. 

\SHAE: Maybe she hates you less than she hates everyone else. 

\SANSA: I doubt it. 

\SHAE: Maybe she's jealous of you. 

\SANSA: Why would she be jealous? 

\CERSEI: Sansa. I was wondering where our little dove had flown. You look pale, child. Is your red flower still blooming? 

\SANSA: Yes. 

\CERSEI: Fitting, isn't it? The men will bleed out there and you will bleed in here. \sd{To \SGNS.} Pour Lady Sansa some wine. 

\ti{\SGNS ~pours a glass of wine, gives it to \CERSEI.}

\SANSA: I'm not thirsty, Your Grace. 

\CERSEI: So? I didn't offer you water. \sd{Passes \SANSA ~the glass.}

\SANSA: \sd{Looking at \SERI.} What's he doing here? 

\CERSEI: Ser Ilyn? He's here to defend us. When the axes smash down those doors, you may be glad to have him. 

\SANSA: But we have guards to defend us. 

\CERSEI: Guards we have paid. Should the city fall, they'll be the first ones out of the doors. 

\ti{Enter \textbf{SER MANDON}.}

\textbf{SER MANDON}: The lads caught a groom and two maids trying to sneak away with a stolen horse and some gold cups. 

\CERSEI: The battle's first traitors. Have Ser Ilyn see to them.  Put their heads on spikes outside thestables as a warning \sd{\textbf{SER MANDON} bows and exits, with \SERI}. The only way to keep the small folk loyal is to make certain they fear you more than they do the enemy.  Remember that if you ever hope to
become a queen.

\SANSA: You said he was here to protect us. 

\CERSEI: He is. Traitors are a danger to us all. More wine. 


\scene

\textit{KINGS LANDING: THE RAMPARTS / STANNIS' FLEET} 

\ti{In one corner of the stage, \MATTHOS ~and \DAVOS ~aboard Stannis' fleet.  On the ramparts are \TYRION, \JOFFREY, and a \SERGEANT. Elsewhere, on a cliff-top overlooking the bay, is \BRONN.}

\JOFFREY: There they are. 

\TYRION: Archers to their marks. 

\SERGEANT: Archers, to your marks! \sd{Pause.} Archers! Nock your arrows! 

\TYRION: Hold fast. 

\SERGEANT: Hold fast! 

\JOFFREY: What are you doing? We need to attack them. 

\TYRION: Hold fast. 

\NARRATOR: A single ship leaves the harbour and sails towards Stannis' fleet 

\JOFFREY: There's only one ship. Where are the rest of them? Where are the rest of them?! 

\MATTHOS: There's only one ship. 

\DAVOS: \sd{With a pause after each instruction whilst it is carried out.} Archers, stand to! Man the below! Nock! Draw! Hold. \sd{To himself.} There's no one on board. 

\n The ship gets closer, spilling a trail of wildfire behind it, and finally Davos sees and understands. 

\DAVOS: Wildfire. Steer clear! Steer clear! 

\ti{\TYRION ~gives the signal with a torch. \BRONN, seeing this, lights an arrow, shoots it at the wildfire.}

\n Bronn's flaming arrow arcs over the bay, coming down in the trail of wildfire left on the water$\ldots$

\DAVOS: Matthos! Get down! 

\sfx Massive explosion

\ti{Everyone is shocked by what they see, except \JOFFREY, who smirks}

\ti{\DAVOS ~\& \MATTHOS ~are both knocked down by the blast, their fate uncertain.}

\n The wildfire in the water acts like a fuse, leading to the ship full of wildfire. That explodes, filling the bay with a dreadful green light, and obliterating much of Stannis' fleet in a single blast. Men covered in burning wildfire throw themselves screaming into the water. The harbour is full of red and green flames and the sounds of dying men. The few surviving ships press grimly on towards the beach.

\STANNIS: Prepare to land. 

\CAPTAIN: Your Grace$\ldots$ 

\STANNIS: The dwarf has played his little trick. 

\CAPTAIN: The wildfire$\ldots$  

\STANNIS: He can only play it once. 

\CAPTAIN: We're too far from the gates. The fire, their archers$\ldots$ hundreds will die. 

\STANNIS: Thousands. \sd{Turns, addressing the men at arms in his ship.} Come with me and take this city! 

\ti{The crowd cheers.}


\scene

\textit{MAEGOR'S HOLDFAST}

\ti{\CERSEI ~continues to drink wine, attended by \SGNS. Elsewhere, \SANSA ~prays quietly with some other women.} 

\CERSEI: Sansa, come here, little dove. 

\SANSA: \sd{Going to her.} My Queen?

\CERSEI: What are you doing? 

\SANSA: Praying. 

\CERSEI: You're perfect, aren't you? Praying. What are you praying for? 

\SANSA: For the Gods to have mercy on us all. 

\CERSEI: Oh. On all of us? 

\SANSA: Yes, Your Grace. 

\CERSEI: Even me? 

\SANSA: Of course, Your Grace. 

\CERSEI: Even Joffrey? 

\SANSA: Joffrey is my--- 

\CERSEI: Oh, shut up, you little fool. Praying to the Gods to have mercy on us all. The Gods have no mercy. That's why they're Gods. My father told me that when he caught me praying. My mother had just died, you see. I didn't really understand the concept of death, the finality of it. I thought that if I prayed very, very hard, the Gods would return my mother to me. I was four. 

\SANSA: Your father doesn't believe in the Gods? 

\CERSEI: He believes in them, he just doesn't like them very much. \sd{To \SGNS.} One for her. \sd{\SGNS ~pours a glass, gives it to \CERSEI.} Here. \sd{Giving the glass to \SANSA.} Sit. Drink. \sd{\SANSA ~takes a little sip.} Not like that. Drink, girl. \sd{\SANSA ~does so.} I should have been born a man. I'd rather face a thousand swords than be shut up inside with this flock of frightened hens. 

\SANSA: They are your guests under your protection. You asked them here. 

\CERSEI: It was expected of me, as it will be of you if you ever become Joffrey's queen. If my wretched brother should somehow prevail, these hens will return to their cocks and crow of how my courage inspired them, lifted their spirits. 

\SANSA: And if the city should fall? 

\CERSEI: You'd like that, wouldn't you? The Red Keep should hold for a time, long enough for me to go to the walls and yield to Lord Stannis in person. If it were anyone else outside those gates, I might have hoped for a private audience. But this is Stannis Baratheon. I'd have a better chance of seducing his horse. Have I shocked you, little dove? Tears aren't a woman's only weapon. The best one's between your legs. Learn how to use it. Drink. Do you have any notion of what happens when a city is sacked? No, you wouldn't, would you? If the city falls, these fine women should be in for a bit of a rape. Half of them will have bastards in their bellies come the morning. You'll be glad of your red flower then. When a man's blood is up, anything with tits looks good. A precious thing like you will look very, very good. A slice of cake just waiting to be eaten. 

\scene

\textit{KINGS LANDING: THE RAMPARTS / THE BEACH}

\ti{\TYRION, \JOFFREY, \PODRICK, and \HOUND ~watch the advance. \JOFFREY ~looks scared. Nearby, \LANCEL ~is loitering out of harm's way, near \SERGEANT. \STANNIS ~and \CAPTAIN ~approach the castle (as per narration).}

\n Stannis and his troops row towards the beach.

\TYRION: He's a serious man$\ldots$ Stannis Baratheon. 

\JOFFREY: They're coming. They're coming ashore. 

\TYRION: Archers! Rain fire on them. 

\JOFFREY: There are too many. 

\TYRION: Hound, form a welcome party for any Baratheon troop that manages to touch solid ground \sd{\HOUND ~starts to leave, going towards \SERGEANT ~and \LANCEL.} Pod, run to the King's gate. Bring any men guarding it here now. 

\PODRICK: Yes, My Lord. \sd{Exit.}

\HOUND: Let's go. Stannis is sending us fresh meat. \sd{slaps \LANCEL ~on the chest} You too! \sd{to \SERGEANT} Any of these flaming fucking arrows come near me, I'll strangle you with your own guts. \sd{Exeunt \HOUND, \SERGEANT, \LANCEL.}

\n Stannis and his troops land amidst a hail of arrows. Nonetheless, many of them make it to the city wall.

\STANNIS: The mud gate, go now! 

\CAPTAIN: First and second squads, to the gate! To the mud gate! 

\ti{Re-enter \HOUND ~onto the beach, leading a sortie which includes \LANCEL.}

\HOUND: Any man dies with a clean sword, I'll rape his fucking corpse. 

\ti{People on the beach fight.}

\n The Hound's men engage the attackers in hand-to-hand combat on the beach. In the midst of the m\^el\'ee, an arrow finds Lancel Lannister$\ldots$

\ti{\LANCEL ~is wounded, and retreats.}


\scene

\textit{KING'S LANDING: MAEGOR'S HOLDFAST.}

\ti{\CERSEI ~(attended by \SGNS) and \SANSA ~talk, as before. \SERI ~has returned, and \SHAE ~is on stage.} 

\CERSEI: When we were young, Jaime and I, we looked so much alike even our father couldn't tell us apart. I could never understand why they treated us differently. Jaime was taught to fight with sword and lance and mace, and I was taught to smile and sing and please. He was heir to Casterly Rock and I was sold to some stranger like a horse to be ridden whenever he desired. 

\SANSA: You were Robert's queen. 

\CERSEI: And you will be Joffrey's. Enjoy--- \sd{Noticing \SHAE.} I don't think I know this one. \sd{They go over to \SHAE.}. Pretty. \sd{\SHAE ~curtsies, badly.} That's the worst curtsy I've ever seen. Here, it's not difficult. I mastered it when I was four. Straighten your back and bend. \sd{\SHAE ~curtsies, much better} Better. You learn fast. How long have you been in Lady Sansa's service?

\SHAE: A few weeks, Your Grace. 

\CERSEI: When did you leave Lorath? \sd{\SHAE ~is surprised.} I had a Lorathi handmaiden once. But she was a nobleman's daughter. You're not. When did you come to Westeros? 

\SHAE: Ten years ago, Your Grace. 

\CERSEI: From Lorathi commoner to the Red Keep in ten years, all without learning how to curtsy. I imagine that's a very interesting story. What's your name? 

\SHAE: Shae, Your Grace. 

\CERSEI: Tell us a story, Shae. 

\ti{An awkward pause.}

\SHAE: When I was thirteen, I--- 

\ti{Enter \LANCEL.}

\LANCEL: Your Grace! 

\CERSEI: What news? 

\LANCEL: The Imp has set the river afire. Hundreds of ships are burning, maybe more. Stannis's fleet destroyed, but$\ldots$ but$\ldots$ but his troops have landed outside the city walls. 

\CERSEI: Where is Joffrey? 

\LANCEL: On the battlements with Lord Tyrion. 

\CERSEI: Bring him back inside at once. 

\LANCEL: But, Your Grace$\ldots$  

\CERSEI: What? 

\LANCEL: The King's presence is good for morale. 

\CERSEI: Bring him back to his chambers now. 

\LANCEL: Not here? 

\CERSEI: With the women and children? Do you want him to be mocked as a coward for the rest of his life? 

\LANCEL: No, but I$\ldots$  

\CERSEI: Now! 

\ti{Exit \LANCEL}

\CERSEI: When I told you about Ser Ilyn earlier, I lied. Do you want to hear the truth? You want to know why he's really here? He's here for us. Stannis may take the city, he may take the throne, but he will not take us alive. 


\scene

\textit{KINGS LANDING: RAMPARTS / BEACH.}

\ti{\JOFFREY, \TYRION, \PODRICK, \textbf{SER MANDON} are on the Ramparts. A \textbf{SERVING BOY} is near the gate.} 

\n The beach is in chaos, with smoke and flames from the burning ships and flaming arrows making it hard to tell what is going on. And the Hound is afraid of fire$\ldots$

\ti{Enter \HOUND, retreating through the gate with his men.}

\HOUND: Someone bring me a drink. \sd{\textbf{SERVING BOY} hands him a water-skin}. Fuck the water. \sd{Discarding the water.} Bring me wine. \sd{\textbf{SERVING BOY} gives him a bottle of wine. \HOUND ~drinks deeply.}

\TYRION: Can I get you some iced milk and a nice bowl of raspberries, too? 

\HOUND: Eat shit, dwarf. 

\TYRION: You're on the wrong side of the wall. 

\HOUND: I lost half my men. The Blackwater's on fire. 

\JOFFREY: \sd{Scared, trying to cover.} Dog, I command you to go back out there and fight. 

\TYRION: You're Kingsguard, Clegane. You must beat them back or they're going to take this city$\ldots$ your king's city. 

\HOUND: Fuck the Kingsguard. Fuck the city. Fuck the King. \sd{Exit.}

\n Stannis' men invert row-boats over their heads to protect them from arrows and rocks hurled from the walls. Thus protected, they bring up a battering ram to the Mud Gate.

\ti{Enter \LANCEL, who runs to \JOFFREY.}

\LANCEL: Your Grace, the Queen has sent me to bring you back to the Red Keep. 

\TYRION: If you won't defend your own city, why should they? 

\JOFFREY: What would you have me do? 

\TYRION: Lead. Get down there and lead your people against the invaders who want to kill them. 

\JOFFREY: What did my mother say exactly? Did she have urgent business with me? 

\LANCEL: She did not say, Your Grace. 

\JOFFREY: Ser Boros, Ser Mandon, stay with my Uncle and represent the king on the field of battle. \sd{Exit with \LANCEL.}

\ti{The fighting men [audience!] notice the king depart, begin to mutter `where is the king?', mill around.}

\TYRION: \sd{Softly.} I'll lead the attack. \sd{To the troops.} I'll lead the attack! Pod, my helmet. Ser Mandon, you will bear the King's banner. Men, form up. They say I'm half a man. But what does that make the lot of you? 

\textbf{MAN 1}: The only way out is through the gates. And they're at the gates. 

\TYRION: There's another way out. I'm going to show you. We'll come out behind them and fuck them in their arses.  Don't fight for your king and don't fight for his kingdoms.  Don't fight for honour.  Don't fight for glory.  Don't fight for riches, because you won't get any.  This is your city Stannis means to sack.  That's your gate he's ramming.  If he gets in, it will be your houses he burns, your gold he steals, your women he will rape.  Those are brave men knocking at our door.  Let's go kill them.

\ti{Cheers. \TYRION ~leads the newly-heartened men off.}


\scene

\textit{MAEGOR'S HOLDFAST}

\ti{\CERSEI ~is sat with \TOMMEN. Elsewhere, \SHAE ~\& \SANSA ~sit together, and \SERI ~loiters. Enter \LANCEL.} 

\LANCEL: The battle is lost, Your Grace. Stannis's troops are at the gates. When the Goldcloaks saw the King leaving, they lost all heart. 

\CERSEI: Where is my son? 

\LANCEL: I want to escort him back to the battle. 

\CERSEI: Why do I care what you want? Bring me---

\LANCEL: Now listen to me--- 

\ti{\CERSEI ~hits \LANCEL ~where he is wounded. \LANCEL ~cries in pain, and falls to the floor. Exit \CERSEI, dragging \TOMMEN ~with her.}

\SANSA: \sd{Addressing the other women.} Don't be afraid. The Queen has raised the drawbridge. This is the safest place we can be. Joffrey's not hurt. He's fighting bravely. His knights have rallied behind him. They will save the city. Shall we sing a hymn? 

\ti{\SANSA ~starts to sing, and the other women join in, continuing for the rest of the scene.}

Gentle Mother, font of mercy,\\
Save our sons from war, we pray,\\
Stay the swords and stay the arrows,\\
Let them know a better day.

Gentle Mother, strength of women,\\
Help our daughters through this fray,\\
Soothe the wrath and tame the fury,\\
Teach us all a kinder way.

\SHAE: \sd{To \SANSA.} You must go. Run to your chamber and bar your door. Stannis won't hurt you. \sd{Indicating \SERI.} This one will. 

\SANSA: Come with me. 

\SHAE: I need to say goodbye to someone. 

\SANSA: The Queen said they'd rape everyone. 

\SHAE: \sd{Lifts her skirts, revealing a dagger strapped to her calf.} No one is raping me. Go. Run. \sd{\SANSA ~runs out.}


\scene

\textit{KINGS LANDING: SANSA'S CHAMBER}

\ti{\HOUND ~is concealed in a corner. Enter \SANSA. She goes to her dolls, and picks one up.} 

\HOUND: The lady is starting to panic. 

\SANSA: \sd{Startled.} What are you doing here? 

\HOUND: Not here for long. I'm going. 

\SANSA: Where? 

\HOUND: Someplace that isn't burning. North, might be. Could be. 

\SANSA: What about the king? 

\HOUND: He can die just fine on his own. I can take you with me. Take you to Winterfell. I'll keep you safe. Do you want to go home? 

\SANSA: I'll be safe here. Stannis won't hurt me. 

\HOUND: Look at me. Stannis is a killer. The Lannisters are killers. Your father was a killer. Your brother is a killer. Your sons will be killers someday. The world is built by killers. So you'd better get used to looking at them. 

\SANSA: You won't hurt me. 

\HOUND: No, little bird, I won't hurt you. \sd{Exit.}


\scene

\textit{KINGS LANDING: BEACH}

\ti{\CAPTAIN ~and \STANNIS ~are at the walls.} 

\CAPTAIN: Heave! Heave! Come on, you bastards! Get up those ladders! 

\ti{\STANNIS ~is first up the ladder, and exits onto the ramparts.}

\n Tyrion's forces pour through a secret gate, and take the attacking forces completely by surprise.

\ti{Enter \TYRION, who kills the surprised \CAPTAIN.}

\TYRION: Attack! Roll it over! \sd{Grabs torch, burns the rowboat/shield.}

\CROWD: Halfman! Halfman! Halfman! Halfman! Halfman! Halfman! Halfman! Halfman! 

\n The soldiers' celebrations are interrupted by the arrival of another large body of Stannis' troops.

\ti{Enter \PODRICK, and \textbf{SER MANDON}, seperately}

\TYRION: \sd{Seeing the attacking force.} Oh, fuck me. 

\sfx battle noises

\n Battle is joined again. In the m\^el\'ee, Tyrion is relieved to see a member of the Kingsguard$\ldots$

\ti{\textbf{SER MANDON} approaches \TYRION, and suddenly swings at him, wounding him in the face. As \textbf{SER MANDON} goes for the killing blow, \PODRICK ~stabs him from behind with a spear, killing him, then catches \TYRION ~as he collapses.}

\ti{Enter \TYWIN, leading a large force.}

\PODRICK: \sd{To \TYRION, seeing the troops arrive.} My lord!

\ti{\TYRION ~passes out in \PODRICK's arms.}

\scene

\textit{KINGS LANDING: THE GREAT HALL}

\ti{\CERSEI ~sits on the Iron Throne, \TOMMEN ~on her lap. She ~fidgets with the bottle of Nightshade that Pycelle gave her earlier.} 

\CERSEI: Shh. Be calm, my sweet. 

\TOMMEN: They're still fighting. 

\CERSEI: No one's going to hurt you. I'll tell you a story. You know the one about the mother lion and her little cub? They lived in the woods. 

\TOMMEN: The Kingswood. 

\CERSEI: Yes, my love. In the Kingswood there lived a mother and her cub. She loved him very much. But there were other things that lived in the woods. Evil things. 

\TOMMEN: Like what? 

\CERSEI: Like stags. 

\TOMMEN: Stags aren't evil. They only eat grass. 

\CERSEI: And wolves. He could hear them howling in the night. The little cub was frightened. His mother said, You are a lion, my son. You mustn't be afraid. For one day all the beasts will bow to you. You will be king. All the stags will bow. All the wolves will bow. The bears in the north and the foxes of the south, all the birds in the sky and the beasts in the sea$\ldots$ they will all come to you, little lion$\ldots$ to rest a crown upon your head. And the cub said, `Will I be strong and fierce like my father? `Yes,' said his mother. `You will be strong and fierce just like your father. I will keep you safe, my love. I promise you.'

\ti{\CERSEI ~raises the bottle to \TOMMEN's lips.}

\ti{With a crash, the doors open. Enter \TYWIN, with a large body of men. \CERSEI ~lets the bottle fall to the floor.}

\CERSEI: Father. 

\TYWIN: The battle is over. We have won. 

\ti{Freeze.}

\textbf{SINGER}: \sd{Off-stage.}

    And who are you, the proud lord said,\\
    That I must bow so low? \\
    Only a cat of a different coat, \\
    That's all the truth I know. \\
    In a coat of gold or a coat of red, \\
    A lion still has claws, \\
    And mine are long and sharp, my lord, \\
    As long and sharp as yours. \\
    And so he spoke, and so he spoke, \\
    That lord of Castamere, \\
    But now the rains weep o'er his hall, \\
    With no one there to hear. \\
    Yes now the rains weep o'er his hall, \\
    And not a soul to hear.\\

\end{document}
