\input{preamble}
\input{ep20_cast}
\title{Episode 20 (S2E10): Valar Morghulis}
\author{}
\date{}
\maketitle

\input{ep20_casttable}

\scene

\textit{KINGS LANDING: TYRION'S ROOM} 

\ti{\TYRION ~slowly awakens, his left eye and part of his face bandaged. As he gains consciousness, he sees \PYCELLE ~standing over him.}

\TYRION: Pod. Pod! \sd{Enter \PODRICK ~} Find Bronn or Varys. Tell them I am here with Maester Pycelle. Tell them I am very much alive. 

\PODRICK: Yes, My Lord. \sd{Exit \PODRICK.}

\PYCELLE: Would you like something for the pain? 

\TYRION: What happened? 

\PYCELLE: The murderer and traitor Stannis Baratheon suffered a stunning defeat at the hands of your father. 

\TYRION: Where am I? 

\PYCELLE: These are your new chambers. A little cramped, perhaps, but you don't need much room, do you? You are no longer Hand of the King. Oh. For your trouble. 

\ti{\PYCELLE ~throws \TYRION ~a coin. Exit \PYCELLE.}


\scene

\textit{KINGS LANDING: GREAT HALL} 

\ti{Enter \TYWIN. The Great Hall is full of people, with soldiers lining a passage to the Iron Throne where \JOFFREY ~sits, and the court standing in rows behind the soldiers. At the front, stand \LORAS ~and \MARGAERY, with \VARYS ~and \PYCELLE ~on the other side, all looking up at \TYWIN ~and \JOFFREY. \CERSEI ~sits on a low seat next to \JOFFREY. \SANSA ~looks on from a balcony above, along with more of the noblewomen.}  

\JOFFREY: I, Joffrey of the House Baratheon, first of my name, the rightful King of the Andals and the First Men, Lord of the Seven Kingdoms and protector of the Realm, do hereby proclaim my grandfather Tywin Lannister the saviour of the city and the Hand of the King. 

\TYWIN: Thank you, Your Grace. 

\JOFFREY: Lord Petyr Baelish, step forward. For your good service and ingenuity in uniting the Houses of Lannister and Tyrell, I declare that you shall be granted the castle of Harrenhal$\ldots$ With all its attendant lands and incomes to be held by your sons and grandsons from this day until the end of time. 

\LITTLEFINGER: You honour me beyond words, Your Grace. I shall have to acquire some sons and grandsons. 

\ti{General laughter.}

\JOFFREY: Ser Loras Tyrell. Your House has come to our aid. The whole realm is in your debt, none more so than I. If your family would ask anything of me, ask it and it shall be yours. 

\LORAS: Your Grace, my sister Margaery, her husband was taken from us before$\ldots$ She remains innocent. I would ask you to find it in your heart to do us the great honour of joining our Houses. 

\JOFFREY: Is this what you want, Lady Margaery?

\MARGAERY: With all my heart, Your Grace. I have come to love you from afar. Tales of your courage and wisdom have never been far from my ears. And those tales have taken root deep inside of me. 

\JOFFREY: Well, I too have heard tales of your beauty and grace, but the tales do not do you justice, My Lady. It would be an honour to return your love, but I am promised to another. A King must keep his word. 

\CERSEI: Your Grace, in the judgment of your small council, it would be neither proper nor wise for you to wed the daughter of a man beheaded for treason, a girl whose brother is in open rebellion against the throne as we speak. For the good of the realm, your councillors beg you to set Sansa Stark aside. 

\CROWD: \sd{General muttering and hubbub.} Margaery! We want Margaery! 

\JOFFREY: I would like to heed your wishes and the wishes of my people, but I took a holy vow. 

\PYCELLE: Your Grace, the gods do indeed hold betrothal solemn, but your father, blessed be his memory, made this pact before the Starks revealed their falseness. I have consulted with the High Septon and he assures me that their crimes against the realm free you from any promise you have made to them in the sight of the gods. 

\JOFFREY: \sd{To the room.} The gods are good. I am free to heed my heart. Ser Loras, I will gladly wed your sweet sister. \sd{\LORAS ~rises. \JOFFREY ~addresses \MARGAERY ~} You will be my Queen and I will love you from this day until my last day. 

\ti{Applause from the crowd. \JOFFREY ~swaggers back to his throne. \SANSA ~walks away, smiling when out of view of the noblewomen. \LITTLEFINGER ~approaches up the stairs, from behind \SANSA.}

\LITTLEFINGER: My Lady. My sincerest condolences. 

\SANSA: They're right$\ldots$ I'm not good enough for him. 

\LITTLEFINGER: You shouldn't say that. You'll be good enough for many things. He'll still enjoy beating you. And now that you're a woman, he'll be able to enjoy you in other ways as well. 

\SANSA: But if he's not marrying me$\ldots$  

\LITTLEFINGER: He'll let you go home? Joffrey's not the sort of boy who gives away his toys. You have a tender heart, just like your mother did at your age. I can see so much of her in you. She was like a sister to me. For her sake, I'll help get you home. 

\SANSA: King's Landing is my home now. 

\LITTLEFINGER: Look around you. We're all liars here. And every one of us is better than you. 


\scene

\textit{KINGS LANDING: LITTLEFINGER'S BROTHEL} 

\ti{\ROS ~sits in front of a mirror, applying make-up to bruises on her face. The door opens, with knocking at the same time. \ROS ~looks up briefly and continues applying concealing make-up.}

\ROS: Come in. Make yourself comfortable. 

\ti{Enter \VARYS ~in a hooded cloak. He sits on the bed, and \ROS ~rises and approaches him. She doesn't yet know who he is.} 

\ROS: That doesn't look very comfortable. Here, watch me. 

\ti{\ROS ~starts to undress, half taking off her top. \VARYS ~pulls back his hood.}

\VARYS: No need for that, my dear. 

\ROS: You sure? Most men like what they see. 

\VARYS: I'm not like most men. 

\ROS: That's what most men say. \sd{\ROS ~puts her top back on.} If you don't want what most men want, then you'd better tell me what you'd like me to do. \sd{\ROS ~sits next to \VARYS.}

\VARYS: I would like you to tell me if working for Lord Baelish has been all you'd hoped it would be. 

\ROS: Have we met? 

\VARYS: You wouldn't remember me if we had? 

\ROS: I meet a lot of men. 

\VARYS: And I think you remember all of them. I think your true talents are wasted on them. 

\ROS: You're very kind, My Lord. Allow me to return the favour. 

\ti{\ROS ~reaches for \VARYS� ~groin. She pauses, withdraws, and stands.}

\VARYS: You're afraid. Why? Nothing dangerous down there. 

\ROS: I know who you are. 

\VARYS: And, unlike your current employer, I protect those who work for me. I don't abuse them to satisfy royal whims or force them to abuse each other. 

\ROS: How do you know about that? 

\VARYS: I thought you said you knew who I was. 

\ROS: What can I do for you, Lord Varys?

\ti{\VARYS ~pats the bed, and \ROS ~reluctantly sits back down next to him. \VARYS ~lifts her chin with his finger.}

\VARYS: Littlefinger looks at you and sees a collection of profitable holes. I see a potential partner. 

\ROS: I'm afraid of him. 

\VARYS: Oh, you should be. He's a dangerous man. But everyone has their weaknesses. Your current employer hides his very well, but not as well as he thinks. 


\scene

\textit{THE WESTERLANDS} 

\ti{\JAIME ~stands on a rocky stretch by the water, while \BRIENNE ~hauls in a small boat. \JAIME's ~hands are tied to a rope, which is held by \BRIENNE.}

\JAIME: You're a virgin, I take it?

\ti{\BRIENNE ~has finished with the boat, and pushes \JAIME ~ahead.} 

\BRIENNE: Walk. 

\ti{They walk up the rocky shore towards the trees.}

\JAIME: Childhood must have been awful for you. Were you a foot taller than all the boys? They laughed at you, called you names? Some boys like a challenge. One or two must have tried to get inside big Brienne. 

\BRIENNE: One or two tried. 

\JAIME: Ah. But you fought them off. But maybe you wished one of them could overpower you, fling you down, tear off your clothes. But none of them were strong enough. I'm strong enough. 

\BRIENNE: Not interested. 

\JAIME: Of course you are. You'd love to know what it feels like to be a woman.

\ti{\BRIENNE ~looks up at three women hanging from a branch of a tree. Around the neck of the middle woman is a sign, reading: `THEY LAY WITH LIONS'.}

\JAIME: Ah. They lay with lions. Tavern girls, I'd say. Probably served my father's soldiers. Maybe one of them gave up a kiss and a feel. That's how they earned this. The glorious work of the northern freedom fighters. Must make you proud to serve the Starks. 

\BRIENNE: I don't serve the Starks. I serve Lady Catelyn. 

\JAIME: Tell yourself that tonight when they swing in your dreams. What are you doing? 

\ti{\BRIENNE ~pushes \JAIME ~forcefully towards a tree, and ties him up.}

\BRIENNE: Burying them. 

\JAIME: We shouldn't stay here. We should get back on the river. I think these women would understand if$\ldots$  

\BRIENNE: \sd{Approaching the women.} I don't care what you think. 

\STARKSOLDIERa: \sd{Offstage.} I didn't leave it here. 

\JAIME: \sd{Quietly, to \BRIENNE.} Untie me now. 

\STARKSOLDIERa: \sd{Offstage.} I gave it to you to cut the rope, and
now I don't have me dagger no more. So unless it got stuck in your ass
on its way to your cunt, it stands to reason that it's gone
$\ldots$ \sd{enter 2 \textbf{STARK SOLDIERS}} Whoa! What's your
business here?

\BRIENNE: Travelling a prisoner. 

\STARKSOLDIERa: \sd{Laughing uproariously.} You're a woman. A woman!

\STARKSOLDIERb: Well, fuck me! 

\BRIENNE: If you've quite finished up$\ldots$ \sd{\textbf{STARK SOLDIERS} start laughing again.} All right, we'll be going. \sd{\BRIENNE ~walks towards \JAIME.} 

\STARKSOLDIERa: Whoa, whoa. Who do you fight for? 

\BRIENNE: The Starks. \sd{\BRIENNE ~starts to untie \JAIME.} 

\STARKSOLDIERb: What did he do? 

\JAIME: \sd{Adopting a rather less noble accent.} Apparently eating is now a crime. Who knew? 

\BRIENNE: No, stealing is a crime. 

\JAIME: But it's not a crime to starve. That's justice for you. 

\STARKSOLDIERa: Where are you taking him? 

\BRIENNE: To Riverrun. 

\STARKSOLDIERb: Why Riverrun? 

\BRIENNE: Steal from the Tullys, it's their dungeons you rot in. 

\STARKSOLDIERb: Why not kill him? 

\JAIME: For stealing a pig? 

\BRIENNE: I don't give the orders. He must be important to someone. 

\STARKSOLDIERa: Sending him with you? How important could he be? All right, have it your way, m'lady. 

\STARKSOLDIERb: \sd{To \JAIME.} Do I know you? 

\JAIME: Have you been to Ashemark? 

\STARKSOLDIERb: No. 

\JAIME: Then you don't know me. 

\STARKSOLDIERb: Do you ever go to the river market at Salt Rock? 

\JAIME: Is it near Ashemark?

\STARKSOLDIERb: No. 

\JAIME: I've never been there. 

\STARKSOLDIERa: What do you think of these beauties? 

\ti{\BRIENNE ~pauses and looks back, as does \JAIME.}

\BRIENNE: I hope you gave them quick deaths. 

\STARKSOLDIERa: Two of them we did, yeah. 

\ti{\BRIENNE ~turns and starts walking again, pushing \JAIME ~in front of her.}

\STARKSOLDIERb: Wait. \sd{Walking up to \JAIME ~again.} I do know you. \sd{To \STARKSOLDIERa.} That's Jaime Lannister. 

\JAIME: I wish someone had told me. I wouldn't have had to steal that pig. 

\BRIENNE: If this is the Kingslayer, I think I'd know about it. 

\STARKSOLDIERa: How do you know what the Kingslayer looks like? 

\STARKSOLDIERb: I was at Whispering Wood. I saw him. They dragged him out of the woods and threw him down before the King. 

\BRIENNE: He's not the Kingslayer. Sorry to disappoint you. If he was, I'd only be traveling his head. 

\STARKSOLDIERb: I have a question for you both. And I want you to answer it at the same time. I count to three, you both answer. What's his name? One. Two. Three. 

\enlargethispage*{20pt}
\ti{Beat. \BRIENNE ~pushes \JAIME ~away and \BRIENNE
~and \textbf{STARK SOLDIERS} fight. \JAIME ~watches from the
side. \STARKSOLDIERb ~is quickly killed. \STARKSOLDIERa ~is disarmed
and knocked to the ground. He lies on the ground as \BRIENNE ~drops
her knives, and pulls out her sword.}

\BRIENNE: Two quick deaths. 

\ti{\BRIENNE ~provides \STARKSOLDIERa ~with a very slow death indeed.}

\JAIME: Those were Stark men. 

\BRIENNE: I don't serve the Starks. I serve Lady Catelyn. I told her I'd take you to King's Landing, and that's what I'm going to do. Stay.


\scene

\textit{ROBB'S CAMP} 

\ti{\ROBB ~is seated in his tent, and \CATELYN ~sits down near him.}

\CATELYN: Walder Frey is a dangerous man to cross. 

\ROBB: I know that. 

\CATELYN: And you mean to do it anyway? 

\ROBB: I love her. 

\CATELYN: I know that seems important to you. 

\ROBB: It is important to me. 

\CATELYN: Your father didn't love me when we married. He hardly knew me or I him. Love didn't just happen to us. We built it slowly over the years, stone by stone, for you, for your brothers and sisters, for all of us. It's not as exciting as secret passion in the woods, but it is stronger. It lasts longer. 

\ROBB: And that is what would be in store for me with one of Walder Frey's daughters, what you and father had? 

\CATELYN: Why not? Because she's not beautiful? Because she's not exotic and exciting? 

\ROBB: Now you're arguing just to argue because you arranged it. 

\CATELYN: And you agreed to it. You gave him your word. Treat your oaths recklessly and your people will do the same. If your father lived his life for one thing$\ldots$  

\ROBB: My father is dead. And the only parent I have left has no right to call anyone reckless.

\ti{Exit \ROBB.}


\scene

\textit{DRAGONSTONE} 

\ti{\STANNIS ~and \MELISANDRE ~stand with their backs to each other.}

\STANNIS: You said you saw my victory in the flames. 

\MELISANDRE: I did. I still see it. 

\STANNIS: The flames lied. And I'm no better than a savage trusting in a fire god. \sd{\MELISANDRE ~walks around until she is in front of \STANNIS ~} I fought for your god in Blackwater Bay. I led my men to the gates of the Seventh Hell as their brothers burned alive, and for what? Attacked from behind by Tywin Lannister and the Tyrells. If you see so much in your flames, why didn't you warn me? 

\MELISANDRE: The Lord of Light only allows me glimpses. 

\STANNIS: You claimed to speak for a god. 

\MELISANDRE: Will you quit the war just because you've lost a battle? 

\STANNIS: You talk about war as if you understand it. 

\MELISANDRE: I've been fighting far longer than you. 

\STANNIS: Have you? Show me how you fight. \sd{Putting hands round \MELISANDRE's ~neck and choking her.} Show me. Where's your god now? Will he save you? Where is your god? 

\MELISANDRE: Inside you. 

\ti{\STANNIS ~lets \MELISANDRE ~go, and she collapses to the floor, as he walks away, his back to her again.}

\STANNIS: I murdered my brother. 

\ti{\MELISANDRE ~stands and approaches \STANNIS.}

\MELISANDRE: We murdered him. Share the weight with me. 

\STANNIS: He wasn't your brother. 

\MELISANDRE: \sd{Next to \STANNIS ~and stroking his neck and shoulders.} This war has just begun. It will last for years. Thousands will die at your command. You will betray the men serving you. You will betray your family. You will betray everything you once held dear. And it will all be worth it because you are the Son of Fire. You are the Warrior of Light. You will sweep aside this pretender and that one. You will be King. 

\STANNIS: You promise these things, but$\ldots$ you don't know. None of us know. 

\MELISANDRE: Let me show you. \sd{Walking towards one of the fires, pulling \STANNIS ~with her, by the hand.} Look into the fire, my King. Look. 

\STANNIS: I see fire. 

\MELISANDRE: Keep looking. Do you see? Do you see, my King? 

\ti{\STANNIS ~stares deeply into the flames.}

\STANNIS: Yes. 


\scene

\textit{WINTERFELL} 

\sfx Horns

\ti{\THEON ~sits opposite a fire in his room. \LUWIN ~stands in the doorway.}

\THEON: I will kill that man. I don't care how many arrows they feather me with, how many spears they run through me, I will kill that horn-blowing cunt before I fall. 

\LUWIN: They want you to know you're surrounded. 

\THEON: I know I'm surrounded. I know that because I stood on the battlements and saw I was surrounded. 

\LUWIN: They don't want you to sleep. They want to sap your spirit before---  

\THEON: Thank you, wise bald man. Thank you for explaining siege tactics to me. No word from my father? 

\LUWIN: No. 

\THEON: Send more ravens. 

\LUWIN: You killed all the ravens. 

\THEON: The first time I saw Winterfell--- 

\sfx{Horns sound} 

\THEON: The first time I saw Winterfell, it looked like something that had been here for thousands of years and would be here for thousands of years after I was dead. I saw it and I thought, of course Ned Stark crushed our rebellion and killed my brothers. We never stood a chance against a man who lives here. 

\LUWIN: Lord Stark went out of his way to make it your home. 

\THEON: Yes, my captors were so very kind to me. You love reminding me of that. Everyone in this frozen pile of shit has always loved reminding me of that. You know what it's like to be told how lucky you are to be someone's prisoner? To be told how much you owe them? And then to go back home to your real father---

\sfx{Horns sound} 

\THEON: I will kill that man. I swear it to the Drowned God, the Old Gods, the New Gods, to every fucking god in every fucking heaven, I will kill that man. 

\LUWIN: Theon, listen to me. I serve Winterfell. Now Winterfell is yours. I'm bound by oath to serve you. 

\THEON: And what's your counsel, trusted friend? 

\LUWIN: Run. Five hundred Northmen wait outside the walls. You have twenty men. You can't win. Wait for nightfall and run. 

\THEON: There's nowhere to run. I'd never make it back to the Iron Islands. And even if I did, even if by some miracle I slipped through the lines and made it home, I'd be a coward. The Greyjoy who ran. The shame of the family. 

\LUWIN: Don't go home. Join the Night's Watch. Once a man has taken the Black$\ldots$ he's beyond reach of the law. All his past crimes are forgiven. 

\THEON: I won't make it to the Wall. I won't make it ten feet past the Winterfell gates. 

\LUWIN: There are ways. Hidden passageways built so the Lords of Winterfell could escape. The road will be dangerous. But with a little luck$\ldots$ the Night's Watch is an ancient, honourable order. You'll have opportunities there. 

\THEON: The opportunity for Jon Snow to cut my throat in my sleep. 

\LUWIN: The opportunity to make amends for what you've done. 

\THEON: I've done a lot, haven't I? Things I never imagined myself doing. 

\LUWIN:  I've known you many years, Theon Greyjoy. You're not the man you're pretending to be. Not yet. 

\THEON: You may be right. But I've gone too far to pretend to be anything else. 


\scene

\textit{WINTERFELL: THE COURTYARD} 

\sfx Horn.

\ti{\THEON ~stands on a wall with his sword out, surrounded by his \IRONBORN ~below, including \LORREN ~and \DAGMER.}

\THEON: You hear that? That's the mating call of the Northmen. They want to fuck us. Well, I haven't had a good fuck in weeks. I'm ready for one.  They say every Ironborn man is worth a dozen from the mainland. 

\IRONBORN: Aye! 

\THEON: You think they're right? 

\IRONBORN: Aye. 

\THEON: We die today, brothers. We die bleeding from a hundred wounds with arrows in our necks and spears in our guts, but our war cries will echo through eternity. They will sing about the battle of Winterfell until the Iron Islands have slipped beneath the waves. Every man, woman, and child will know who we were and how long we stood. Aggar and Gelmarr; Wex and Urzen; Stygg and Black Lorren$\ldots$  Ironborn warriors will cry out our names as they leap onto the shores of Seagard and Faircastle. 

\ti{\THEON, who so isn't Henry V, descends from the wall, joining the \IRONBORN ~in the courtyard. \DAGMER ~is behind him}

\IRONBORN: Aye! 

\THEON: Mothers will name their sons for us. 

\IRONBORN: Aye! 

\THEON: Girls will think of us with their lovers inside them. 

\IRONBORN: Aye! 

\sfx Horn sounds.

\THEON: And whoever kills that fucking horn-blower will stand in bronze above the shores of Pyke! 

\IRONBORN: Aye! 

\THEON: What is dead may never die! 

\IRONBORN: What is dead may never die! 

\ti{\THEON ~raises his sword and gives a Mighty Battle Cry.}

\ti{\DAGMER ~clocks \THEON ~on the head with the stick of his spear, and \THEON ~collapses.}

\LORREN: Thought he'd never shut up. 

\DAGMER: It was a good speech. Didn't want to interrupt. 

\ti{Enter \LUWIN.}

\LUWIN: What is this? What are you doing? 

\ti{\DAGMER ~stabs \LUWIN ~with his spear.}

\DAGMER: \sd{To \LORREN ~and the rest of the \IRONBORN.} Let's go home. Come on. 

\ti{Exit \IRONBORN, dragging \THEON ~offstage, as \LUWIN ~falls to the ground.}


\scene

\textit{KINGS LANDING: TYRION'S ROOM} 

\ti{\TYRION ~is lying in his bed. \VARYS ~sits near him. \PODRICK ~stands by the door.}

\TYRION: Why should I believe you? 

\VARYS: Why would I lie about it? 

\TYRION: To create strife between my sister and me. 

\VARYS: Where before there was nothing but love. Ser Mandon Moore tried to kill you on your sister's orders. If it weren't for your Squire's bravery, you'd be a dead man. 

\TYRION: Pod. 

\PODRICK: Yes, My Lord? 

\TYRION: Would it be excessive of me to ask you to save my life twice in a week? 

\PODRICK: No, My Lord. 

\TYRION: You're a good lad. Get Bronn, tell him I want four of his most loyal Goldcloaks outside my door at all times. 

\ti{\PODRICK ~makes as if to go.}

\VARYS: I'm afraid your friend has been relieved of his command of the City Watch. The Goldcloaks are now firmly in the hands of your father or your sister. It varies from cloak to cloak. 

\TYRION: Then my hill tribesmen. 

\ti{\PODRICK ~starts to leave again.}

\VARYS: Have gone home. Your father paid them quite handsomely. I'm afraid we won't be seeing each other for some time, My Lord. 

\TYRION: Don't want to swim too close to a drowning man? And I thought we were friends. 

\VARYS: We are. Podrick, would you mind? 

\ti{\PODRICK ~opens the door as \VARYS ~rises. \SHAE ~enters and sits on the bed by \TYRION. \VARYS ~starts to leave.}
 
\VARYS: \sd{To \TYRION.} There are many who know that without you this city faced certain defeat. The King won't give you any honours, the histories won't mention you, but we will not forget. Come along now, Podrick. 

\ti{Exit \VARYS ~and \PODRICK.}

\SHAE: My love. 

\TYRION: It was good of you to come. 

\SHAE: Good of me? Of course I come. 

\ti{\SHAE ~reaches towards the bandage on \TYRION's face, and he pushes her hand away.}

\SHAE: I want to see you. 

\TYRION: Believe me, you don't. 

\SHAE: Have you looked? I will be the first. 

\ti{\SHAE ~unwraps \TYRION's bandages. He has a scar running diagonally across his face.}

\TYRION: Well? 

\SHAE: \sd{Gently.} You are a mess. 

\TYRION: I'm a monster as well as a dwarf. You should charge me double. 

\SHAE: You think I'm here for money? 

\TYRION: That was the arrangement we made. I pay you and you lie to me. 

\SHAE: Aw, I'm a poor little rich man and nobody loves me, so I make jokes all the time and pay them to laugh. Fuck your money. Let's leave. 

\TYRION: Leave? 

\SHAE: Leave King's Landing. They tried to kill you. They will try again. Going into wars, fighting soldiers$\ldots$ you're terrible at this. Let's take a boat to Pentos and never come back. You don't belong here. 

\TYRION: What would we do in Pentos? 

\SHAE: Eat, drink, fuck, live. 

\TYRION: I want to go with you. 

\SHAE: So do it.  Your father, your sister, all these bad people, they can't stop you. Forget about them. Come with me. 

\TYRION: I can't. I do belong here. These bad people are what I'm good at. Outtalking them, outthinking them. It's what I am. And I like it. I like it more than anything I've ever done. Are you going to leave? 

\SHAE: You have a shit memory. I am yours and you are mine. 

\ti{\TYRION ~starts to cry. \SHAE ~lies down on \TYRION's chest, and \TYRION ~holds her.}


\scene

\textit{NEAR ROBB'S CAMP} 

\ti{A firelight ceremony. \SEPTON ~stands in front of \ROBB ~and \TALISA ~, binding their hands together with cloth}

\SEPTON: In the sight of the Seven, I hereby seal these two souls, binding them as one for eternity. Look upon one another and say the words. 

\textbf{ROBB/TALISA}: Father, Smith, Warrior, Mother, Maiden, Crone, Stranger I am hers/his and she/he is mine from this day until the end of my days. 

\ti{\ROBB ~and \TALISA ~kiss.}


\scene

\textit{QARTH: OUTSIDE THE HOUSE OF THE UNDYING} 

\ti{\JORAH, \DAENERYS ~and \KOVARRO ~walk up a path towards the House of the Undying, \JORAH ~leading and \KOVARRO ~bringing up the rear}

\KOVARRO: Vaes leisi, zhey khaleesi. Me nem nesa. [A house of ghosts, khaleesi. It is known.]

\ti{They reach the bottom of the steps, and pause.}

\KOVARRO: Finne loshaki? [Where are the guards?] 

\JORAH: Vo loshaki. Moveki addrivi k'athmovezari, vo ki tawakofi. [No guards. The warlocks kill with sorcery, not steel.] 

\DAENERYS: Azhi morea kis tat. [Let them try.] 

\ti{\DAENERYS ~leading, they walk up to the outside walls. The walls go round in a circle and there is no door.}

\DAENERYS: Is this a riddle? 

\ti{\DAENERYS ~strides off, walking around the outside walls. \JORAH ~follows trying to keep her in sight, while \KOVARRO ~stays still. Just as \JORAH ~loses \DAENERYS ~from sight, he is back to the start and sees \KOVARRO ~, who turns. \DAENERYS ~is nowhere to be seen.}

\JORAH: \sd{Shouting.} Khaleesi! Khaleesi! Khaleesi! 

\ti{\DAENERYS ~is now inside the House of the Undying. She pulls a torch from the wall and looks around.}

\DAENERYS: Are you trying to frighten me with magic tricks? You want me? Here I am. Are you afraid of a little girl?

\sfx Dragons.

\ti{\DAENERYS ~hears the sound of dragons, and sets off in the direction of the sound.} 


\scene

\textit{IN THE WILDERNESS}

\ti{\GENDRY, \ARYA ~and \HOTPIE ~look up and see \JAQEN ~standing on a cliff above them.}

\GENDRY: How did he find us? 

\ti{\ARYA ~keeps walking, leaving \GENDRY ~and \HOTPIE ~behind. \JAQEN ~appears behind her.}

\ARYA: What are you doing here? 

\JAQEN: Waiting for you. 

\ARYA: How did you know we'd come this way? 

\JAQEN: After all the things you have seen, this is your question? 

\ARYA: How did you kill those guards? Was it hard? 

\JAQEN: No harder than taking a new name if you know the way. 

\ARYA: Show me how. I want to be able to do it, too. 

\JAQEN: If you would learn, you must come with me. 

\ARYA: Where? 

\JAQEN: Far and away across the Narrow Sea to Braavos. 

\ARYA: My dancing master was from Braavos. 

\JAQEN: To be a dancing master is a special thing, but to be a faceless man$\ldots$ that is something else entirely. A girl has many names on her lips.  Joffrey, Cersei, Tywin Lannister, Ilyn Payne, the Hound. Names to offer up to the Red God. She could offer them all one by one. 

\ARYA: I want to. But I can't. I need to find my brother and mother. And my sister. I need to find her, too. 

\JAQEN: Then we must part. A man has duties as well. Here. \sd{Holding out a coin.}

\ARYA: What is it? 

\JAQEN: A coin of great value. 

\ARYA: \sd{Taking the coin.} Could it buy a horse? 

\JAQEN: It is not meant for the buying of horses. 

\ARYA: Then what good is it? 

\JAQEN: If the day comes when you must find me again, just give that coin to any man from Braavos and say these words to him, ``Valar Morghulis''. 

\ARYA: Valar Morghulis. \sd{\JAQEN ~starts to leave.} Please don't go, Jaqen. 

\JAQEN: Jaqen is dead. Say it again. Valar Morghulis. 

\ARYA: Valar Morghulis. 

\JAQEN: Good.

\ti{\JAQEN ~turns away from \ARYA ~. When he turns back, he has a different face.}

\JAQEN: Farewell, Arya Stark. 

\ti{Exit \JAQEN.}


\scene

\textit{WINTERFELL} 

\ti{\OSHA, \BRAN ~and \HODOR, and \RICKON ~sneak into the courtyard at Winterfell.}

\BRAN: Osha, what are you doing? 

\n The group walk through the courtyard at Winterfell. It is burned. Carts lie blackened on their side, and bodies are scattered across the ground. Ashes blow through the air, and some fires are still burning. The Dire Wolves begin to whine, leading the group to the clearing just outside Winterfell. This is where they find Maester Luwin, lying propped against a tree.

\ti{\RICKON ~runs to \LUWIN. \OSHA, \BRAN ~and \HODOR ~follow.}

\BRAN: Tell us what medicine to get from your chambers. 

\RICKON: We'll make you better. 

\LUWIN: I feel just fine. 

\BRAN: They burned it down. They burned everything. 

\LUWIN: Not everything. Not you. But they may come back. You have to go. Put on your warmest clothes. Pack as much food as you can carry and go north. 

\OSHA: North's the wrong way. Their mother and brother are south. 

\LUWIN: We don't know where. There are too many enemies in the South. Go to the Wall to Jon. He'll look after you and let your mother know you're safe. 

\BRAN: I don't want to leave you. 

\LUWIN: No more than I want to leave you. \sd{Taking \BRAN's hand.} I pulled you into the world. Both of you. \sd{To \BRAN ~and \RICKON.} I've seen both your faces almost every day since. And for that, I consider myself very, very lucky. Go now with Hodor. Go on. I'll be right here. 

\HODOR: \sd{Picking up \BRAN ~} Hodor. 

\ti{Exit \HODOR, \BRAN ~and \RICKON. \OSHA ~kneels by \LUWIN ~}

\LUWIN: Osha. \sd{Grabbing \OSHA's shoulder} You must protect them. You're the only one who can. You may have to protect them against your own kind. 

\OSHA: I've got no great love for my own kind. I'll get you milk of the poppy. Tell me where to find it. 

\LUWIN: I don't want milk of the poppy. \sd{Nodding towards \OSHA's knife.} Do it quickly. 

\ti{\OSHA ~glances behind, to where the others exited, and pulls out the knife.}

\n Osha, Bran, Rickon and Hodor make their way across the plain, Hodor pushing Bran in a cart. Winterfell burns behind them.


\scene

\textit{QARTH: HOUSE OF THE UNDYING} 

\sfx Dragons screeching

\ti{DAENERYS is searching for her dragons in the House of the Undying.}

\NARRATOR: Daenerys wanders through dark corridors in the House of the Undying, holding a torch and following the sound of dragons. She approaches a door, listening for dragons, and then pushes it open. She enters a round, empty chamber, with a large stone table at the centre, and doorways all around the room. She looks around, trying to identify where the dragon noises are coming from.\\
She chooses one of the doors, and walks through it, into the Great Hall. It is covered in snow, which is still falling through the ruined ceiling. Daenerys places the torch down and looks up at the ruined hall, before slowly approaching the Iron Throne. She reaches out$\ldots$ and then hearing the sound of dragons again, she walks away, following the sound.\\
As Daenerys walks, a large door in front of her slides upwards, and she walks through$\ldots$ and is now outside the Wall. There is too much snow to easily see, but she makes out a tent in the distance and heads towards it.\\
Entering the tent, Daenerys is now in the tent of Drogo, who sits holding a child

\DROGO: Jalan atthirari anni. [Moon of my life.] 

\ti{\DAENERYS ~slowly approaches, staring at the child.}

\DAENERYS: Jini athmovezar qoyi ven athmovezar fini fich yera anhoon-fini fich yera anhoon hatif$\ldots$ [This is dark magic, like the magic that took you from me. Took you from before I could even$\ldots$] Ishish anha drivak vosma anha ray nesok mae vos. Ishish anha ma yeroon she Rhaeshi Ajjalani. [Maybe I am dead and I just don't know it yet. Maybe I am with you in the Night Lands.] 

\DROGO: Ma ishish anha zajje emralat Rhaeshis Ajjalani oma yeroon. Ishish anha ast Vezhofaan meme jifo hilee ma anha jad jinnaan haji ayolat yera. [Or maybe I refused to enter the Night Lands without you. Maybe I told the Great Stallion to go fuck himself and came back here to wait for you.]  

\DAENERYS: Jini vena tikh meyer jif ti. [That sounds like something that you would do.]

\ti{\DROGO ~gently pulls \DAENERYS ~down to sit next to him. \DAENERYS ~sits and reaches out to touch the child.} 

\DROGO: Ma ishish me atthirarido. Atthirarido che yeri che anni$\ldots$ Anha vo nesok. \sd{\DAENERYS ~looks up at \DROGO.} Jini qafe ha mahrazhea ville ma qorasoa reddi. [Or maybe it is a dream. Your dream, my dream$\ldots$ I do not know. These are questions for wise men with skinny arms.] Yer jalan atthirari anni. Haz nesak anha disse, ma anha zigerok nesat vos alikh.  Ma hash jini atthirarido, hash anha vaddrivak mahrazhes fin kis vallatha anna. [You are the Moon of my Life. That is all I know, and all I need to know. And if this is a dream, I will kill the man who tries to wake me.] 

\ti{\DAENERYS ~looks back at the child, and then turns to \DROGO.}

\sfx{Dragons}

\ti{\DAENERYS ~leans against \DROGO.}

\DAENERYS: Until the sun rises in the west and sets in the east, until the rivers run dry and the mountains blow in the wind like leaves.

\ti{\DAENERYS ~strokes \DROGO's face. \DAENERYS ~touches the child one last time, and exits. Cut to the chamber of the House of the Undying, where \DAENERYS ~enters. The dragons ~are now on the table in the centre, and \DAENERYS ~reaches out to them. \PYAT ~appears behind \DAENERYS.}
 
\PYAT: They miss their mother. They want to be with you. Do you want to be with them? You will be. When your dragons were born, our magic was born again. It is strongest in their presence. And they are strongest in yours. You will be with them, through winter, summer, and winter again. Across a thousand thousand seasons you will be with them. 

\ti{Chains appear on \DAENERYS' wrists, and \PYAT ~pulls the chains tight from two sides of the room, until \DAENERYS ~has her arms pulled wide to either side.} 

\PYAT: And we will be with you until time comes to an end. Welcome home, Daenerys Stormborn. 

\DAENERYS: This is not my home. My home is across the sea where my people are waiting for me. 

\PYAT: They will be waiting a long time. 

\ti{\DAENERYS ~turns her head to see her dragons behind her.}

\DAENERYS: \sd{To \PYAT.} Dracarys. 

\n Pyat leans to look at the dragons, and the dragons breathe fire at him with increasing ferocity. The flames pass right through Daenerys, who still stands in chains, watching Pyat burn.

\ti{\PYAT ~falls to the floor. The chains fall from \DAENERYS' wrists.}


\scene

\textit{NORTH OF THE WALL} 

\ti{The \textbf{WILDLINGS} are walking across the mountains in single file, with \YGRITTE, \JON ~and \HALFHAND ~among them. \JON ~and \HALFHAND's hands are tied together with rope}

\YGRITTE: We should be there by sundown. Won't be a fun night for you. Mance knows how to make crows sing. If you know what to say, you might just make it through the night.  Not talking's not the way to go. 

\ti{\YGRITTE ~dodges behind \JON ~and steals his sword.}

\JON: Careful with that. You might cut yourself. Never swung a sword before, have you? You look like a baby with a rattle. 

\ti{\YGRITTE ~moves aggressively towards \JON ~with the sword out.}

\HALFHAND: Enough of that! 

\ti{\HALFHAND ~elbows the Wildling behind him, \WILDLINGa , in the face, draws his sword, and charges towards \JON. They start to fight. \JON ~falls to the ground and \HALFHAND ~is held back by \WILDLINGa ~and \WILDLINGb}

\JON: Stop! 

\HALFHAND: \sd{Struggling to free himself} Why, traitor? So you can give Mance Rayder an invitation to Castle Black? 

\ti{\YGRITTE ~runs round to \JON ~and throws his sword next to him.}

\LORDOFBONES: Let `em fight. 

\ti{\WILDLINGa ~and \WILDLINGb ~let go of \HALFHAND, who charges \JON ~as \JON ~stands. They fight. After some clashing, they circle each other.}

\HALFHAND: \sd{Circling.} That's it? That's what you can do? You little shit. 

\ti{Fighting continues. \JON ~then slips around behind \HALFHAND, avoiding a clash.} 

\HALFHAND: \sd{Standing opposite \JON.} Your traitor father teach you that? \sd{Fighting, and then they lock swords.} Or was it your whore mother?

\ti{Fighting. \HALFHAND ~headbutts \JON, who falls to the ground. \JON ~rises and fighting continues. \HALFHAND ~is disarmed. Beat. \JON ~stabs \HALFHAND ~and pulls his sword free.}

\HALFHAND: We are the Watchers on the Wall. \sd{Falls}

\YGRITTE: \sd{To \LORDOFBONES.} You can tell Mance that's the man who killed Qhorin Halfhand. 

\ti{\LORDOFBONES ~walks to \JON ~, and takes his sword, using it to cut the ropes binding \JON's wrists.}

\LORDOFBONES: \sd{To the Wildlings.} Burn the body. \sd{To \JON.} You don't want this one coming back for you. \sd{Walks away.}

\YGRITTE: \sd{Approaches \JON.} Come along, Jon Snow. Time to meet the King Beyond The Wall. 


\scene

\textit{QARTH: XARO'S CHAMBERS} 

\ti{\XARO ~is lying in his bed, with \DOREAH ~next to him. \KOVARRO ~gently eases his blade under \XARO's ~necklace, and rips it off.} 

\XARO: \sd{Sitting up in alarm.} What the---

\ti{\DOREAH ~also sits up quickly. \DAENERYS, with her dragons, \JORAH ~and the rest of the Dothraki move forward until they are in sight.}

\DOREAH: Khaleesi, please. He said you'd never leave Qarth alive. 

\DAENERYS: Come. 

\ti{\DAENERYS ~turns and walks away. \JORAH ~pulls his sword and points it at \XARO.}

\scene

\ti{QARTH: XARO'S VAULT.} 

\ti{\XARO ~and \DOREAH ~now have their hands bound. \KOVARRO ~uses the necklace to open the vault.}

\DAENERYS: \sd{Moving to the entrance of the vault, with a torch.} Nothing. \sd{To \XARO.} Thank you, Xaro Xhoan Daxos. Thank you for teaching me this lesson. 

\ti{\DAENERYS ~nods to \KOVARRO, who pushes \XARO ~forward. \DOREAH ~follows.}

\XARO: I am King of Qarth. I can help you now, truly help you. \sd{He is pushed to the entrance of the vault.} We can take the Iron Throne. I'll bring you a thousand ships. 

\DOREAH: \sd{Crying.} Please, Khaleesi, I beg you. 

\ti{Both \XARO ~and \DOREAH ~are pushed into the vault.}

\DOREAH: Khaleesi. Please! Please! 

\XARO: All that you have dreamed is within your reach! I beg you, please! \sd{\JORAH ~pushes the vault door closed.} Khaleesi! 

\scene

\textit{QARTH: XARO'S CHAMBERS} 

\ti{\DAENERYS, \KOVARRO, \JORAH ~and the remaining Dothraki are in Xaro's house, pulling out all of Xaro's things.}

\JORAH: It's all a lie. 

\DAENERYS: Looks real enough to me. \sd{Picking up a golden bowl.} Real enough to buy a ship? 

\JORAH: Aye, a small ship. 

\ti{\JORAH ~takes the bowl and \DAENERYS ~exits.}

\JORAH: \sd{To Dothraki} Mas ovray movekkhi moskay. [The remaining valuables are for loading.] 

\ti{Looting.}


\scene

\textit{NORTH OF THE WALL} 

\ti{\GRENN, \EDD ~and \SAM ~are poking around in the snow with hoes and spades, looking for animal droppings.}

\GRENN: I thought we were coming north to fight wildlings. \sd{Picking up Moose poo.} Is this goat? 

\EDD: It's moose. \sd{Placing moose poo in his sack.} 

\GRENN: People shouldn't live anywhere you need to burn shit to keep warm. 

\EDD: Well, you see a tree, let me know. 

\SAM: If you step back and think about it, the thing about Gilly that's so interesting is---  

\EDD: \sd{Kneeling and poking around in the snow.} Just bloody kill me. 

\ti{During the next line, \GRENN ~also kneels and roots around in snow.}

\SAM: No, truly. The thing about her that I find so interesting is that after all that Craster's done to her, she's still got hope that life might get better. 

\EDD: The thing about Gilly that you find so interesting is that she said six words to you. \sd{Rising.}

\SAM: \sd{To \EDD.} And the thing about you that I find so interesting is absolutely nothing. \sd{\GRENN ~also rises.}

\sfx Horn blast.

\SAM: It's Jon and the Halfhand. They're back.

\sfx Horn blast.

\GRENN: \sd{Throwing down hoe and drawing sword} Two blasts is wildlings. 

\EDD: You're not fighting them alone. Come on. \sd{Moving away.}

\sfx Horn blast.

\ti{All pause. \GRENN ~and \EDD ~are facing in one direction, while \SAM ~stands with his back to them, facing the other direction.}

\GRENN: Three blasts? 

\EDD: \sd{Shouting.} Run! 

\ti{\SAM ~stares off into the distance, looking. Then turns round to see \GRENN ~and \EDD ~running away.}

\SAM: \sd{Running after Grenn and Edd} Wait! Wait for me! \sd{Falls in the snow} Grenn! Edd! 

\ti{Exit \GRENN ~and \EDD. \SAM ~stands.}

\n Sam looks all around. The snow is thick and the visibility is very poor, but he can just make out some shapes in the distance. He hurries behind a large boulder and hides.\\
Behind the boulder are large numbers of the undead, slowly approaching. A horse pulls up next to Sam. It has skin flayed off from its neck and chest, and on the horse is a White Walker, holding a crystal sword.\\
The White Walker looks down at Sam, who whimpers and looks away, crying. The White Walker turns to face onward, and raises his spear. As he moves forward, hundreds of the undead follow behind$\ldots$

\end{document}
